### 2017-03-07 designs/blockcipher/arx/1/paper/design.tex
practicing tex/work backup

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Ella Rose\inst{1}}
\institute{Paso Robles, California \email{python_pride@protonmail.com}}
\title[\texttt Design 3-4-17]{\texttt Design 3-4-17}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Block Cipher]{Block Cipher}

\begin{abstract}
  We define and explain the design of a 256-block cipher. The minimalist design is tailored to produce high throughput and low latency on general purpose CPUs, and simple implementation in hardware. Additionally, due to the bit-sliced nature of the design, we predict that it would be reasonably efficient in constrained environments..
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
We describe a cipher algorithm that uses simple XOR, AND, and rotate left instructions on four 64-bit words. Minimum amounts of diffusion are guaranteed through the application of a shift rows and mix column like structure. The 4x4 s-box is the most compact  implementation of all ideal 4x4 s-boxes, and is implemented in 9 instructions. % to do: \cite{http://skew2011.mat.dtu.dk/proceedings/Finding%20Optimal%20Bitsliced%20Implementations%20of%204%20to%204-bit%20S-boxes.pdf}

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left. The state is modeled as a 4x64 grid, with each 64-bit word representing a row. The 64-bit rows will be referred to by $a$, $b$, $c$, and $d$. We define functions in the following section about the algorithm.

\section{Algorithm}
The cipher is an Even-Mansour based construct. It uses a key addition layer, followed by application of a permutation, followed by another key addition layer. The design uses this simple key addition layer, as opposed to generating round keys and applying them after every iteration of the permutation (as is common), because we cannot cite an explicit reason or benefit for so many key application layers. This saves implementation complexity, as there is no key schedule or cacheing of the key schedule.

Each iteration of the permutation consists of alternating linear diffusion and non-linear layers. The diffusion layer consists of three applications of the shift and mix function with differing rotation amounts, which is designed to spread differences around the state evenly. This is followed by the non-linear layer, which is an optimal bitsliced implementation of an optimal 4x4 s-box. The s-box is applied 64 times in parallel on each 4-bit high 1-bit wide section of the state.

Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs.

In psuedocode, the cipher is defined as follows:

\begin{verbatim}
add_key(state, key)
for round_number in 1 ... round_count:
        add_constant(state, round)
        permutation(state)
add_key(state, key)
\end{verbatim}

Next, we will define the $generate\_constant$ function:

\begin{align}
constant := round\_number\\
constant := constant \oplus (constant <<< 3)\\
constant := constant \oplus (constant <<< 6)\\
constant := constant \oplus (constant << 17)\\
constant := constant \oplus (constant << 15)\\
constant := constant \oplus (constant << 24)\\
\end{align}

And the add constant function:

\begin{align}
a = a \oplus generate\_constant(round\_number)
\end{align}

Now we can define the permutation:

%\begin{align}

\begin{align}
\displaystyle\sum_{i=0}^{4} mixPair(a_i, b_i), mixPair(c_i, d_i)\\
\end{align}

Inside the mixState function, applications of mixPairs are interleaved with shiftRows instructions, with a final application of mixPairs operating across halves in order to mix the top and bottom rows of the state:

\begin{align}
mixPairs(a, b, c, d)\\
shiftRows(b, d, 1) \\
mixPairs(a, b, c, d) \\
shiftRows(b, d, 2) \\
mixPairs(a, b, c, d) \\
mixPairs(a, c, b, d) \\
\end{align}

After mixState is applied, the words are transposed by feeding the indices into to s\_box4a:

\begin{align}
for\ i\ in\ 0\ ...\ 16:\\
	\quad j = sbox[i] \\
	\quad state_j = state_i \\
\end{align}

\section{Design\ Rationale}
In this section we will explain the reasoning behind each step. \\

The addConstant function creates a different permutation for each round. This is primarily to guard against slide attacks. The constants are generated by the s\_box, index, and round number because these resources are conveniently accessible when the constants are applied. We see no reason to utilize a more complex function to generate the constants. \\

The addKey function is self explanatory - in order for the transformation to provide confidentiality, secret information must be introduced. \\

An s-box serves the purpose of adding non-linearity to the algorithm. The s-boxes chosen here were selected from the work "Cryptographic Analysis of All 4x4-Bit S-Boxes". The s-box that is used for the transposition layer facilitates an efficient implementation, namely:

\begin{align}
    temp = a[0]\\
    a[0] = c[3]\\
    c[3] = c[0]\\
    c[0] = d[1]\\
    d[1] = c[2]\\
    c[2] = d[2]\\
    d[2] = a[2]\\
    a[2] = b[0]\\
    b[0] = d[0]\\
    d[0] = a[1]\\
    a[1] = b[1]\\
    b[1] = b[2]\\
    b[2] = c[1]\\
    c[1] = a[3]\\
    a[3] = d[3]\\
    d[3] = b[3]\\
    b[3] = temp\\
\end{align}

Otherwise, no special consideration was given to which "golden" 4x4 s-boxes were used: Since each golden 4x4-sbox possesses more or less equivalent cryptographic properties, implementation considerations such as above are the sole criteria for selecting among the available mappings.

Two 4x4 s-boxes are used instead of an 8x8 s-box because of the potential for space savings in constrained environments. Additionally, it may be possible to decompose each 4x4 s-box into a circuit that can be computed discretely, and the size of the s-box would seem to influence the complexity of the resultant circuit. This could be advantageous for creating constant time implementations. Additionally, the smaller s-boxes may (or may not) be less vulnerable to cache based timing attacks, as the contents of both tables should fit in a cache line. \\

The mixState function attempts to spread input differences over as much of the state as possible. It does so with an implementation that scales well with different optimization opportunities on 8-bit platforms, 32-bit platforms, and SIMD capable platforms.

On constrained (i.e. 8-bit) platforms, mixPairs can be applied successively on two 8-bit words at a time\\
If space is available, the mixPairs function can be memoized and stored in a 65KB table\\
If 32-bit words are available, mixPairs can evaulatethe XORs for four pairs of bytes in parallel by operating on two rows at once\\
If vector rotate instructions are available, then the 32-bit mixPairs function listed above may perform the leftward rotations on each byte in parallel\\
If enough registers are available, multiple instances of the algorithm could be run in parallel.\\

mixState is supposed to provide "weak alignment", as opposed to the "strong alignment" that Rijndael has. This means that differences do not propagate along cleanly defined boundaries, and instead spread randomly over the entire state. This is supposed to reduce "clustering" of trails.

The transposition step ensures an irregular arrangement of word pairs are fed into the mixState function. 
\end{document}

### 2017-03-07 designs/blockcipher/strangeencryptor.py

@@ -27,20 +27,20 @@ def branch(word):
     word ^= rotate_left(word, 6, 8)
     return word
     
-KEY = list(set([branch(word) for word in range(32)]))
+KEY = [branch(word) for word in range(32)]
 KEY = dict((entry, KEY.index(entry)) for entry in KEY)
 _KEY = dict((value, key) for key, value in KEY.items())
 
 def encrypt(data, key, decoder=KEY, rounds=ROUNDS):
     key <<= 5
     for round in range(rounds):
-        print "Data: ", data
+        #print "Data: ", data
         data ^= key
-        print "Data ^ key: ", data
+        #print "Data ^ key: ", data
         data = branch(data)
-        print "Branch(data): ", data
+        #print "Branch(data): ", data
         data = decoder[data]
-        print "Decoder[data]: ", data
+        #print "Decoder[data]: ", data
     return data
     
 def decrypt(data, key, encoder=_KEY, rounds=ROUNDS):
@@ -55,7 +55,7 @@ def decrypt(data, key, encoder=_KEY, rounds=ROUNDS):
     
 def test_encrypt():
     ciphertexts = []
-    key = 0
+    key = 1
     for byte in range(32):
         ciphertext = encrypt(byte, key)
         plaintext = decrypt(ciphertext, key)

### 2017-03-07 designs/permutation/linear.py

@@ -5,8 +5,8 @@ PRINT_STRING = "Branch number for 2x {}-bit words: {} (optimum: {})"
 
 def branch8(word):
     # 0 1 2 3  4 5 6 7    
-    word ^= rotate_left(word, 4)
-    word ^= rotate_left(word, 7)
+    word ^= rotate_left(word, 3)
+    word ^= rotate_left(word, 6)
     return word
 
 def mix8(a, b):

### 2017-03-07 other/scratch/compositiontest.py

@@ -1,0 +1,51 @@
+from crypto.utilities import rotate_left, rotate_right
+
+def bit_transposition(state):
+    output = bytearray(8)
+    for index in range(8):
+        output[index] = 0
+        for index2 in range(8):            
+            byte = state[index2]
+            output[index] |= ((byte & 1) << index2) & 255
+            state[index2] = rotate_right(byte, 1, 8)  
+        output[index] = rotate_right(output[index], index, 8)
+    state[:] = output[:]  
+    
+def branch(word): 
+    word ^= rotate_left(word, 3, 8)
+    word ^= rotate_left(word, 6, 8)
+    return word    
+    
+def wtf(word):
+   # word |= rotate_left(word, 3, 8)    
+   # word &= rotate_left(word, 6, 8)
+    word ^= (rotate_left(word, 1, 8) & rotate_left(word, 6, 8)) | rotate_left(word, 3, 8)           
+    return word
+    
+def composed_function(data):    
+    for round in range(2):
+        for index, word in enumerate(data):
+            data[index] = branch(word)
+        bit_transposition(data)
+       # for index, word in enumerate(data):
+       #     data[index] = branch(word)
+       # bit_transposition(data)    
+                
+def test_composed_function():
+    data = range(8)
+    data[1] = 1
+    composed_function(data)
+    print data
+    
+def test_wtf():
+    outputs = []
+    for byte in range(256):
+        for round in range(32):
+            byte = wtf(byte)
+        outputs.append(wtf(byte))
+    print len(set(outputs))     
+     
+if __name__ == "__main__":
+    #test_composed_function()
+    test_wtf()
+    

### 2017-03-10 designs/blockcipher/arx/2/paper/design3817.tex
backing up work

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

\usepackage{algpseudocode}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Anonymous\inst{1}}
\institute{City, State \email{address@provider.com}}
\title[\texttt Design 3-8-17]{\texttt Design 3-8-17}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Block Cipher]{Block Cipher}

\begin{abstract}
  We define a substitution-permutation based block cipher with an 256-bit block size and 512-bit key size. The design is oriented towards desktop CPUs and dedicated hardware. The bit sliced design works best with the largest word size available, so we define a variant that utilizes 64-bit words. The design makes use of only XOR/AND gates and rotations. The 4x4 S-Box is calculated discretely each application, and uses the shortest possible number of instructions among all ideal 4x4 S-Boxes.\\ 
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
 Block ciphers are a widely used component in many cryptography schemes. They can be used with a mode of operation to provide confidentiality (as well as authenticity and integrity) to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function. When required, block ciphers can be designed with a smaller state size (80-128 bits) then a hash or stream cipher (160 bits+), which can lead to smaller and less expensive hardware implementations. Block ciphers are a very versatile class of algorithm.

Substitution-Permutation Networks (SPN) are a class of block cipher construction. Typically, a substiution-permutation network will consist of key addition layers interleaved with alternating applications of non-linear and linear functions. The non-linear function is often times referred to as an "S-Box", and frequently is implemented in the form of a lookup table or memoized function (but does not have to be). The S-Box is usually designed to resist linear and differential cryptanalysis and provides the source of "confusion" in the cipher. The linear function typically provides the "diffusion" in the cipher, and is responsible for ensuring that small input differences propagate to large output differences. The cannonical example of a Substitution-Permutation network is the Advanced Encryption Standard ("AES").

We define a SPN cipher algorithm that is oriented towards 64-bit CPUs and dedicated hardware. The linear layer guarantees a very high number of active S-Boxes over the course of two rounds, and the non-linear layer is applied without the use of tables. This enables the algorithm to be resilient to timing based side channel attacks that can practically break an otherwise theoretically secure algorithm. In many other designs, discrete evaluation of the S-Box function can introduce a significant slowdown in the algorithm. This not the case here, as application of the S-Box requires only 9 instructions. Since the S-Box is applied on 64 sets of bits at once in parallel, the total instruction cost to apply the S-Box to the entire state on an architecture with 64-bit words is only 9 instructions.\footnote{This is 9 instructions, which does not mean 9 clock cycles - The CPU very well may able to do it in well under 9 clock cycles due to pipelining and multiple execution units}

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left. The state consists of four 64-bit words. We denote the four words as $a$, $b$, $c$, and $d$. We refer to the key that is exclusive-or'd into the state as the "Linear Key", and the key that is used for the bit transposition as the "Non-Linear Key". The four 64-bit words of the a key will be referred to as $k0$, $k1$, $k2$, and $k3$. The incrementing counter that is fed to the constant generation function is denoted as $i$\\

We will use the following function names: $K_l$ refers to the linear key addition layer, while $K_n$ refers to the non-linear key addition layer (the keyed bit permutation); $K_f$ refers to the composition of $K_n$ and $K_l$, meaning $K_f(a, b, c, d) \equiv K_l(K_n(a, b, c, d))$. Application of the linear layer is denoted as $L(a, b, c, d)$, while application of the non-linear/S-Box layer is denoted as $S(a, b, c, d)$. The "load" function unpacks a 256-bit key into four 64-bit words.

\section{Algorithm}
 We define a Substitution-Permutation Network type cipher algorithm. The first thing to note is that the algorithm utilizes a non standard key addition layer. The key addition layer consists of two parts; First, a non-linear key addition layer is applied, in the form of a keyed bitwise permutation. Second, a standard linear key addition layer is applied, in the form of exclusive-or with the Linear Key. The key addition layer is applied before/after every four iterations of the permutation.

Each round of the permutation consists of generation and addition of the round constant to the word $a$ of the state via exclusive-or, application of the non-linear layer or "S-Box" to the columns of the state, and lastly the linear branching layer. Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before/after each step. \\

\begin{algorithmic}
\Function{$encrypt$}{$a, b, c, d, nonlinear\_key, linear\_key$}
	\State $i \gets 0;$
	\For {$step \gets 0; step < 4; step \gets step + 1$}
		\State $a, b, c, d \gets bit\_shuffle(a, b, c, d, nonlinear\_key);$
		\State $a, b, c, d \gets add\_key(a, b, c, d, linear\_ key);$

		\For{$round \gets 0; round < 4; round \gets round + 1;$}	
			\State $a, b, c, d \gets round_function(a, b, c, d, i);$	
			\State $i \gets i + 1$
		\EndFor
	\EndFor
\EndFunction\\
\end{algorithmic}

The bit shuffle function is the non-linear key addition layer. It uses the nonlinear key as the selector input to the choice swap function to transpose bits. The choice swap function powers the shuffle columns function, which transposes the elements of each 4-bit column. Successive applications of shuffle columns are interleaved with shift rows, so that that three applications ensures coverage of the entire state. Similarly to the linear diffusion layer, two rounds are applied to ensure a high degree of difference in the output distribution.\\

\begin{algorithmic}
\Function{$bit\_shuffle$}{$a, b, c, d, nonlinear\_key$}
	\State $k0, k1, k2, k3 \gets load(nonlinear\_key)$
	\For{$round \gets 0; round < 2; round \gets round + 1;$}
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 1,\ \ 2,\ \ 3, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 4,\ \ 8,\ 12, k0, k1, k2, k3);$
		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, 16, 32,\ 48, k0, k1, k2, k3);$
	\EndFor
\EndFunction\\
\end{algorithmic}

The add key function simply combines the linear key with the state via the exclusive-or function:\\

\begin{algorithmic}
\Function{$add\_key$}{$a, b, c, d, linear\_key$}
	\State $k0, k1, k2, k3 \gets load(linear\_key)$ % need to clarify k0 and friends are used for linear key to, and define load
	\State $a \gets a \oplus k0$
	\State $b \gets b \oplus k1$
	\State $c \gets c \oplus k2$
	\State $d \gets d \oplus k3$
\EndFunction
\end{algorithmic}

The permutation is composed of three functions: addition of the round constant, the non-linear S-Box layer, and the linear diffusion layer. Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function .

\begin{algorithmic}
\Function{$round\_function$}{$a, b, c, d, i$}
	\State $a \gets a \oplus generate\_constant(i)$
	\State $a, b, c, d \gets S\-Box(a, b, c, d)$
	\State $a, b, c, d \gets linear\_layer(a, b, c, d)$
\EndFunction\\
\end{algorithmic}

The $generate\_constant$ function is defined as follows: \\

\begin{algorithmic}
\Function{$generate\_gonstant$}{$i$}
	\State $constant \gets i$
	\State $constant \gets constant \oplus (constant \lll 3)$
	\State $constant \gets constant \oplus (constant \lll 6)$
	\State $constant \gets constant \oplus (constant \lll 17)$
	\State $constant \gets constant \oplus (constant \lll 15)$
	\State $constant \gets constant \oplus (constant \lll 24)$	
\EndFunction\\
\end{algorithmic}

The non-linear S-Box function applies a 4x4 S-Box with ideal cryptographic properties on each of the 64 columns of the state. The S-Box is not evaluated via table lookup, but is computed explicitly upon each invocation. This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as follows: \\

\begin{algorithmic}
\Function{$S\-Box$}{$a, b, c, d$}
	\State $t \gets a$
	\State $a \gets (a \land b) \oplus c$
	\State $c \gets (b \lor c) \oplus d$
	\State $d \gets (d \land a) \oplus t$
	\State $b \gets b \oplus (c \land t)$
\EndFunction\\
\end{algorithmic}

Finally, the linear diffusion function consists of three applications of the $Shift\_And\_Mix$ function with varying rotation amounts. The shift and mix function can be viewed as a variant of the well established shiftRows and mixColumns paradigm for providing diffusion. The "mixColumns" function presented here is minimalist, and utilizes four instructions total to mix all 64 columns of the state in parallel. \\

\begin{algorithmic}
\Function{$linear\_layer$}{$a, b, c, d$}
	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 1, 2, 3)$
	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 4, 8, 16)$
	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 16, 32, 48)$
\EndFunction\\

\Function{$shift\_and\_mix$}{$a, b, c, d, r1, r2, r3$}
	\State $b, c, d \gets shift\_rows(b, c, d, r1, r2, r3)$
	\State $a, b, c, d \gets mix\_columns(a, b, c, d)$
\EndFunction\\

\Function{$shift\_rows$}{$b, c, d, r_1, r_2, r_3$}
	\State $b\gets b \lll r_1$
	\State $c \gets c \lll r_2$
	\State $d \gets d \lll r_3$
\EndFunction\\

\Function{$mix\_columns$}{$a, b, c, d$}
	\State $a \gets a \oplus d$
	\State $b \gets b \oplus c$
	\State $c \gets c \oplus a$
	\State $d \gets d \oplus b$
\EndFunction\\
\end{algorithmic}

\section{Design\ Rationale}
The non-linear key addition layer, or keyed bitwise permutation, is designed to thwart algebraic attacks by making it to where the terms of the equations that describe the cipher output are a secret. The transposition may additionally complicate linear and differential cryptanalysis. A software implementation of the bitwise permutation utilizes the choice swap function to conditionally transpose bits according to the key. Because this is a bit sliced operation, it should scale reasonably well across different architectures and word sizes. A hardware implementation has the potential to implement the bitwise permutation via crossed wires, which could save considerable time. The software implementation of the bitwise permutation is not terribly slow, but it does use more instructions then the linear and non-linear parts of the round function. Resistance of the algorithm against related key attacks was not considered; Considering the nature of the transposition operation, it is probable that one could easily find two keys that will take a given input to identical output states. For this reason, combined with the fact that no key schedule is applied to the non-linear key, we do not recommend the usage of this variant as the building block of a compression function.

The linear exclusive-or key addition layer is standard and is used in many if not most (modern) cipher designs. This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate. Additionally, exclusive-or is an involution, which can simplify implementation even more in some cases. \\

No key schedule is applied to either the linear key or non-linear key. Application of a key schedule requires additional space, time, and code complexity, for benefits that often times are not immediately obvious or ever explicitly stated. The cipher LED utilizes no key schedule, relying on addition of the round constants to simulate the activity of alternative round keys; It appears to be resistant even to related key attacks because/despite of this fact. We choose to utilize this model in the design here and collect the time, space, and complexity savings.

The rotation amounts in the linear layer were not chosen heuristically or arbitrarily. By using these amounts, we ensure that input differences will spread out and maximize the number of active s-boxes. This can be easily seen with the help of visual aid. The first shift and mix step is analogous to the shift and mix step of AES, applying a column mixing operation on 4 words and then rotating the rows sideways to spread the differences to the neighboring columns. Because the state is 64 bits wide instead of 16 bits wide, we require three applications with increasing rotation amounts to spread an input difference across the complete state. The mix column operation here operates on 4 bits at a time; The goal is to ensure that approximately half of the input bits influence half of the output bits. This is accomplished by the exclusive-or of one of the bits with another bit, for doing so ensures that two bits now influence the augend. Due to the requirement of maintaining bijectivity, we are unable to make exactly half of the input bits influence half of the output bits; We can outline exactly which bits influence which other bits by examing the mix column operation closely:

\begin{algorithmic}
\Function{$mix\_columns$}{$a, b, c, d$}
	\State $a \gets a \oplus d$ 
	\Comment{$a$ is influenced by $a, d$}
	\State $b \gets b \oplus c$ 
	\Comment{$b$ is influenced by $b, c$}
	\State $c \gets c \oplus a$ 
	\Comment{$c$ is influenced by $a, c, d$}
	\State $d \gets d \oplus b$ 
	\Comment{$d$ is influenced by $b, c, d$}
\EndFunction
\end{algorithmic}

The S-Box was presented in Finding Optimal Bitsliced Representations of 4x4 S-Boxes; It is represented via a circuit diagram on page 9, table 5. This particular mapping offers ideal cryptographic properties as well as the lowest implementation cost among all ideal 4x4 s-boxes. Due to the fact that one can easily examine the system of equations that represents the cipher simply by examining the combined linear and non-linear layers, we opted to implement our keyed bit transposition layer as a countermeasure against potential algebraic attacks.

The constant generation function was created in a manner that follows the train of thought of the mix column function: simply ensure each input bit influences half of the output bits. Due to the word size, we had to run a search to find the best rotation amounts; We judged results by maximizing the minimum difference between successive output words. Successive outputs of the constant generation function have a high weight and hamming distance. Addition of the round constants eliminates rotational symmetry that would otherwise be present in the design. Usually, round constants provide resistance against slide attacks; Due to the block size of the construction here, slid pairs should not occur often enough to be a problem; This mostly likely provides greater resistance to generic slide attacks then addition of the constant.

\section{Conclusion}
 We define an 256-bit Substitution-Permutation based block cipher with a 512-bit key that is oriented towards 64-bit CPUs and dedicated hardware. Our design uses only simple XORs, ANDs, and rotations, and offers a simple and constant-time implementation. While perhaps not ideal for smaller architectures, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes. We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the cipher structure.

\end{document}

### 2017-03-10 latex/cipher_templates/blockcipher/generic/template.tex
backing up work

--- 2017-03-10 designs/blockcipher/arx/2/paper/design3817.tex
@@
 \usepackage[utf8]{inputenc}
-
-\usepackage{algpseudocode}
 
@@
 \institute{City, State \email{address@provider.com}}
-\title[\texttt Design 3-8-17]{\texttt Design 3-8-17}
+\title[\texttt Design date]{\texttt Design date}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Block Cipher]{Block Cipher}
+\keywords[Block Cipher]{Block Cipher}\todo{Keywords?}
 
 \begin{abstract}
-  We define a substitution-permutation based block cipher with an 256-bit block size and 512-bit key size.
-The design is oriented towards desktop CPUs and dedicated hardware.
-The bit sliced design works best with the largest word size available, so we define a variant that utilizes 64-bit words.
-The design makes use of only XOR/AND gates and rotations.
-The 4x4 S-Box is calculated discretely each application, and uses the shortest possible number of instructions among all ideal 4x4 S-Boxes.\\
+  We define a block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size.
+The design is oriented towards PLATFORM TYPE\todo{Constrained Devices?
+Consumer CPUs?
+What architecture/native word sizes?}.
+The design makes use of certain instruction types or gates.
+\todo{XOR/AND?
+ADD/XOR?
+Multiplication?
+Modular Exponentiation?
+Lookup Tables?}\\
 \end{abstract}
@@
 
-Substitution-Permutation Networks (SPN) are a class of block cipher construction.
-Typically, a substiution-permutation network will consist of key addition layers interleaved with alternating applications of non-linear and linear functions.
-The non-linear function is often times referred to as an "S-Box", and frequently is implemented in the form of a lookup table or memoized function (but does not have to be).
-The S-Box is usually designed to resist linear and differential cryptanalysis and provides the source of "confusion" in the cipher.
-The linear function typically provides the "diffusion" in the cipher, and is responsible for ensuring that small input differences propagate to large output differences.
-The cannonical example of a Substitution-Permutation network is the Advanced Encryption Standard ("AES").
-
-We define a SPN cipher algorithm that is oriented towards 64-bit CPUs and dedicated hardware.
-The linear layer guarantees a very high number of active S-Boxes over the course of two rounds, and the non-linear layer is applied without the use of tables.
-This enables the algorithm to be resilient to timing based side channel attacks that can practically break an otherwise theoretically secure algorithm.
-In many other designs, discrete evaluation of the S-Box function can introduce a significant slowdown in the algorithm.
-This not the case here, as application of the S-Box requires only 9 instructions.
-Since the S-Box is applied on 64 sets of bits at once in parallel, the total instruction cost to apply the S-Box to the entire state on an architecture with 64-bit words is only 9 instructions.\footnote{This is 9 instructions, which does not mean 9 clock cycles - The CPU very well may able to do it in well under 9 clock cycles due to pipelining and multiple execution units}
+\todo{Explain the motivation for the design described here}
 
 \section{Definitions}
-We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left.
-The state consists of four 64-bit words.
-We denote the four words as $a$, $b$, $c$, and $d$.
-We refer to the key that is exclusive-or'd into the state as the "Linear Key", and the key that is used for the bit transposition as the "Non-Linear Key".
-The four 64-bit words of the a key will be referred to as $k0$, $k1$, $k2$, and $k3$.
-The incrementing counter that is fed to the constant generation function is denoted as $i$\\
-
-We will use the following function names: $K_l$ refers to the linear key addition layer, while $K_n$ refers to the non-linear key addition layer (the keyed bit permutation); $K_f$ refers to the composition of $K_n$ and $K_l$, meaning $K_f(a, b, c, d) \equiv K_l(K_n(a, b, c, d))$.
-Application of the linear layer is denoted as $L(a, b, c, d)$, while application of the non-linear/S-Box layer is denoted as $S(a, b, c, d)$.
-The "load" function unpacks a 256-bit key into four 64-bit words.
+\todo{Define the notation used in this paper}\\
+\todo{Define how the state is laid out and indexed/addressed}\\
+We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...
 
 \section{Algorithm}
- We define a Substitution-Permutation Network type cipher algorithm.
-The first thing to note is that the algorithm utilizes a non standard key addition layer.
-The key addition layer consists of two parts; First, a non-linear key addition layer is applied, in the form of a keyed bitwise permutation.
-Second, a standard linear key addition layer is applied, in the form of exclusive-or with the Linear Key.
-The key addition layer is applied before/after every four iterations of the permutation.
-
-Each round of the permutation consists of generation and addition of the round constant to the word $a$ of the state via exclusive-or, application of the non-linear layer or "S-Box" to the columns of the state, and lastly the linear branching layer.
-Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before/after each step.
-\\
-
-\begin{algorithmic}
-\Function{$encrypt$}{$a, b, c, d, nonlinear\_key, linear\_key$}
-	\State $i \gets 0;$
-	\For {$step \gets 0; step < 4; step \gets step + 1$}
-		\State $a, b, c, d \gets bit\_shuffle(a, b, c, d, nonlinear\_key);$
-		\State $a, b, c, d \gets add\_key(a, b, c, d, linear\_ key);$
-
-		\For{$round \gets 0; round < 4; round \gets round + 1;$}	
-			\State $a, b, c, d \gets round_function(a, b, c, d, i);$	
-			\State $i \gets i + 1$
-		\EndFor
-	\EndFor
-\EndFunction\\
-\end{algorithmic}
-
-The bit shuffle function is the non-linear key addition layer.
-It uses the nonlinear key as the selector input to the choice swap function to transpose bits.
-The choice swap function powers the shuffle columns function, which transposes the elements of each 4-bit column.
-Successive applications of shuffle columns are interleaved with shift rows, so that that three applications ensures coverage of the entire state.
-Similarly to the linear diffusion layer, two rounds are applied to ensure a high degree of difference in the output distribution.\\
-
-\begin{algorithmic}
-\Function{$bit\_shuffle$}{$a, b, c, d, nonlinear\_key$}
-	\State $k0, k1, k2, k3 \gets load(nonlinear\_key)$
-	\For{$round \gets 0; round < 2; round \gets round + 1;$}
-		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 1,\ \ 2,\ \ 3, k0, k1, k2, k3);$
-		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, \ 4,\ \ 8,\ 12, k0, k1, k2, k3);$
-		\State $a, b, c, d \gets shift\_and\_shuffle(a, b, c, d, 16, 32,\ 48, k0, k1, k2, k3);$
-	\EndFor
-\EndFunction\\
-\end{algorithmic}
-
-The add key function simply combines the linear key with the state via the exclusive-or function:\\
-
-\begin{algorithmic}
-\Function{$add\_key$}{$a, b, c, d, linear\_key$}
-	\State $k0, k1, k2, k3 \gets load(linear\_key)$ % need to clarify k0 and friends are used for linear key to, and define load
-	\State $a \gets a \oplus k0$
-	\State $b \gets b \oplus k1$
-	\State $c \gets c \oplus k2$
-	\State $d \gets d \oplus k3$
-\EndFunction
-\end{algorithmic}
-
-The permutation is composed of three functions: addition of the round constant, the non-linear S-Box layer, and the linear diffusion layer.
-Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function .
-
-\begin{algorithmic}
-\Function{$round\_function$}{$a, b, c, d, i$}
-	\State $a \gets a \oplus generate\_constant(i)$
-	\State $a, b, c, d \gets S\-Box(a, b, c, d)$
-	\State $a, b, c, d \gets linear\_layer(a, b, c, d)$
-\EndFunction\\
-\end{algorithmic}
-
-The $generate\_constant$ function is defined as follows: \\
-
-\begin{algorithmic}
-\Function{$generate\_gonstant$}{$i$}
-	\State $constant \gets i$
-	\State $constant \gets constant \oplus (constant \lll 3)$
-	\State $constant \gets constant \oplus (constant \lll 6)$
-	\State $constant \gets constant \oplus (constant \lll 17)$
-	\State $constant \gets constant \oplus (constant \lll 15)$
-	\State $constant \gets constant \oplus (constant \lll 24)$	
-\EndFunction\\
-\end{algorithmic}
-
-The non-linear S-Box function applies a 4x4 S-Box with ideal cryptographic properties on each of the 64 columns of the state.
-The S-Box is not evaluated via table lookup, but is computed explicitly upon each invocation.
-This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as follows: \\
-
-\begin{algorithmic}
-\Function{$S\-Box$}{$a, b, c, d$}
-	\State $t \gets a$
-	\State $a \gets (a \land b) \oplus c$
-	\State $c \gets (b \lor c) \oplus d$
-	\State $d \gets (d \land a) \oplus t$
-	\State $b \gets b \oplus (c \land t)$
-\EndFunction\\
-\end{algorithmic}
-
-Finally, the linear diffusion function consists of three applications of the $Shift\_And\_Mix$ function with varying rotation amounts.
-The shift and mix function can be viewed as a variant of the well established shiftRows and mixColumns paradigm for providing diffusion.
-The "mixColumns" function presented here is minimalist, and utilizes four instructions total to mix all 64 columns of the state in parallel.
-\\
-
-\begin{algorithmic}
-\Function{$linear\_layer$}{$a, b, c, d$}
-	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 1, 2, 3)$
-	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 4, 8, 16)$
-	\State $a, b, c, d \gets shift\_and\_mix(a, b, c, d, 16, 32, 48)$
-\EndFunction\\
-
-\Function{$shift\_and\_mix$}{$a, b, c, d, r1, r2, r3$}
-	\State $b, c, d \gets shift\_rows(b, c, d, r1, r2, r3)$
-	\State $a, b, c, d \gets mix\_columns(a, b, c, d)$
-\EndFunction\\
-
-\Function{$shift\_rows$}{$b, c, d, r_1, r_2, r_3$}
-	\State $b\gets b \lll r_1$
-	\State $c \gets c \lll r_2$
-	\State $d \gets d \lll r_3$
-\EndFunction\\
-
-\Function{$mix\_columns$}{$a, b, c, d$}
-	\State $a \gets a \oplus d$
-	\State $b \gets b \oplus c$
-	\State $c \gets c \oplus a$
-	\State $d \gets d \oplus b$
-\EndFunction\\
-\end{algorithmic}
+\todo{Define the algorithm in detail}\\
+\todo{Describe the block cipher construction type, i.e. Feistel, SPN, Even-Mansour, ARX, etc}\\
+\todo{Define the round function or permutation}
 
 \section{Design\ Rationale}
-The non-linear key addition layer, or keyed bitwise permutation, is designed to thwart algebraic attacks by making it to where the terms of the equations that describe the cipher output are a secret.
-The transposition may additionally complicate linear and differential cryptanalysis.
-A software implementation of the bitwise permutation utilizes the choice swap function to conditionally transpose bits according to the key.
-Because this is a bit sliced operation, it should scale reasonably well across different architectures and word sizes.
-A hardware implementation has the potential to implement the bitwise permutation via crossed wires, which could save considerable time.
-The software implementation of the bitwise permutation is not terribly slow, but it does use more instructions then the linear and non-linear parts of the round function.
-Resistance of the algorithm against related key attacks was not considered; Considering the nature of the transposition operation, it is probable that one could easily find two keys that will take a given input to identical output states.
-For this reason, combined with the fact that no key schedule is applied to the non-linear key, we do not recommend the usage of this variant as the building block of a compression function.
-
-The linear exclusive-or key addition layer is standard and is used in many if not most (modern) cipher designs.
-This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate.
-Additionally, exclusive-or is an involution, which can simplify implementation even more in some cases.
-\\
-
-No key schedule is applied to either the linear key or non-linear key.
-Application of a key schedule requires additional space, time, and code complexity, for benefits that often times are not immediately obvious or ever explicitly stated.
-The cipher LED utilizes no key schedule, relying on addition of the round constants to simulate the activity of alternative round keys; It appears to be resistant even to related key attacks because/despite of this fact.
-We choose to utilize this model in the design here and collect the time, space, and complexity savings.
-
-The rotation amounts in the linear layer were not chosen heuristically or arbitrarily.
-By using these amounts, we ensure that input differences will spread out and maximize the number of active s-boxes.
-This can be easily seen with the help of visual aid.
-The first shift and mix step is analogous to the shift and mix step of AES, applying a column mixing operation on 4 words and then rotating the rows sideways to spread the differences to the neighboring columns.
-Because the state is 64 bits wide instead of 16 bits wide, we require three applications with increasing rotation amounts to spread an input difference across the complete state.
-The mix column operation here operates on 4 bits at a time; The goal is to ensure that approximately half of the input bits influence half of the output bits.
-This is accomplished by the exclusive-or of one of the bits with another bit, for doing so ensures that two bits now influence the augend.
-Due to the requirement of maintaining bijectivity, we are unable to make exactly half of the input bits influence half of the output bits; We can outline exactly which bits influence which other bits by examing the mix column operation closely:
-
-\begin{algorithmic}
-\Function{$mix\_columns$}{$a, b, c, d$}
-	\State $a \gets a \oplus d$ 
-	\Comment{$a$ is influenced by $a, d$}
-	\State $b \gets b \oplus c$ 
-	\Comment{$b$ is influenced by $b, c$}
-	\State $c \gets c \oplus a$ 
-	\Comment{$c$ is influenced by $a, c, d$}
-	\State $d \gets d \oplus b$ 
-	\Comment{$d$ is influenced by $b, c, d$}
-\EndFunction
-\end{algorithmic}
-
-The S-Box was presented in Finding Optimal Bitsliced Representations of 4x4 S-Boxes; It is represented via a circuit diagram on page 9, table 5.
-This particular mapping offers ideal cryptographic properties as well as the lowest implementation cost among all ideal 4x4 s-boxes.
-Due to the fact that one can easily examine the system of equations that represents the cipher simply by examining the combined linear and non-linear layers, we opted to implement our keyed bit transposition layer as a countermeasure against potential algebraic attacks.
-
-The constant generation function was created in a manner that follows the train of thought of the mix column function: simply ensure each input bit influences half of the output bits.
-Due to the word size, we had to run a search to find the best rotation amounts; We judged results by maximizing the minimum difference between successive output words.
-Successive outputs of the constant generation function have a high weight and hamming distance.
-Addition of the round constants eliminates rotational symmetry that would otherwise be present in the design.
-Usually, round constants provide resistance against slide attacks; Due to the block size of the construction here, slid pairs should not occur often enough to be a problem; This mostly likely provides greater resistance to generic slide attacks then addition of the constant.
+\todo{Explain the reasoning for each step of the algorithm}\\
+\todo{Explain how constants are generated and what purpose they serve}\\
+\todo{Describe why the linear and non-linear layers were designed/chosen}\\
+\todo{Justify numerical design decisions, such as word transpositions indices and rotation amounts}\\
 
 \section{Conclusion}
- We define an 256-bit Substitution-Permutation based block cipher with a 512-bit key that is oriented towards 64-bit CPUs and dedicated hardware.
-Our design uses only simple XORs, ANDs, and rotations, and offers a simple and constant-time implementation.
-While perhaps not ideal for smaller architectures, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes.
-We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the cipher structure.
+ We define an N-bit block cipher with a K-bit key that is oriented towards PLATFORM TYPE. \todo{Fill in values for block size/key size and platform type} 
+\todo{Concisely summarize the rest of the paper in a paragraph or two}
 

### 2017-03-10 latex/cipher_templates/blockcipher/spn/template.tex
backing up work

--- 2017-03-10 latex/cipher_templates/blockcipher/generic/template.tex
@@
 \begin{abstract}
-  We define a block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size.
+  We define a substitution-permutation based block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size.
 The design is oriented towards PLATFORM TYPE\todo{Constrained Devices?
@@
 
+Substitution-Permutation networks are class of block cipher construction.
+Typically, a substiution-permutation network will consist of key addition layers interleaved with alternating applications of non-linear and linear functions.
+The non-linear function is often times referred to as an "S-Box", and frequently is implemented in the form of a lookup table or memoized function (but does not have to be).
+The S-Box is usually designed to resist linear and differential cryptanalysis and provides the source of "confusion" in the cipher.
+The linear function typically provides the "diffusion" in the cipher, and is responsible for ensuring that small input differences propagate to large output differences.
+The cannonical example of a Substitution-Permutation network is the Advanced Encryption Standard ("AES").
+
 \todo{Explain the motivation for the design described here}
@@
 \todo{Define how the state is laid out and indexed/addressed}\\
-We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...
+We use $\oplus$ to denote XOR and $\lll$ to denote bitwise rotation left.
+We denote application of the S-Box via $S(x)$ and application of the inverse S-Box via $S^{-i}(x)$.
+The elements of the state are indexed as: \todo{How is the state indexed?}
 
@@
 \todo{Define the round function or permutation}
+
+ We define a Substitution-Permutation network type cipher algorithm.
+The algorithm consists of alternating applications of a key addition layer every number of rounds.
+\todo{After how many rounds is the key applied?} The round function consists of a linear diffusing function and non-linear confusing function.
+Denoting the key addition layer as $K_f(x)$, the linear layer as $L_f(x)$, and the non-linear layer as $N_f(x)$, the following composed function is iterated ROUND COUNT \todo{Insert round count} number of times:
+
+\begin{align}
+   N(L(K(m)))
+\end{align}
+
+The key addition layer adds the words of the key to the words of the state using exclusive-or. \todo{How does the key act on the state?}
+
+The linear layer is computed as follows: \todo{How is the linear layer computed?}
+
+The non-linear layer consists of the application of the S-Box on W-bit sub-sections of the state. \todo{How is the S-Box applied? What word size? On columns or rows?}
 
@@
 
+The exclusive-or key addition layer is standard and is used in many if not most (modern) cipher designs \todo{Is the key addition layer just XOR?} .
+This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate.\\
+
+The key scheduling algorithm was designed for the following reasons: \todo{Is there a key schedule? Why was the key schedule designed the way it was?}
+
+The linear layer is structured some way for certain reasons \todo{Why/How does it provide diffusion? Does it accomplish anything other then diffusion?}
+
+The S-Box was selected according to the following critera: \todo{How was the S-Box selected?}
+
+The constants were generated via the following function: .\todo{How were the constants generated?
+Or, how was the function that generates the constants selected?} Addition of different constants each round should provide resistance to slide attacks.
+\todo{Do the constants accomplish anything else?
+Is any other symmetry (i.e rotational symmetry) present without them?}
+
 \section{Conclusion}
- We define an N-bit block cipher with a K-bit key that is oriented towards PLATFORM TYPE. \todo{Fill in values for block size/key size and platform type} 
+ We define an N-bit Substitution-Permutation based block cipher with a K-bit key that is oriented towards PLATFORM TYPE. \todo{Fill in values for block size/key size and platform type} 
 \todo{Concisely summarize the rest of the paper in a paragraph or two}

### 2017-03-10 C/3417/blockcipher.c

@@ -15,7 +15,7 @@
 #define shift_rows(b, c, d, r0, r1, r2)({b = rotate_left(b, r0); c = rotate_left(c, r1); d = rotate_left(d, r2);})
 #define mix_columns(a, b, c, d)({a ^= d; b ^= c; c ^= a; d ^= b;})
 #define shift_and_mix(a, b, c, d, r0, r1, r2)({shift_rows(b, c, d, r0, r1, r2); mix_columns(a, b, c, d);})
-#define sbox(a, b, c, d)({t = a; a = (a & b) ^ c; c = (b & c) ^ d; d = (d & a) ^ t; b ^= c & t;})
+#define sbox(a, b, c, d)({t = a; a = (a & b) ^ c; c = (b | c) ^ d; d = (d & a) ^ t; b ^= c & t;})
 #define round_function(a, b, c, d, round_number)({\
     a ^= generate_constant(round_number);\
     shift_and_mix(a, b, c, d, 1, 2, 3);\

### 2017-03-10 designs/blockcipher/arx/2/encrypt.py

@@ -1,0 +1,137 @@
+ROUNDS = 4              # 2 ** (-differential_probability * active_sboxes) == 2 ** (-2 * 64) == (2 ** -128) ?
+KEY_ADDITION_LAYERS = 4 # minimum of 4: https://eprint.iacr.org/2013/391.pdf "...block ciphers based on the EM scheme with one key should have at least 4 rounds ..."
+
+def rotate_left(word, amount):
+    return ((word << amount) | (word >> (64 - amount))) & 0xFFFFFFFFFFFFFFFF
+        
+def generate_round_constant(word): # 10 instructions
+    word ^= rotate_left(word, 3)
+    word ^= rotate_left(word, 6)
+    word ^= rotate_left(word, 17)
+    word ^= rotate_left(word, 15)
+    word ^= rotate_left(word, 24)
+    return word
+    
+def shift_rows(b, c, d, r1, r2, r3): # 3 instructions
+    b = rotate_left(b, r1)
+    c = rotate_left(c, r2)    
+    d = rotate_left(d, r3)
+    return b, c, d
+    
+def mix_columns(a, b, c, d): # 4 instructions
+    a ^= d # ad
+    b ^= c # bc
+    c ^= a # acd
+    d ^= b # bcd
+    return a, b, c, d
+                
+def shift_and_mix(a, b, c, d, r1, r2, r3):    # 7 instructions =    
+    b, c, d = shift_rows(b, c, d, r1, r2, r3) # 3 instructions + 
+    return mix_columns(a, b, c, d)            # 4 instructions 
+    
+def sbox(a, b, c, d): # 9 instructions 
+    """ Optimal 4x4 s-box implementation; Applies 64 s-boxes in parallel on the columns. """                        
+    t = a    
+    a = (a & b) ^ c
+    c = (b | c) ^ d
+    d = (d & a) ^ t
+    b ^= c & t        
+    return a, b, c, d  
+        
+def linear_layer(a, b, c, d):    
+    a, b, c, d = shift_and_mix(a, b, c, d, 1, 2, 3) # each 4x4 subsection is active      # 7
+    a, b, c, d = shift_and_mix(a, b, c, d, 4, 8, 12) # each 16x4 subsection is active    # 7
+    a, b, c, d = shift_and_mix(a, b, c, d, 16, 32, 48) # each 64x4 subsection is active  # 7   
+    return a, b, c, d
+    
[…]

### 2017-03-14 latex/algorithmdesign/untitled-4.tex
finally made a 512-bit permutation

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{Brief Article}
\author{The Author}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\section{First section}

Meet Bob and Alice. Bob and Alice are pen pals; they write letters to each other, and send them through the mail. Additionally, we will introduce Eve:  Eve has no respect for others, as well as a pathological need to try and do wrong; She is not opposed to lying, cheating, and stealing, and is very creative in this arts. She will go to great length to do these things if she thinks it will benefit her; Even when there is no real benefit to her, she will do such things whenever she can get away with it, simply because she can.

Unfortunately, Eve is the mail carrier. Fortunately, Bob and Alice are aware of Eve's nature, and they seek to find ways of communicating with each other without Eve interfering. In order to do so, they need to enumerate all of the ways that Eve could abuse their communications, and develop appropriate counter-measures.

\subsection{Lying, Cheating, and Stealing}

The first and most obvious concern is Eve opening and reading the messages that are exchanged between Bob and Alice.

Second, and slightly more devious, is that Eve could manipulate messages sent between the two.

Third, Eve actually does not have to wait for Bob to actually send a letter to Alice. She can simply write her own letter, put Bob's name on it, and deliver it to Alice.

Fourth, she could withhold or make copies of messages, and save them for delivery at some other arbitrary point in time.

Finally, Eve could simply choose not to deliver the messages at all.

\subsection{Solutions}

For example, Bob might send Alice a christmas card with money inside, and a note that says "I am sending you \$20; I hope you have a nice holiday". Upon opening this, Eve could simply take the money, and leave a new note in the card that say "Sorry, I can't afford gifts this year; I hope you have a nice holiday anyways. PS: Please send me some money". Then she could easily repeat this process.

\end{document}

### 2017-03-14 C/31017/encrypt.c

@@ -1,0 +1,53 @@
+#define WORDSIZE unsigned long
+#define KEY_ADDITION_LAYERS 4
+#define rotate_left(a, amount)((a << amount) | (a >> (32 - amount)))
+
+#define gen_constant(word){\
+    t = word;\
+    t ^= rotate_left(t, 3);\
+    t ^= rotate_left(t, 6);\
+    t ^= rotate_left(t, 13);\
+    t ^= rotate_left(t, 8);}
+        
+#define shift_rows(b, c, d, r1, r2, r3){\
+    b = rotate_left(b, r1);\
+    c = rotate_left(c, r2);\
+    d = rotate_left(d, r3);}
+
+#define mix_columns(a, b, c, d){\
+    t = a;\
+    a = (a & b) ^ c;\
+    c = (b | c) ^ d;\
+    d = (d & a) ^ t;\
+    b = b ^ (c & t);}
+
+#define mix(a, b, c, d, r1, r2, r3){\
+    mix_columns(a, b, c, d);\
+    shift_rows(b, c, d, r1, r2, r3);}
+    
+#define add_key(a, b, c, d, k0, k1, k2, k3){a ^= k0; b ^= k1; c ^= k2; d ^= k3;}
+#define load(data, a, b, c, d){a = data[0]; b = data[1]; c = data[2]; d = data[3];}
+#define store(data, a, b, c, d){data[0] = a; data[1] = b; data[2] = c; data[3] = d;}
+        
+#define round_function(a, b, c, d, round_number){\
+    gen_constant(round_number);\
+    a ^= t;\
+    mix(a, b, c, d, 1, 2, 3);\
+    mix(a, b, c, d, 4, 8, 12);\
+    mix(a, b, c, d, 8, 12, 16);}
+    
+void encrypt(WORDSIZE* data, WORDSIZE* key){
+    unsigned int key_number;
+    WORDSIZE a, b, c, d, k0, k1, k2, k3, t;
+    load(data, a, b, c, d);
+    load(key, k0, k1, k2, k3);
+    for (key_number = 0; key_number < KEY_ADDITION_LAYERS; key_number++){
+        add_key(a, b, c, d, k0, k1, k2, k3);        
+        round_function(a, b, c, d, ((4 * key_number) + 1));               
+        round_function(a, b, c, d, ((4 * key_number) + 2));                
+        round_function(a, b, c, d, ((4 * key_number) + 3));                
[…]

### 2017-03-14 designs/blockcipher/arx/3/encrypt.py

@@ -1,0 +1,108 @@
+ROUNDS = 5              # 2 ** (-differential_probability * active_sboxes) == 2 ** 
+KEY_ADDITION_LAYERS = 4 # minimum of 4: https://eprint.iacr.org/2013/391.pdf "...block ciphers based on the EM scheme with one key should have at least 4 rounds ..."
+
+def rotate_left(word, amount):
+    return ((word << amount) | (word >> (64 - amount))) & 0xFFFFFFFFFFFFFFFF
+        
+def generate_round_constant(word): # 10 instructions
+    word ^= rotate_left(word, 3)
+    word ^= rotate_left(word, 6)
+    word ^= rotate_left(word, 17)
+    word ^= rotate_left(word, 15)
+    word ^= rotate_left(word, 24)
+    return word
+    
+def shift_rows(b, c, d, r1, r2, r3): # 3 instructions
+    b = rotate_left(b, r1)
+    c = rotate_left(c, r2)    
+    d = rotate_left(d, r3)
+    return b, c, d
+    
+def mix_columns(a, b, c, d): # 9 instructions
+    """ Optimal 4x4 s-box implementation; Applies 64 s-boxes in parallel on the columns. """                        
+    t = a    
+    a = (a & b) ^ c
+    c = (b | c) ^ d
+    d = (d & a) ^ t
+    b ^= c & t        
+    return a, b, c, d  
+                
+def shift_and_mix(a, b, c, d, r1, r2, r3):    # 12 instructions = 
+    a, b, c, d = mix_columns(a, b, c, d)            # 9 instructions    
+    b, c, d = shift_rows(b, c, d, r1, r2, r3) # 3 instructions + 
+    return a, b, c, d
+                
+def round_function(a, b, c, d, round_number): # 47 instructions
+    a ^= generate_round_constant(round_number) # 11     
+    a, b, c, d = shift_and_mix(a, b, c, d, 1, 2, 3)              # 12   
+    a, b, c, d = shift_and_mix(a, b, c, d, 4, 8, 12)              # 12     
+    a, b, c, d = shift_and_mix(a, b, c, d, 16, 32, 48)              # 12     
+    return a, b, c, d
+                  
+def add_key(a, b, c, d, key):
+    a ^= key[0]; b ^= key[1]; c ^= key[2]; d ^= key[3];    
+    return a, b, c, d
+    
+def load(data):
+    a = data[0]; b = data[1]; c = data[2]; d = data[3];
+    return a, b, c, d
+    
+def store(data, a, b, c, d):
[…]

### 2017-03-14 designs/blockcipher/arx/3/encrypthw.py

@@ -1,0 +1,137 @@
+ROUNDS = 4              # 2 ** (-differential_probability * active_sboxes) == 2 ** 
+KEY_ADDITION_LAYERS = 4 # minimum of 4: https://eprint.iacr.org/2013/391.pdf "...block ciphers based on the EM scheme with one key should have at least 4 rounds ..."
+
+def rotate_left(word, amount):
+    return ((word << amount) | (word >> (64 - amount))) & 0xFFFFFFFFFFFFFFFF
+        
+def generate_round_constant(word): # 10 instructions
+    word ^= rotate_left(word, 3)
+    word ^= rotate_left(word, 6)
+    word ^= rotate_left(word, 17)
+    word ^= rotate_left(word, 15)
+    word ^= rotate_left(word, 24)
+    return word
+    
+def shift_rows(b, c, d, r1, r2, r3): # 3 instructions
+    b = rotate_left(b, r1)
+    c = rotate_left(c, r2)    
+    d = rotate_left(d, r3)
+    return b, c, d
+    
+def mix_columns(a, b, c, d): # 4 instructions
+    """ Optimal 4x4 s-box implementation; Applies 64 s-boxes in parallel on the columns. """                        
+    t = a    
+    a = (a & b) ^ c
+    c = (b | c) ^ d
+    d = (d & a) ^ t
+    b ^= c & t        
+    return a, b, c, d  
+                
+def shift_and_mix(a, b, c, d, r1, r2, r3):    # 7 instructions = 
+    a, b, c, d = mix_columns(a, b, c, d)            # 4 instructions    
+    b, c, d = shift_rows(b, c, d, r1, r2, r3) # 3 instructions + 
+    return a, b, c, d
+                
+def round_function(a, b, c, d, round_number): # 41 instructions (not counting loop)            
+    a ^= generate_round_constant(round_number) # 11     
+    a, b, c, d = shift_and_mix(a, b, c, d, 1, 2, 3)              # 9     
+    a, b, c, d = shift_and_mix(a, b, c, d, 4, 8, 12)              # 9     
+    a, b, c, d = shift_and_mix(a, b, c, d, 16, 32, 48)              # 9     
+    return a, b, c, d
+              
+def choice(a, b, c):
+    return c ^ (a & (b ^ c))
+    
+def choice_swap(a, b, c):
+    t = b
+    b = choice(a, b, c)
+    c = choice(a, c, t)
+    return b, c        
+        
[…]

### 2017-03-14 designs/streamcipher/arxstream.py

@@ -1,0 +1,71 @@
+from crypto.utilities import rotate_left, slide, bytes_to_words, words_to_bytes
+
+WORDSIZE = 32
+MASK = (2 ** WORDSIZE) - 1
+
+def mix_columns(a, b, c, d, mask=MASK):
+    a = (a + b) & mask
+    c = (c + d) & mask
+    b ^= c
+    d ^= a
+    return a, b, c, d
+    
+def shift_rows(b, c, d, r1, r2, r3, wordsize=WORDSIZE):
+    b = rotate_left(b, r1, wordsize)
+    c = rotate_left(c, r2, wordsize)
+    d = rotate_left(d, r3, wordsize)
+    return b, c, d
+    
+def mix_block(a, b, c, d):
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 1, 2, 3)
+    
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 4, 8, 12)
+
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 8, 12, 16)    
+    return a, b, c, d
+    
+def mix_blocks(block0, block1, block2, block3):    
+    for round in range(4):
+        block0 = mix_block(*block0)
+        block1 = mix_block(*block1)
+        block2 = mix_block(*block2)
+        block3 = mix_block(*block3)
+    
+    a0, b0, c0, d0 = block0    #a0, b3, c2, d1  
+    a1, b1, c1, d1 = block1    #a1, b0, c3, d2    
+    a2, b2, c2, d2 = block2    #a2, b1, c0, d3    
+    a3, b3, c3, d3 = block3    #a3, b2, c1, d0            
+    return ((a0, b3, c2, d1), (a1, b0, c3, d2), (a2, b1, c0, d3), (a3, b2, c1, d0)) 
+   
+def generate_key_stream(key, nonce, block_count):
+    for index, byte in enumerate(key):
+        nonce[index] ^= byte
+        
+    state = [block128 for block128 in slide(bytes_to_words(nonce, 4), 4)]    
+    output = []  
+    while len(output) < block_count:
+        for round in range(2):
+            state = mix_blocks(*state)
+        output.extend(state[0] + state[1] + state[2] + state[3])    
+    return words_to_bytes(output, 4)
+    
+def visualize_mix_block():
+    from crypto.analysis.visualization import test_4x32_function
[…]

### 2017-03-16 latex/algorithmdesign/cipherconstructions.tex
SIMD testing

--- 2017-03-14 latex/algorithmdesign/untitled-4.tex
@@
 
-\section{First section}
+\section{Cipher Constructions}
 
-Meet Bob and Alice.
-Bob and Alice are pen pals; they write letters to each other, and send them through the mail.
-Additionally, we will introduce Eve:  Eve has no respect for others, as well as a pathological need to try and do wrong; She is not opposed to lying, cheating, and stealing, and is very creative in this arts.
-She will go to great length to do these things if she thinks it will benefit her; Even when there is no real benefit to her, she will do such things whenever she can get away with it, simply because she can.
+The design of a cipher can be split into (at least) two parts: The cipher construction, and the core permutation.
+The two archetypal examples of cipher construction are the Feistel Network and Substiution-Permutation Network.
 
-Unfortunately, Eve is the mail carrier.
-Fortunately, Bob and Alice are aware of Eve's nature, and they seek to find ways of communicating with each other without Eve interfering.
-In order to do so, they need to enumerate all of the ways that Eve could abuse their communications, and develop appropriate counter-measures.
+In the former, the state is divided into two sections that are typically of equal size; A key is added to some side(s), then a core "randomizing" function is applied to one half to produce a key stream; This key stream is then combined with the other half, in order to encipher it.
+We can see then, that the core "randomizing function" is interchangeable within the Feistel Network construction.
 
-\subsection{Lying, Cheating, and Stealing}
+In a Substitution-Permutation network, the state is typically subdivided into many smaller sections.
+The algorithm typically consists of addition of a key layer, followed by at least one application of an invertible "randomizing" function applied to the entire state; This is repeated until a sufficient "security margin" is obtained.
+This construction can be modeled as the composition of two functions: The key addition function, and the application of the core permutation on the state.
+As in the Feistel Network, the core permutation is interchangeable within the Substitution-Permutation network construction.
 
-The first and most obvious concern is Eve opening and reading the messages that are exchanged between Bob and Alice.
+We can see then, that there are at least two, effectively separate aspects to cipher design: The cipher construction, and the core permutation.
+This work focuses on the former.
+While the core permutation is critical for resistance to generic attacks such as linear and differential cryptanalysis, there also exist generic attacks against the cipher constructions.
+Additionally, while the design of the permutation can be hugely influential on the performance of the algorithm, so too can the cipher construction.
 
-Second, and slightly more devious, is that Eve could manipulate messages sent between the two.
+\section{Construction Design Considerations}
 
-Third, Eve actually does not have to wait for Bob to actually send a letter to Alice. She can simply write her own letter, put Bob's name on it, and deliver it to Alice.
+First, the target platform needs to be established.
+What is ideal for constrained hardware is not necessarily ideal for a modern CPU.
+In addition to the target platform(s), the performance goals of the algorithm should be outlined: Is latency important, or is throughput for large messages important?
+Is it important to use as little (or much) RAM?
 
-Fourth, she could withhold or make copies of messages, and save them for delivery at some other arbitrary point in time.
+Less obvious concerns that are still very important include: Is resistance to side channel leakage minimized? Does it facilitate or impede attempts to implement counter-measures?
 
-Finally, Eve could simply choose not to deliver the messages at all.
+"The simple" - RC4 like (shuffling huge array of words)
 
-\subsection{Solutions}
+"The small" - 8-bit friendly/constrained device friendly.
 
-For example, Bob might send Alice a christmas card with money inside, and a note that says "I am sending you \$20; I hope you have a nice holiday".
-Upon opening this, Eve could simply take the money, and leave a new note in the card that say "Sorry, I can't afford gifts this year; I hope you have a nice holiday anyways.
-PS: Please send me some money".
-Then she could easily repeat this process.
+"The fast" - salsa like (SIMD with big registers)
+
+\subsection{A subsection}
+
+More text.
 

### 2017-03-16 latex/algorithmdesign/untitled-4.tex
SIMD testing

@@
 
-Unfortunately, Eve is the mail carrier.
+Unfortunately, Eve is the mail carrier, and is responsible for delivering messages to/from the pair.
 Fortunately, Bob and Alice are aware of Eve's nature, and they seek to find ways of communicating with each other without Eve interfering.
@@
 
-For example, Bob might send Alice a christmas card with money inside, and a note that says "I am sending you \$20; I hope you have a nice holiday".
-Upon opening this, Eve could simply take the money, and leave a new note in the card that say "Sorry, I can't afford gifts this year; I hope you have a nice holiday anyways.
-PS: Please send me some money".
-Then she could easily repeat this process.
+In order to preclude Eve's ability to read their messages, Bob and Alice realize they need some way to obscure the information such that only the intended recipient may recover the actual information from the transported information.
+They need some kind of set of steps that they can apply to their message that will: 1: Produce output that is meaningless, and 2: The steps can be undone by the intended receipient to recover the actual message.
+
+So clearly, they reason, they need some kind of technique that will allow the two of them be able to perform the steps, but nobody else (i.e.
+Eve) should be able to perform the steps.
+After some thought, they realize that if they can keep some part of the steps secret, and only the two of them know the secret steps, then clearly Eve will not be able perform the transformation and recover the message.
+The pair realize that Eve will go out of her way to attempt to figure out the secret steps, and that they will likely need to include many secrets; If they only use one secret, Eve could easily guess it.
+
+% communicating the coin flip
 

### 2017-03-16 latex/cipher_templates/blockcipher/arx/template.tex
SIMD testing

--- 2017-03-10 latex/cipher_templates/blockcipher/generic/template.tex
@@
 
+The ARX construction is one method for designing a block cipher.
+ARX based ciphers forego the use of lookup tables as a source of non-linearity, utilizing integer addition and boolean functions combined with rotations and xor to obtain the required source of "confusion".
+ARX designs are generally simple to implement without exposing timing based side channels.
+They tend to be efficient in software on a modern CPU, as many designs can utilize the parallelism offered by large registers and vectorized instructions.
+
 \todo{Explain the motivation for the design described here}

### 2017-03-16 designs/permutation/arxcalibur512.py

@@ -29,8 +29,11 @@ def mix_block(a, b, c, d):
     b, c, d = shift_rows(b, c, d, 8, 12, 16)    
     return [a, b, c, d]
 
+def generate_constant(counter):
+    return mix_block(*mix_block(counter, counter + 1, counter + 2, counter + 3))    
+    
 def add_constant(counter, block0, block1, block2, block3):
-    a, b, c, d = mix_block(*mix_block(counter, counter + 1, counter + 2, counter + 3))
+    a, b, c, d = generate_constant(counter)
     block0[0] ^= a
     block1[0] ^= b
     block2[0] ^= c

### 2017-03-25 C/3232017/paper/permutations.tex
backup

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

\usepackage{algpseudocode}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Anonymous\inst{1}}
\institute{City, State \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Permutation]{Permutation}

\begin{abstract}
  We define a permutation with an 512-bit block size. The design is oriented towards consumer CPUs, though it should be scalable across a wide variety of platforms. The design makes use of only constant time bitwise operations (XOR/AND/OR) and fixed rotations. 
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
 Psuedorandom permutations are a core building block of modern cryptography. They are utilized to create block ciphers in Substitution-Permutation networks, as well as to create hash functions via the Sponge construction. By separating the design of cipher and hash constructions from the design of permutations, we can simplify the responsibilities of each component. The permutation should produce a random output block for any given input block; This implies the requirement for resisting known generic distinguishing frameworks, such as linear and differential cryptanalysis.

We define a 512-bit permutation, which is large enough to instantiate a sponge construction. It is a bit-sliced SIMD design. We utilize the class 13 representative from the paper "Finding Optimal Bit-Sliced Representations of 4x4 S-Boxes" with minimal instruction cost. Additionally, we present a method for generating "good" constants at effectively no extra cost.

\section{Definitions}
We use $\oplus$ to denote XOR, $\land$ to denote AND, $\lor$ to denote OR, and $\lll$ to denote bitwise rotation left. We use $\Vert$ to indicate concatenation. \\

The state consists of 4 adjacent slices, where each slice consists of 4 32-bit words arranged in rows. We refer to each 4-bit high, 1-bit wide subsection of a slice as a column, and each 1-bit high, 32-bit wide subsection of a slice as a row. There are 32 columns per slice, for a total of 128 columns in the entire state. The top row of each slice collectively is referred to as $a$, the second row is referred to as $b$, the third row is referred to as $c$, and the bottom row of each slice is referred to as $d$. When a subscript is affixed, it indexes the slice; Slices are numbered $0, 1, 2, 3$ from front to back. $a_0$ means the top row of the first slice, $a_1$ means the top row of the second slice, etc.

We require the use of one temporary variable, which is referred to as $t$. We refer to the inputs to the constant generation function as $constantSeed$; When subscripted, the number indexes the slice.

\section{Algorithm}
Each slice is mixed in parallel according to the following steps:

\begin{algorithmic}
\Function{$permutation$}{$a, b, c, d$}
	\State $a \gets addConstant(a)$
	\State $a, b, c, d \gets linear(a, b, c, d)$
	\State $a, b, c, d \gets nonlinear(a, b, c, d)$
\EndFunction\\
\Function{$add\_constant$}{$a$}
	\State $a \gets a \oplus constantSeed$
	\State $constantSeed_0 \gets constantSeed_0 + 4$
	\State $constantSeed_1 \gets constantSeed_1 + 4$
	\State $constantSeed_2 \gets constantSeed_2 + 4$
	\State $constantSeed_3\gets constantSeed_3 + 4$
\EndFunction\\
\Function{$linear$}{$a, b, c, d$}
	\State $a, b, c, d \gets mix\_and\_shift(a, b, c, d, 1, 2, 3)$
	\State $a, b, c, d \gets mix\_and\_shift(a, b, c, d, 4, 8, 12)$
	\State $a, b, c, d, \gets mix\_and\_shift(a, b, c, d, 8, 12, 16)$
	\State $a, b, c, d \gets mix\_and\_shift(a, b, c, d, 1, 2, 3)$
	\State $a, b, c, d \gets mix\_and\_shift(a, b, c, d, 4, 8, 12)$
	\State $a, b, c, d, \gets mix\_and\_shift(a, b, c, d, 8, 12, 16)$	
\EndFunction
\Function{$mix\_and\_shift$}{$a, b, c, d, r1, r2, r3$}
	\State $a, b, c, d \gets mix\_columns(a, b, c, d)$
	\State$b, c, d \gets shift\_rows(b, c, d, r1, r2, r3)$
\EndFunction
\Function{$mix\_columns$}{$a, b, c, d$}
	\State $a \gets a \oplus b$
	\State $c \gets c \oplus d$
	\State $b \gets b \oplus c$
	\State $d \gets d \oplus a$
\EndFunction
\Function{$shift\_rows$}{$b, c, d, r1, r2, r3$}
	\State $b \gets b \lll r1$
	\State $c \gets c \lll r2$
	\State $d \gets d \lll r3$
\EndFunction\\
\Function{$nonlinear$}{$a, b, c, d$}
	\State $t \gets a$
	\State $a \gets (a \land b) \oplus c$
	\State $c \gets (c \lor b) \oplus d$
	\State $d \gets (d \land a) \oplus t$
	\State $b \gets b \oplus (c \land t)$
\EndFunction\\
\end{algorithmic}

This is followed by a sliding of the rows, such that the rows of the slices become mixed:

\begin{algorithmic}
\Function{$slide\_rows$}{$b, c, d$}
	\State $b \gets b_1 \Vert b_2 \Vert b_3 \Vert b_0$
	\State $c \gets c_2 \Vert c_3 \Vert c_0 \Vert c_1$	
	\State $d \gets d_3 \Vert d_0 \Vert d_1 \Vert d_2$
\EndFunction
\end{algorithmic}

\todo{Describe the layout of the state with pictures!}\\

\section{Design\ Rationale}
\subsection{Constants}
The addition of the round constant serves multiple purposes. Some attacks can exploit the fact that identical functions are used every round; Addition of the round constants ensures that the permutation is different each round, which may resist some attacks. The constants also break the rotational symmetry that would otherwise be present in such a bit sliced design.

The constants are derived by applying the linear diffusing function to a unique sequence of values (the "seed"). This offers numerous advantages: reduced code size, reduced degrees of freedom, and "good" constants with a high hamming distance. Additionally, we can receive these benefits for no extra computational cost by utilizing the linearity of the diffusing function:

\begin{align}
Linear(state \oplus constantSeed) \equiv Linear(state) \oplus Linear(constantSeed)
\end{align}

The constant seed is initialized with the values $1, 2, 3, 4$. After each generation of constants, the values are each incremented by $4$. The initial sequence is simply a counter that counts upwards, starting at $1$. We start at $1$ instead of $0$ because an all $0$ input to the linear function produces an all $0$ output, meaning no constant would be applied. The increment was chosen as $4$ instead of $1$ so that all the inputs to the constant generation function would be unique.

The constantSeed is only added to row $a$. The constant generated by $linear(constantSeed, 0, 0, 0)$ will cover the other rows as well.

It is not clear whether or not constants would  benefit from "confusion" or higher algebraic degree; As such, we have no reason to apply the S-Box during the constant generation process.

The constants are applied before the non-linear function, rather then after it. Doing so ensures both S-Box inputs and outputs are dependent on the round, rather then just the outputs. Additionally, adding the constants before application of the S-Box enables the constants to increase the algebraic degree of the output. This would not occur if they were added in via xor after the S-Box is applied.

\subsection{Linear layer}
The linear diffusion layer is designed to ensure an even and optimal distribution of bits across each slice of the state. The two applications of the set of mix and shift operations ensures maximum output differences and a high number of active s-boxes. Testing of the lowest weight states demonstrated a minimum number of 25 active s-boxes per slice per round of the permutation; These tests were not exhaustive, but covered the states that were most likely to produce the lowest number of active s-boxes.

The rotation amounts for shift rows were selected to spread the differences around as evenly and quickly as possible. This is easily demonstrated with a visual aide. \todo{visual aide!}

\subsection{Nonlinear S-Box}   %\cite{Finding Optimal Bit-Sliced representations of 4x4 S-Boxes}
We chose to utilize the non-linear function with the lowest known implementation cost; The selected S-Box can be implemented in just nine instructions. This scales very well with larger registers. Because it is computed discretely instead of via table lookup, it is resistant against timing based side channel attacks, which can practically break and otherwise theoretically secure algorithm.

Additionally, this choice offers total transparency: The algebraic structure is present for all to scrutinize; There does not appear to be any room to hide a backdoor of any kind.

\subsection{Slide Rows}
Some mechanism for obtaining diffusion between slices is clearly required. The slide rows method is an analogue to the tried and true shift rows method for providing diffusion. There effectively was no choice in selecting the rotation amounts - it must be some combination of rotations by 1, 2, and 3, so the simplest one was selected.

\section{Conclusion}
 We define an 512-bit permutation that is oriented towards consumer CPUs. We utilize a technique for efficiently generating high quality round constants for no computational expense.
\end{document}

### 2017-03-25 latex/cipher_templates/permutations/permutations.tex
backup

--- 2017-03-10 latex/cipher_templates/blockcipher/generic/template.tex
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Block Cipher]{Block Cipher}\todo{Keywords?}
+\keywords[Permutation]{Permutation}\todo{Keywords?}
 
 \begin{abstract}
-  We define a block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size.
+  We define a permutation with an N\todo{Block size?}-bit block size.
 The design is oriented towards PLATFORM TYPE\todo{Constrained Devices?
@@
 \section{Introduction}
- Block ciphers are a widely used component in many cryptography schemes.
-They can be used with a mode of operation to provide confidentiality (as well as authenticity and integrity) to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function.
-When required, block ciphers can be designed with a smaller state size (80-128 bits) then a hash or stream cipher (160 bits+), which can lead to smaller and less expensive hardware implementations.
-Block ciphers are a very versatile class of algorithm.
+ Psuedorandom permutations are a core building block of modern cryptography.
+They are utilized to create block ciphers in Substitution-Permutation networks, as well as to create hash functions via the Sponge construction.
+By separating the design of cipher and hash constructions from the design of permutations, we can simplify the responsibilities of each component.
+The permutation holds the responsibility to be designed to resist all known generic attack frameworks, such as linear and differential cryptanalysis.
 
@@
 \todo{Define the algorithm in detail}\\
-\todo{Describe the block cipher construction type, i.e. Feistel, SPN, Even-Mansour, ARX, etc}\\
+\todo{Describe the layout of the state}\\
 \todo{Define the round function or permutation}
@@
 \section{Conclusion}
- We define an N-bit block cipher with a K-bit key that is oriented towards PLATFORM TYPE. \todo{Fill in values for block size/key size and platform type} 
+ We define an N-bit permutation that is oriented towards PLATFORM TYPE. \todo{Fill in values for block size and platform type} 
 \todo{Concisely summarize the rest of the paper in a paragraph or two}

### 2017-03-25 C/32017/diffusiontest.py

@@ -1,0 +1,62 @@
+from crypto.utilities import rotate_left
+
+WORDSIZE_BITS = 8
+
+def sub_bytes(a, b, c, d):
+    t = a; a = (a & b) ^ c;  c = (b | c) ^ d; d = (d & a) ^ t; b ^= c & t;
+    return a, b, c, d
+    
+def shift_rows(b, c, d, r1, r2, r3, bits=WORDSIZE_BITS):
+    b = rotate_left(b, r1, bits)
+    c = rotate_left(c, r2, bits)
+    d = rotate_left(d, r3, bits)
+    return b, c, d
+    
+def mix(a, b, c, d, constant=[1], wordsize=WORDSIZE_BITS):
+    t = constant[0]
+    t ^= rotate_left(t, 1, wordsize)
+    constant[0] += 1        
+    a ^= t
+    #backup = (a, b, c, d)    
+    #a >>= 4
+    #b >>= 4
+    #c >>= 4
+    #d >>= 4
+    a, b, c, d = sub_bytes(a, b, c, d)
+    a ^= b; c ^= d; b ^= c; d ^= a;
+    b, c, d = shift_rows(b, c, d, 1, 2, 3)
+    a ^= b; c ^= d; b ^= c; d ^= a;
+    b, c, d = shift_rows(b, c, d, 2, 4, 6)
+    
+    #a ^= (b << 1) & 255
+    #b ^= (c << 2) & 255
+    #c ^= (d << 3) & 255
+    #d ^= (a << 4) & 255
+    #b, c, d = shift_rows(b, c, d, 1, 2, 3)
+    #a ^= b; c ^= d; b ^= c; d ^= a;
+    #a, b, c, d = sub_bytes(a, b, c, d)
+    #b, c, d = shift_rows(b, c, d, 2, 4, 6)
+    #a ^= b; c ^= d; b ^= c; d ^= a;
+    #output = [(a << 4) & 0xff, (b << 4) & 0xff, (c << 4) & 0xff, (d << 4) & 0xff]
+    #a, b, c, d = backup
+    #a &= 15
+    #b &= 15
+    #c &= 15
+    #d &= 15
+    #a, b, c, d = sub_bytes(a, b, c, d)
+    #b, c, d = shift_rows(b, c, d, 1, 2, 3)
+    #a ^= b; c ^= d; b ^= c; d ^= a;
+    #a, b, c, d = sub_bytes(a, b, c, d)
+    #b, c, d = shift_rows(b, c, d, 1, 2, 3)
[…]

### 2017-03-25 C/3232017/activesboxes.py

@@ -1,0 +1,226 @@
+import itertools
+from math import log
+
+from crypto.utilities import slide, rotate_left, integer_to_bytes, bytes_to_integer
+
+def next_bit_permutation(v, mask=0xFFFFFFFF):
+    t = (v | (v - 1)) + 1
+    return (t | ((((t & -t) / (v & -v)) >> 1) - 1)) & mask
+    
+def invert(word, mask=0xFFFFFFFF):
+    return word ^ mask
+    
+def bit_generator(seed_weight, mask=0xFFFFFFFF):    
+    _seed_weight = seed_weight    
+    while True:                
+        yield seed_weight    
+        if not seed_weight:            
+            break        
+        seed_weight = next_bit_permutation(seed_weight, mask)    
+
+def search_minimum_active_sboxes(permutation, test_inputs=[bit_generator(1) for count in range(4)], _counter=lambda: bit_generator(1),
+                                 word_size=32, chunk_size=65536, display_progress=True):    
+    last_outputs = permutation(0, 0, 0, 0)           
+    results = []
+    input_generator = itertools.product(*test_inputs)
+    chunks = 2 ** 20 / chunk_size
+    assert not 2 ** 20 % chunk_size
+    finished = False
+    progress = 0
+    while True:
+        for counter in range(chunk_size):
+            try:
+                inputs = next(input_generator)                  
+            except StopIteration:
+                finished = True
+                break
+            outputs = permutation(*inputs)
+            
+            active_sboxes = 0
+            a0, b0, c0, d0 = last_outputs
+            a1, b1, c1, d1 = outputs
+            for index in range(word_size):
+                mask = 1 << index                                
+                word0 = (a0 & mask) | ((b0 & mask) << 1) | ((c0 & mask) << 2) | ((d0 & mask) << 3)
+                word1 = (a1 & mask) | ((b1 & mask) << 1) | ((c1 & mask) << 2) | ((d1 & mask) << 3)                
+                if word0 != word1:
+                    active_sboxes += 1
+            results.append(active_sboxes)            
+            last_outputs = outputs
+        progress += 1
+        if finished:
+            break        
+        if display_progress:                      
+            print("\n" + ('-' * 79))
[…]

### 2017-03-25 C/3232017/permutation.c

@@ -16,7 +16,6 @@
 
 #define add_constant(a) ({load_register(t, round_constants, 0);\
                           round_constants[0] += 4; round_constants[1] += 4; round_constants[2] += 4; round_constants[3] += 4;\
-                          t ^= rotate_left(t, 3); t ^= rotate_left(t, 6); t ^= rotate_left(t, 13); t ^= rotate_left(t, 8);\
                           a ^= t;})
                            
 void permutation(WORDSIZE* state){    
@@ -26,28 +25,21 @@ void permutation(WORDSIZE* state){
     load_register(a, state, 0); load_register(b, state, 4); 
     load_register(c, state, 8); load_register(d, state, 12);           
     
-    for (index = 0; index < 16; index++){                     
-        add_constant(a);      
-        sub_bytes(a, b, c, d);
-                
-        shift_rows(b, c, d, 1, 2, 3);
-        mix_columns(a, b, c, d);
+    for (index = 0; index < 8; index++){                     
+        add_constant(a);                
         
+        for (index2 = 0; index2 < 2; index2++){              
+            mix_columns(a, b, c, d);
+            shift_rows(b, c, d, 1, 2, 3);
+            
+            mix_columns(a, b, c, d);
+            shift_rows(b, c, d, 4, 8, 12);
+            
+            mix_columns(a, b, c, d);
+            shift_rows(b, c, d, 8, 12, 16);}
         
-        shift_rows(b, c, d, 4, 8, 12);
-        mix_columns(a, b, c, d);
-                
-        shift_rows(b, c, d, 8, 12, 16);
-        mix_columns(a, b, c, d);    
-//        for (index2 = 0; index2 < 2; index2++){              
-//            mix_columns(a, b, c, d);
-//            shift_rows(b, c, d, 1, 2, 3);
-//            
-//            mix_columns(a, b, c, d);
-//            shift_rows(b, c, d, 4, 8, 12);
-//            
-//            mix_columns(a, b, c, d);
-//            shift_rows(b, c, d, 8, 12, 16);}
+        sub_bytes(a, b, c, d);            
+        
         shift_sections(b, c, d);}
         
     store_register(a, state, 0); store_register(b, state, 4);

### 2017-03-25 C/3232017/test.py

@@ -1,0 +1,31 @@
+from crypto.utilities import rotate_left
+
+def shift_rows(b, c, d, r1, r2, r3, mask=0xFFFFFFFF):
+    _b = _c = _d = 0
+    for count in range(4):
+        shift_amount = count * 32            
+        _b ^= rotate_left((b >> shift_amount) & mask, r1, 32) << shift_amount
+        _c ^= rotate_left((c >> shift_amount) & mask, r2, 32) << shift_amount
+        _d ^= rotate_left((d >> shift_amount) & mask, r2, 32) << shift_amount
+    return _b, _c, _d          
+
+def mix_columns(a, b, c, d):
+    # acd        
+    # bcd
+    # abc
+    # abd
+    #a ^= b; c ^= d; b ^= c; d ^= a; a ^= b; c ^= d;            
+    a ^= b; c ^= d; b ^= c; d ^= a; a ^= c; 
+    
+    return a, b, c, d
+    
+def permutation(a, b, c, d):
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 1, 2, 3)
+    
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 4, 8, 12)
+    
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 8, 12, 16)  
+    return a, b, c, d

### 2017-03-25 C/3242017/permutation.c

@@ -12,11 +12,13 @@
 #define mix_columns(a, b, c, d) {a ^= b; c ^= d; b ^= c; d ^= a;}
 #define rotate_left(word, bits) _mm_slli_epi32(word, bits) | _mm_srli_epi32(word, 32 - bits)
 #define shift_rows(b, c, d, r1, r2, r3)({b = rotate_left(b, r1); c = rotate_left(c, r2); d = rotate_left(d, r3);})
+#define mix_slice(a, b, c, d)({mix_columns(a, b, c, d); shift_rows(b, c, d, 1, 2, 3);\
+                               mix_columns(a, b, c, d); shift_rows(b, c, d, 4, 8, 12);\
+                               mix_columns(a, b, c, d); shift_rows(b, c, d, 8, 12, 16);})
+                               
 #define shift_sections(b, c, d) {b = _mm_shuffle_epi32(b, 0b01101100); c = _mm_shuffle_epi32(c, 0b10110001); d = _mm_shuffle_epi32(d, 0b11000110);}
-
 #define add_constant(a) ({load_register(t, round_constants, 0);\
                           round_constants[0] += 4; round_constants[1] += 4; round_constants[2] += 4; round_constants[3] += 4;\
-                          t ^= rotate_left(t, 3); t ^= rotate_left(t, 6); t ^= rotate_left(t, 13); t ^= rotate_left(t, 8);\
                           a ^= t;})
                            
 void permutation(WORDSIZE* state){    
@@ -26,29 +28,13 @@ void permutation(WORDSIZE* state){
     load_register(a, state, 0); load_register(b, state, 4); 
     load_register(c, state, 8); load_register(d, state, 12);           
     
-    for (index = 0; index < 16; index++){                     
-        add_constant(a);      
-        sub_bytes(a, b, c, d);
-                
-        shift_rows(b, c, d, 1, 2, 3);
-        mix_columns(a, b, c, d);
-        
-        
-        shift_rows(b, c, d, 4, 8, 12);
-        mix_columns(a, b, c, d);
-                
-        shift_rows(b, c, d, 8, 12, 16);
-        mix_columns(a, b, c, d);    
-//        for (index2 = 0; index2 < 2; index2++){              
-//            mix_columns(a, b, c, d);
-//            shift_rows(b, c, d, 1, 2, 3);
-//            
-//            mix_columns(a, b, c, d);
-//            shift_rows(b, c, d, 4, 8, 12);
-//            
-//            mix_columns(a, b, c, d);
[…]

### 2017-03-25 designs/permutation/3212017/permutation.py

@@ -1,0 +1,76 @@
+from crypto.utilities import rotate_left
+        
+def permutation(state):
+    mix_columns(state, 0)
+    mix_columns(state, 1)
+    mix_columns(state, 2)
+    mix_columns(state, 3)    
+  #  shift_rows(state)
+        
+def mix_columns(state, base_index):
+    a, b, c, d = state[base_index], state[base_index + 4], state[base_index + 8], state[base_index + 12]
+    
+    a, b, c, d = sbox(a, b, c, d)
+    b, c, d = rotate_words(b, c, d, 1, 2, 3)    
+    a ^= b; c ^= d; b ^= c; d ^= a;
+    
+   # a, b, c, d = sbox(a, b, c, d)
+    b, c, d = rotate_words(b, c, d, 2, 3, 4)    
+    a ^= b; c ^= d; b ^= c; d ^= a;    
+    
+    state[base_index], state[base_index + 4], state[base_index + 8], state[base_index + 12] = a, b, c, d
+    return a, b, c, d
+
+def sbox(a, b, c, d):    
+    t = a;
+    a = (a & b) ^ c
+    c = (b | c) ^ d
+    d = (d & a) ^ t
+    b ^= c & t
+    return a, b, c, d
+    
+def rotate_words(b, c, d, r1, r2, r3):
+    b = rotate_left(b, r1, 8)
+    c = rotate_left(c, r2, 8)
+    d = rotate_left(d, r3, 8)  
+    return b, c, d    
+        
+def shift_rows(state):
+    #  0  1  2  3
+    #  4  5  6  7
+    #  8  9 10 11
+    # 12 13 14 15
+    
+    t = state[4];
+    state[4] = state[5];
+    state[5] = state[6];
+    state[6] = state[7];
+    state[7] = t;
+    
+    t, t2 = state[8], state[9]
+    state[8], state[9] = state[10], state[11]
+    state[10], state[11] = t, t2
+    
+    t = state[15]
+    state[15] = state[14]
+    state[14] = state[13]
+    state[13] = state[12]
+    state[12] = t
+    
+def visualize_permutation():
+    from crypto.analysis.visualization import test_4x4x8_function
+    state = [0] * 16
+    state[3] = 1
+    
+    def test_function(*args):
+        state = list(args)
+        permutation(state)
+        return state
+    test_4x4x8_function(test_function, state)
+    
+if __name__ == "__main__":
+    visualize_permutation()
+    
+    
+    
+    

### 2017-03-25 designs/permutation/revisited.py

@@ -1,0 +1,52 @@
+from crypto.utilities import rotate_left, xor_sum
+
+WORDSIZE = 8
+
+def branch(word):
+    word ^= rotate_left(word, 3)
+    word ^= rotate_left(word, 6)
+    return word
+        
+def choice(a, b, c):
+    return c ^ (a & (b ^ c))
+    
+def choice_swap(k, a, b):
+    t = a
+    a = choice(k, a, b)
+    b = choice(k, b, t)
+    return a, b               
+        
+def permutation(state, sbox, wordsize=WORDSIZE, cache=[branch(index) for index in range(32)]):    
+    assert len(state) < 32    
+    _sum = xor_sum(state) # 16
+    size = len(state)
+    for index in range(size):
+        #for index2 in range(index, size):
+        #    word0, word1 = state[index], state[index2]
+        #    _sum ^= word0 ^ word1
+        #    word0, word1 = choice_swap(_sum, word0, word1)
+        #    state[index] = rotate_left(sbox[word0 ^ cache[index]], 1, wordsize)
+        #    state[index2] = sbox[rotate_left(word1, 1, wordsize) ^ cache[index2]]
+        #    _sum ^= state[index] ^ state[index2]
+            
+            
+        byte = state[index]
+        state[index] = sbox[_sum ^ cache[index]] # 3
+        _sum = rotate_left(sbox[_sum ^ byte ^ state[index]], 1, wordsize) # 4
+                    
+            
+    #print state        
+    
+def test_permutation():
+    from crypto.analysis.metrics import test_permutation
+    from crypto.designs.blockcipher.standardized.aes_procedures import S_BOX
+        
+    def test_function(data):
+        data = bytearray(data)
+        permutation(data, S_BOX)
+        return bytes(data)
+    test_permutation(test_function, 16, avalanche_test=False, randomness_test=False)
+                
+if __name__ == "__main__":
+    test_permutation()
+    

### 2017-03-25 utilities.py

@@ -35,11 +35,11 @@ def rotate(input_string, amount):
         amount = amount % len(input_string)
         return input_string[-amount:] + input_string[:-amount]                
 
-def rotate_right(x, r, bit_width=8, _mask=dict((bit_width, ((2 ** bit_width) - 1)) for bit_width in (8, 16, 32, 64, 128))): 
+def rotate_right(x, r, bit_width=8, _mask=dict((bit_width, ((2 ** bit_width) - 1)) for bit_width in (2, 4, 8, 16, 32, 64, 128))): 
     r %= bit_width
     return ((x >> r) | (x << (bit_width - r))) & _mask[bit_width]
     
-def rotate_left(x, r, bit_width=8, _mask=dict((bit_width, ((2 ** bit_width) - 1)) for bit_width in (8, 16, 32, 64, 128))):  
+def rotate_left(x, r, bit_width=8, _mask=dict((bit_width, ((2 ** bit_width) - 1)) for bit_width in (2, 4, 8, 16, 32, 64, 128))):  
     r %= bit_width
     return ((x << r) | (x >> (bit_width - r))) & _mask[bit_width]
     

### 2017-04-13 latex/keyexchange/paper.tex
added rsareuse idea

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Anonymous\inst{1}}
\institute{City, State \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Key Exchange]{Key Exchange}\todo{Keywords?}

\begin{abstract}
  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\ 
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
 The ability to exchange cryptographic keys over insecure channels is of vital importance to the function of the internet; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.\\

The introduction of Quantum Computing and post-quantum cryptography has lead to the development of lattice based cryptographic schemes that are believed to be secure even when faced with quantum parallelism. Simply put, RSA and DH will need replacement at some point, and lattices seem like a promising alternative.

Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment. This property is also extremely important because it allows for the simple construction of public key encryption schemes and key exchange shemes from secret key ciphers. We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.

\section{Definitions}
We use $+$ to denote addition, $ab$ to denote multiplication, and $\mod p$ to denote the modulo operation.

\section{Algorithm}
First, we shall define the key exchange algorithm; Then, we shall define a secret key cipher suitable for instantiating the key exchange algorithm.

\subsection{Key Exchange Algorithm}
Let $pb_1$ and $pb_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
\begin{align}
    e \gets secret \\
    c \gets (pb_1  r_1) + (pb_2 r_2) + e
\end{align}

Then the value $c$ is shared with the owner of the public key. The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $pb_1$ is an encryption of $0$, $pb_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $pb_2$. So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.

\subsection{Secret Key Cipher}
Creation of the $pb_1$ and $pb_2$ values requires a secure, additively homomorphic cipher. We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process. Let $p_1$ and $p_2$ be two large numbers, where $log_2(p_1) >= log_2(p_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\

To encrypt a ciphertext, compute:

\begin{align}
   c \gets (p_1 r_1) + (p_2 r_2) + m
\end{align}

Where the $r$ values are of appropriate size relative to $p_1$ and $p_2$ \todo{what sizes are appropriate}
While decryption is computed as:

\begin{align}
    m \gets (c \mod p_1) \mod p_2
\end{align}

\subsection{Note}
While the decryption circuit works via two modulo operations of the base points of the lattice, this operation does not work for the public key/key exchange portion of the algorithm - The reason is because in the secret key cipher, the two different lattice points are of largely different size; In the key exchange algorithm, both points are roughly the same size, and so the double modulo operation does not function identically.

\section{Conclusion}
 We define a simple lattice based key exchange algorithm. The algorithm utilizes 2 bignum multiplications and 2 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key. Public keys typically occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
\end{document}

### 2017-04-13 latex/secretkeybasedpublickeyencryption/paper.tex
added rsareuse idea

--- 2017-04-13 latex/keyexchange/paper.tex
@@
 Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment.
-This property is also extremely important because it allows for the simple construction of public key encryption schemes and key exchange shemes from secret key ciphers.
+This property is also extremely important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers.
 We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.

### 2017-04-13 designs/homomorphic/latticebased/keyexchange.py

@@ -11,31 +11,46 @@ def generate_public_key(private_key, encryption_function=secretkey.encrypt):
     return pb1, pb2
     
 def generate_keypair():
-    private_key = generate_private_key()
+    private_key = generate_private_key()    
     public_key = generate_public_key(private_key)
-    return public_key, private_key
+    _public_key = randomize_public_key(public_key)
+    assert _public_key != public_key
+    return _public_key, private_key
     
 def exchange_key(random_secret, public_key, r_size=SECRET_SIZE):    
     pb1, pb2 = public_key
-    r1, r2 = secretkey.random_integer(r_size), secretkey.random_integer(r_size)
-    return (pb1 * r1) + (pb2 * r2) + random_secret
+    r1, r2 = secretkey.random_integer(r_size), secretkey.random_integer(r_size - 8)
+    return ((pb1 * r1) - (pb2 * r2)) + random_secret
     
 def recover_key(ciphertext, private_key, decryption_function=secretkey.decrypt):    
     return decryption_function(ciphertext, private_key)
+      
+from math import log      
+def _randomize_key(key, r = lambda: secretkey.random_integer(8)):
+    _key = (key * r()) - (key * r()) + (key * r()) + (key * r())           
+    while _key < 0 or log(_key, 2) > 1200: # re-roll if it's negative or too big
+        _key = (key * r()) - (key * r()) + (key * r()) + (key * r())          
+    return _key
     
+def randomize_public_key(public_key):
+    pub1, pub2 = public_key
+    pub1 = _randomize_key(pub1)
+    pub2 = _randomize_key(pub2)    
+    assert pub1 > 0 and pub2 > 0, (pub1, pub2)
+    return pub1, pub2        
+        
 def test_exchange_key_recover_key():    
-    public_key, private_key = generate_keypair()    
+    public_key, private_key = generate_keypair()   
+    hamming_weight = lambda number: format(number, 'b').count('1')
+    print("Public key size : {} + {} = {}".format(hamming_weight(public_key[0]), hamming_weight(public_key[1]), sum(hamming_weight(item) for item in public_key)))
+    print("Private key size: {}".format(sum(hamming_weight(item) for item in private_key)))        
     for counter in range(65536):
         message = secretkey.random_integer(32)
         ciphertext = exchange_key(message, public_key)    
         plaintext = recover_key(ciphertext, private_key)
-        assert plaintext == message, (plaintext, message)
-    
-    hamming_weight = lambda number: format(number, 'b').count('1')
[…]

### 2017-04-13 utilities.py

@@ -391,14 +391,26 @@ def test_integer_to_words_words_to_integer():
 def random_integer(size_in_bytes):
     return bytes_to_integer(bytearray(os.urandom(size_in_bytes)))
     
-def big_prime(size_in_bytes, test_count=256):    
+def _generate_prime_test_n(amount):    
+    prime_test_n = 1    
+    generator = prime_generator()
+    for item in (next(generator) for count in range(amount)):
+        prime_test_n *= item
+    return prime_test_n
+    
+def big_prime(size_in_bytes, test_count=1024, prime_test_n=[None]):
+    if prime_test_n[0] is None:
+        prime_test_n[0] = _generate_prime_test_n(test_count)
+    test_number = prime_test_n[0]        
     while True:
-        candidate = random_integer(size_in_bytes)
-        for test_number in (random_integer(size_in_bytes) for count in range(test_count)):
-            if gcd(candidate, test_number) != 1:
-                candidate = random_integer(size_in_bytes)
-                break
-        else:
+        candidate = random_integer(size_in_bytes)        
+        if gcd(candidate, test_number) == 1 and candidate != 1:
             return candidate
+        #for test_number in (random_integer(size_in_bytes) for count in range(test_count)):
+        #    if gcd(candidate, test_number) != 1:
+        #        candidate = random_integer(size_in_bytes)
+        #        break
+        #else:
+        #    return candidate
         
         

### 2017-04-13 latex/keyexchange/secretkeybasedpublickeyencryption.tex
noted ability to re-use RSA keypairs

--- 2017-04-13 latex/secretkeybasedpublickeyencryption/paper.tex
@@
 
-\author{Anonymous\inst{1}}
-\institute{City, State \email{address@provider.com}}
+\author{Ella Rose\inst{1}}
+\institute{Paso Robles, CA \email{address@provider.com}}
 \title[\texttt Design date]{\texttt Design date}
@@
   We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas.
-The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\
+The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.
+Additionally, it is possible to utilize pre-existing RSA keypairs to perform the exchange.
+While doing so does not increase security beyond that of regular RSA, it is much faster.\\
 \end{abstract}
@@
 \subsection{Key Exchange Algorithm}
-Let $pb_1$ and $pb_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
+Let $p_1$ and $p_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
 \begin{align}
     e \gets secret \\
-    c \gets (pb_1  r_1) + (pb_2 r_2) + e
+    c \gets (p_1  r_1) + (p_2 r_2) + e
 \end{align}
@@
 Then the value $c$ is shared with the owner of the public key.
-The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $pb_1$ is an encryption of $0$, $pb_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $pb_2$.
+The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$.
 So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.
@@
 \subsection{Secret Key Cipher}
-Creation of the $pb_1$ and $pb_2$ values requires a secure, additively homomorphic cipher.
+Creation of the $p_1$ and $p_2$ values requires a secure, additively homomorphic cipher.
 We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process.
-Let $p_1$ and $p_2$ be two large numbers, where $log_2(p_1) >= log_2(p_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\
+Let $s_1$ and $s_2$ be two large numbers, where $log_2(s_1) >= log_2(s_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\
 
@@
 \begin{align}
-   c \gets (p_1 r_1) + (p_2 r_2) + m
+   c \gets (s_1 r_1) + (s_2 r_2) + m
 \end{align}
 
-Where the $r$ values are of appropriate size relative to $p_1$ and $p_2$ \todo{what sizes are appropriate}
+Where the $r$ values are of appropriate size relative to $s_1$ and $s_2$ \todo{what sizes are appropriate}
 While decryption is computed as:
@@
 \begin{align}
-    m \gets (c \mod p_1) \mod p_2
+    m \gets (c \mod s_1) \mod s_2
 \end{align}
@@
 
+\subsection{Re-using RSA keypairs for the exchange}
+An RSA modulus can be used as a public key for the exchange presented previously; Simply substitute the RSA public key $n$ in place of the points $p_1$ and $p_2$, and modify the decryption algorithm to utilize a single modulo $p$ (as in the $p$ from $pq == n$).
+While this does not offer a security advantage to regular RSA encryption (here we offer no proof of security of any kind), it is significantly faster.
+Performing 1024 key exchanges using naive/textbook RSA-2048 requires approximately 1 second on our test machine; Performing 1024 key exchanges using the RSA-Lattice technique requires about .25 seconds on our test machine.
+This is largely the result of not needing to perform modular exponentiation with the lattice based technique.
+
 \section{Conclusion}
  We define a simple lattice based key exchange algorithm.
-The algorithm utilizes 2 bignum multiplications and 2 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key.
-Public keys typically occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
+The algorithm utilizes 4 bignum multiplications and 4 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key.
+Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
+Interestingly, pre-existing RSA keypairs may be used to instantiate the shceme.
 \end{document}

### 2017-04-14 latex/keyexchange/secretkeybasedpublickeyencryption.tex
broke it!
that was fast!
improved randomize_public_key

@@
 \author{Ella Rose\inst{1}}
-\institute{Paso Robles, CA \email{address@provider.com}}
-\title[\texttt Design date]{\texttt Design date}
+\institute{Paso Robles, CA \email{python_pride@protonmail.com}}
+\title[\texttt Lattice Based Key Exchange]{\texttt Lattice Based Key Exchange}
 
@@
   We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas.
-The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.
-Additionally, it is possible to utilize pre-existing RSA keypairs to perform the exchange.
-While doing so does not increase security beyond that of regular RSA, it is much faster.\\
+The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\
 \end{abstract}
@@
 
-Then the value $c$ is shared with the owner of the public key.
+Where $r_1$ and $r_2$ are randomly generated values of appropriate size.\todo{What sizes are appropriate?} Then the value $c$ is shared with the owner of the public key.
 The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$.
@@
 
-\subsection{Re-using RSA keypairs for the exchange}
-An RSA modulus can be used as a public key for the exchange presented previously; Simply substitute the RSA public key $n$ in place of the points $p_1$ and $p_2$, and modify the decryption algorithm to utilize a single modulo $p$ (as in the $p$ from $pq == n$).
-While this does not offer a security advantage to regular RSA encryption (here we offer no proof of security of any kind), it is significantly faster.
-Performing 1024 key exchanges using naive/textbook RSA-2048 requires approximately 1 second on our test machine; Performing 1024 key exchanges using the RSA-Lattice technique requires about .25 seconds on our test machine.
-This is largely the result of not needing to perform modular exponentiation with the lattice based technique.
-
 \section{Conclusion}
@@
 Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
-Interestingly, pre-existing RSA keypairs may be used to instantiate the shceme.
 \end{document}

### 2017-04-14 designs/homomorphic/latticebased/keyexchange.py

@@ -1,41 +1,74 @@
+from math import log  
+
 import secretkey
 
+__all__ = ["generate_keypair", "randomize_public_key", "exchange_key", "recover_key",
+           "generate_private_key", "generate_public_key"]
+           
 SECRET_SIZE = 32
 
 def generate_private_key(key_generation_function=secretkey.generate_key):
+    """ usage: generate_private_key(key_generation_function=secretkey.generate_key) => private_key
+    
+        Generates a private key, which is the key for a secret key homomorphic cipher. """
     return key_generation_function()
     
 def generate_public_key(private_key, encryption_function=secretkey.encrypt):
+    """ usage: generate_public_key(private_key, 
+                                   encryption_function=secretkey.encrypt) => public_key
+                                   
+        Returns two encryptions of 0, suitable for use as a public key. """
     pb1 = encryption_function(0, private_key)
     pb2 = encryption_function(0, private_key)
     return pb1, pb2
     
 def generate_keypair():
+    """ usage: generate_keypair(): => public_key, private_key
+    
+        Generates a public key and a private key.
+        A public key consists of 2 different numbers, which are both homomorphic encryptions of 0.
+        The nature of the private key depends on the secret key cipher that is used to instantiate the scheme. """
     private_key = generate_private_key()    
     public_key = generate_public_key(private_key)
     _public_key = randomize_public_key(public_key)
     assert _public_key != public_key
     return _public_key, private_key
     
-def exchange_key(random_secret, public_key, r_size=SECRET_SIZE):    
+def exchange_key(random_secret, public_key, r_size=SECRET_SIZE): 
+    """ usage: exchange_key(random_secret, public_key,
+                            r_size=SECRET_SIZE) => encrypted random_secret
+                            
+        Creates a ciphertext from random_secret that only the holder of the private key may recover the plaintext from. """        
     pb1, pb2 = public_key
     r1, r2 = secretkey.random_integer(r_size), secretkey.random_integer(r_size)
     return ((pb1 * r1) + (pb2 * r2)) + random_secret
     
 def recover_key(ciphertext, private_key, decryption_function=secretkey.decrypt):    
-    return decryption_function(ciphertext, private_key)
-      
-from math import log      
+    """ usage: recover_key(ciphertext, private_key, 
+                           decryption_function=secretkey.decrypt) => random_secret
[…]

### 2017-04-14 designs/homomorphic/latticebased/rsareuse.py

@@ -1,6 +1,5 @@
-""" You can use an unmodified RSA keypair to do a lattice based key exchange.
-    Does not modify keys; Still vulnerable to factorization.
-    But it is much faster. """
+# broken!
+
 from crypto.utilities import big_prime, modular_inverse, random_integer
 
 def random_rsa_key(size):
@@ -58,7 +57,7 @@ def test_rsa_lattice_exchange_recover():
     #print c
     s = rsa_lattice_recover(c, p)
     _s = c % n
-    assert _s != s
+    assert _s != s # dang
     assert s == r, (s, r)
 
     from timeit import default_timer as timer    

### 2017-04-14 designs/homomorphic/latticebased/secretkey.py

@@ -1,11 +1,22 @@
 from os import urandom
+from fractions import gcd
 
-from crypto.utilities import gcd, random_integer
-    
 P1_SIZE = 110
 P2_SIZE = 36
 R_SIZE = 32
-  
+
+# utilities
+def bytes_to_integer(data):
+    output = 0    
+    size = len(data)
+    for index in range(size):
+        output |= data[index] << (8 * (size - 1 - index))
+    return output
+    
+def random_integer(size_in_bytes):
+    return bytes_to_integer(bytearray(urandom(size_in_bytes)))
+    
+# algorithm    
 def generate_key(p1_size=P1_SIZE, p2_size=P2_SIZE):
     p1 = random_integer(p1_size)
     p2 = random_integer(p2_size)
@@ -25,6 +36,7 @@ def decrypt(ciphertext_integer, secret_key):
     p1, p2 = secret_key
     return (ciphertext_integer % p1) % p2    
     
+# unit test    
 def test_encrypt_decrypt():    
     secret_key = generate_key()           
     for m in range(256):                    

### 2017-04-17 latex/permutorconstruction/permutations.tex
improved permutation encryption construction

--- 2017-03-25 latex/cipher_templates/permutations/permutations.tex
@@
 
-\author{Anonymous\inst{1}}
-\institute{City, State \email{address@provider.com}}
-\title[\texttt Design date]{\texttt Design date}
+\author{Ella Rose\inst{1}}
+\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
+\title[\texttt 4-16-17]{\texttt 4-16-17}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Permutation]{Permutation}\todo{Keywords?}
+\keywords[Permutation, Cipher Construction, AEAD]{Permutation, Cipher Construction, AEAD}\todo{Keywords?}
 
 \begin{abstract}
-  We define a permutation with an N\todo{Block size?}-bit block size.
-The design is oriented towards PLATFORM TYPE\todo{Constrained Devices?
-Consumer CPUs?
-What architecture/native word sizes?}.
-The design makes use of certain instruction types or gates.
-\todo{XOR/AND?
-ADD/XOR?
-Multiplication?
-Modular Exponentiation?
-Lookup Tables?}\\
+ We define a permutation based construction for providing single pass authenticated encryption of data.
+Our specific definition recommends a 512-bit permutation and a 256-bit key to encrypt a 256-bit block of data.
+Our construction is very simple and easy to implement; It should be significantly less code then a block cipher with a mode of operation and HMAC.
+It is generic, and can be instantiated with any psuedorandom permutation.
 \end{abstract}
@@
 
-\todo{Explain the motivation for the design described here}
+In this work we present a construction that utilizes a psuedorandom permutation to create a simple streaming authenticated encryption system.
 
@@
 \todo{Define how the state is laid out and indexed/addressed}\\
-We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left...
+We use $\oplus$ to denote XOR and $||$ to denote concatenation.
 
 \section{Algorithm}
-\todo{Define the algorithm in detail}\\
-\todo{Describe the layout of the state}\\
-\todo{Define the round function or permutation}
+\begin{Algorithmic}
+\Function{$encrypt$}{$data, key, iv$}
+	\State $k \gets key$
+	\For{
 

### 2017-04-26 latex/keyexchange/secretkeybasedpublickeyencryption.tex
backing up work

@@
 \usepackage[utf8]{inputenc}
+\usepackage{titlesec}
 
@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[\texttt Lattice Based Key Exchange]{\texttt Lattice Based Key Exchange}
+\title[\texttt EPQ Key Exchange]{\texttt EPQ Key Exchange}
 
@@
 \begin{abstract}
-  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas.
-The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\
+  We define an algorithm for performing a key exchange between two parties. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\ 
 \end{abstract}
@@
 \section{Introduction}
- The ability to exchange cryptographic keys over insecure channels is of vital importance to the function of the internet; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.\\
+ The ability to exchange cryptographic keys over insecure channels is of vital importance to the function of the internet; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.
 
@@
 Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment.
-This property is also extremely important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers.
+This property is important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers.
 We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.
@@
 \section{Definitions}
-We use $+$ to denote addition, $ab$ to denote multiplication, and $\mod p$ to denote the modulo operation.
+We use $+$ to denote integer addition, $ab$ to denote integer multiplication, and $\mod p$ to denote the modulo operation. We use $log(x)$ to indicate the binary logarithm of $x$.
 
 \section{Algorithm}
-First, we shall define the key exchange algorithm; Then, we shall define a secret key cipher suitable for instantiating the key exchange algorithm.
+First, we shall define the asymmetric key exchange algorithm; Then, we shall define a symmetric secret key cipher suitable for instantiating the key exchange algorithm.
 
@@
 
-Where $r_1$ and $r_2$ are randomly generated values of appropriate size.\todo{What sizes are appropriate?} Then the value $c$ is shared with the owner of the public key.
-The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$.
+Where $r_1$ and $r_2$ are randomly generated values of appropriate size.
+Then the value $c$ is shared with the owner of the public key.
+The owner of the public key can recover $e$ from $c$ by applying the homomorphic decryption operation of the secret key cipher to c.
+Because $p_1$ is an encryption of $0$, $p_1 r_1 \equiv 0$, similar for $p_2$.
 So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.
+
+\subsubsection{Additional Information for Key Generation}
+If the size of the shared secret is to be 256 bits, then the ciphertexts produced by symmetric cipher must support the homomorphic addition of a plaintext 256-bit value.
+
+Not all homomorphic constructions support the addition of plaintext values to ciphertext values; Lattices offer this required feature.
+
+It is important that $p_1$ and $p_2$ are coprime to each other. Otherwise, some bits of the secret may be recovered by reducing a ciphertext modulo the greatest common divisor. Specifically:
+
+\begin{align}
+    e \gets secret\\
+    c \gets (p_1 r_1) + (p_2 r_2) + e\\
+    e_0 \gets c \mod gcd(p_1, p_2)
+\end{align}
+
+Where $log(e_0) \equiv log(gcd(p_1, p_2))$.
 
@@
 We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process.
-Let $s_1$ and $s_2$ be two large numbers, where $log_2(s_1) >= log_2(s_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\
+Let $s_1$ and $s_2$ be two large numbers, where $log(s_1) >= log(s_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\
 
@@
 
+\subsubsection{Additional Information for Key Generation}
+$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$
+
 \subsection{Note}
-While the decryption circuit works via two modulo operations of the base points of the lattice, this operation does not work for the public key/key exchange portion of the algorithm - The reason is because in the secret key cipher, the two different lattice points are of largely different size; In the key exchange algorithm, both points are roughly the same size, and so the double modulo operation does not function identically.
+While the decryption circuit works via two modulo operations of the base lattice points, this operation does not work for the public key/key exchange portion of the algorithm - The reason is because in the secret key cipher, the two different lattice points are of largely different size; In the key exchange algorithm, both points are roughly the same size, and so the double modulo operation does not function identically.
+
+\subsection{Public Key Randomization}
+Because the public key consists of malleable homomorphic ciphertexts, it can be randomized without complicating any of the rest of the procedures.
+The presented scheme can utilize encrypted public keys, and we give two potential use cases for the idea.
+
+First, as an additional layer of security, users who wish to send a message to the owner of the public key can first randomize the public key that they are using.
+Assuming that the randomized $p_1$ and $p_2$ are in effect unrelated to the original $p_1$ and $p_2$, then observers of the ciphertext do not even have the base points that the ciphertext was created with.
+
+Secondly, this feature allows for the disassociation of the owner of the public key from the possessor of the public key.
+For example, assume we have three parties, Alice, Bob, and Charlie.
+Charlie does not want Alice to communicate with Bob.
+If Charlie searches Alices computer and he finds Bobs public key, then he will know that Alice has been or intended to communicate with Bob.
+To counter this, Alice can randomize Bobs public key and store only the randomized key.
+The randomized key will be functionally equivalent to the public key associated with Bob, with the exception that nobody may associate it with Bob.
 

### 2017-04-26 C/42517/stats.py

@@ -1,0 +1,36 @@
+from crypto.utilities import rotate_left
+
+def mix_columns(a, b, c, d, mask=0xFFFFFFFF):
+    a = (a + b) & mask
+    c = (c + d) & mask
+    b ^= c
+    d ^= a
+    return a, b, c, d
+    
+def shift_rows(b, c, d, r1, r2, r3):
+    b = rotate_left(b, r1, 32); c = rotate_left(c, r2, 32); d = rotate_left(d, r3, 32);
+    return b, c, d
+    
+def mix_slice(a, b, c, d):    
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 1, 2, 3) 
+                            
+    a, b, c, d = mix_columns(a, b, c, d)
+    b, c, d = shift_rows(b, c, d, 4, 8, 12)
+    
+    a, b, c, d = mix_columns(a, b, c, d); 
+    b, c, d = shift_rows(b, c, d, 8, 12, 16)
+    return a, b, c, d
+    
+def visualize_mix_slice():
+    from crypto.analysis.visualization import test_4x32_function
+    test_4x32_function(mix_slice, (0, 0, 0, 1))
+    
+def test_active_bits():
+    from crypto.analysis.active_bits import search_minimum_active_bits2
+    search_minimum_active_bits2(mix_slice)
+    
+if __name__ == "__main__":
+    #visualize_mix_slice()
+    test_active_bits()
+    

### 2017-04-26 designs/hash/idekhash.py

@@ -1,0 +1,18 @@
+def _h(m, k1, k2):
+    return ((m * k1) + k2)
+    
+def h(m, k1, k2):
+    m_hash = _h(m, k1, k2)
+    return (m * m_hash) + m_hash
+    # m * ((m * k1) + k2) + ((m * k1) + k2)
+    # mm * mk1 + mk2 + mk1 + k2
+    
+def test_h():
+    for m in range(16):
+        for k1 in range(16):
+            for k2 in range(16):
+                print m, h(m, k1, k2)
+                
+if __name__ == "__main__":
+    test_h()
+    

### 2017-04-26 designs/homomorphic/anotheridea.py

@@ -1,0 +1,50 @@
+from crypto.utilities import random_integer, modular_inverse, modular_subtraction
+
+K_SIZE = 32
+Q_SIZE = 16
+DEFAULT_MODULUS = (2 ** (K_SIZE * 8)) + 1
+
+def generate_key(size=K_SIZE):
+    return random_integer(size), random_integer(size / 2), random_integer(size / 2)
+    
+def encrypt(m, secret_key, modulus=DEFAULT_MODULUS, q_size=Q_SIZE):
+    k1, k2, k3 = secret_key    
+    _e = ((m * k2) + k3) % modulus  
+    return _e
+    #assert modular_subtraction(_e, k3, modulus) == (m * k2) % modulus
+    #q = random_integer(q_size)
+    #return (k1 * q) + _e
+    
+def decrypt(c, secret_key, modulus=DEFAULT_MODULUS):
+    k1, k2, k3 = secret_key
+    _e = c #% k1    
+    return (modular_subtraction(_e, k3, modulus) * modular_inverse(k2, modulus)) % modulus
+    
+def test_encrypt_decrypt():
+    key = generate_key()
+    for m in range(256):
+        c = encrypt(m, key)
+        _m = decrypt(c, key)
+        assert _m == m, (_m, m)
+        
+    m1 = 1
+    m2 = 2
+    c1 = encrypt(m1, key)
+    c2 = encrypt(m2, key)
+    c3 = c1 * c2
+    # k1q1 + e1 + k1q2 + e2 == k1q1 + k1q2 + e3
+    # m1k2 + k3 + m2k2 + k3 = m1k2 + m2k2 + k3^2
+    
+    # (k1q1 + e1) * (k1q2 + e2) == k1q1k1q2 + k1q1e2 + k1q2e1 + e1e2
+    
+    # (m1k2 + k3) * (m2k2 + k3) == m1k2m2k2 + m1k2k3 + m2k2k3 + k3^2
+    # m1k2m2k2 + m1k2k3 + m2k2k3
+    # m1k2m2 + m1k3 + m2k3
+    
+    k1, k2, k3 = key
+    m3 = decrypt(c3, (k1, k2, k3 ** 2))
+    assert m3 == m1 * m2, (m3, m1, m2)
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-04-26 designs/homomorphic/modexpbased/discretelogtest.py

@@ -38,10 +38,39 @@
 # accept the smallest produced result      
 from crypto.utilities import modular_inverse
 
-def discrete_logarithm(factor, number, generator, modulus):   
-    test_count = modulus / factor
+# g * g * g * g * g * g * g
+#(g * g * g) * (g * g * g)
+
+# g * g * g
+# g * g
+
+# g * g * g * g * g * g
+# g * g
+
+def calculate_factors(n, g, modulus, test_factors=(2, 3, 5, 7, 11, 13, 17, 19)):
+    factors = []
+    for factor in test_factors:
+        print n, factor, g ** factor, (n / (g ** factor))
+        if (n / (g ** factor)) == 1:
+            return factor
+        elif (n / (g ** factor)) % (g ** factor) == g ** factor:
+            # factor is a factor of the exponent
+            factors.append(factor)
+            break
+    if not factors:
+        factors.append(1)
+    print "Exponent factors: ", factors
+    _exponent = 1
+    for item in factors:
+        _exponent *= item
+    return _exponent
+    
+def discrete_logarithm(number, generator, modulus):   
+    factor = calculate_factors(number, generator, modulus)
+    test_count = 65537#modulus / factor
     inverse = modular_inverse(generator ** factor, modulus)
-    exponent = 0        
+    exponent = 0  
+    print "dl: ", number, factor, inverse
     for _count in range(test_count):
         number *= inverse
         number %= modulus
@@ -56,7 +85,8 @@ def test_discrete_logarithm():
     p = 65537
     for exponent in range(3, 65537, 3):        
         output = pow(g, exponent, p)           
-        _exponent = discrete_logarithm(3, output, g, p)
+        print "Exponent: ", exponent
+        _exponent = discrete_logarithm(output, g, p)
         assert _exponent == exponent, (_exponent, exponent)        
         
         

### 2017-04-26 latex/keyexchange/secretkeybasedpublickeyencryption.tex
fixed hash
hash did not necessarily digest all of the data before

@@
 \subsubsection{Additional Information for Key Generation}
-$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$
+$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$. To instantiate the key exchange scheme, $log(s_1) \equiv $
 
@@
 The algorithm utilizes 4 bignum multiplications and 4 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key.
-Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
+Public keys occupy about 2300 bits using current parameter cohices, while private keys require about 1200 bits.
 \end{document}

### 2017-04-26 C/42517/hash.c

@@ -14,32 +14,37 @@ void hash_function(WORDSIZE* hash_input, WORDSIZE input_length, WORDSIZE* output
                 
     number_of_blocks = input_length / 8;      
     if (input_length % 8 == 0){
-        if (number_of_blocks > 1){
+        if (number_of_blocks >= 1){
             number_of_blocks -= 1;}}
-            
-    for (block_number = 0; block_number < number_of_blocks; block_number++){
+    
+    for (block_number = 0; block_number < number_of_blocks; block_number++){    
         absorb(state, hash_input, 8, (block_number * 8), block_number);}
     
     block_number += 1;    
-    if (input_length % 8 == 0){
-        absorb(state, hash_input, 8, (block_number * 8), (0xFFFFFFFF ^ block_number));}
-    else{
-        absorb(state, hash_input, input_length % 8, (block_number * 8), (0xFFFFFFFF ^ block_number));}
+    int amount = input_length % 8;
+    if (amount == 0){
+        amount = 8;}
+    
+    absorb(state, hash_input, amount, (block_number * 8), (0xFFFFFFFF ^ block_number));    
     copy(output, state, 8, 0, 0);}
                     
 void test_hash(){    
-    #define message_size 32
+    #define message_size 9
 	WORDSIZE message[message_size];
     WORDSIZE hash_result[8];
     unsigned long index;
     
     zero_out(message, message_size);
     clock_t begin = clock();
-    for (index = 0; index < 1000000; index++){
+    for (index = 0; index < 2; index++){
         hash_function(message, message_size, hash_result);}
     clock_t end = clock();
     
     double time_spent = (double)(end - begin) / CLOCKS_PER_SEC;    
     printf("Time required: %.2fs\n", time_spent);
     printf("%lu%lu%lu%lu%lu%lu%lu%lu\n", hash_result[0], hash_result[1], hash_result[2], hash_result[3], hash_result[4], hash_result[5], hash_result[6], hash_result[7]);}
+    
+int main(){
+    test_hash();
+    return 0;}
     

### 2017-04-30 latex/keyexchange/secretkeybasedpublickeyencryption.tex
updated implementation for a design

@@
 
-Where $log(e_0) \equiv log(gcd(p_1, p_2))$.
+Where $log(e_0) \equiv log(gcd(p_1, p_2))$. If $p_1$ and $p_2$ are not coprime, then a simple modulo operation will yield $log(gcd(p_1, p_2))$ bits of the secret $e$.
 
@@
 \subsubsection{Additional Information for Key Generation}
-$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$. To instantiate the key exchange scheme, $log(s_1) \equiv $
+$s_1$ and $s_2$ should be coprime, and $log(s_1) >= log(s_2) * 3$.
+To instantiate the key exchange scheme, $log(s_2) >= log(e)$, where $e$ is the secret to be shared.
+If $e$ is to be 256 bits, then $log(s_2) >= 256$ and $log(s_1) >= 768$.
+We have a python implementation where $log(s_1) \equiv 880$ and $log(s_2) \equiv 288$ for a total of about 1168 bits, or 146 bytes.
 
@@
 
-Secondly, this feature allows for the disassociation of the owner of the public key from the possessor of the public key.
+Secondly, this feature allows for the disassociation of the distributor of the public key from the possessor of the public key.
 For example, assume we have three parties, Alice, Bob, and Charlie.
@@
 
+Any homomorphic secret-key instantiated scheme can trivially produce a randomized public key using the secret key to generate a new public key; The scheme presented here allows for the generation of a randomized public key using only the public key.
+The difference is that in the former case, Bob would have to distribute the randomized key, which would associate it with him (assuming it is signed, for example).
+In the latter case, Bob has only one key, and Alice can obtain a randomized public key on her own.
+
+\subsubsection{Key Randomization Algorithm}
+\begin{align}
+    p_n \gets p_1 r_1 - p_2 r_2 + p_1 r_3 - p_2 r_4\\
+\end{align}
+
+\section{Metrics}
+Private keys are slightly less then 1200 bits or 150 bytes. Public keys are approximately 2300 bits or 280 bytes. Ciphertexts from the key exchange algorithm are about 1500 bits or 185 bytes.
+
+The time required to generate a keypair is about .0019 seconds.
+Our simple python implementation can perform 8192 key exchanges in slightly less then 1 second.
+While a C implementation would probably be faster, most of the time is likely spent doing bignum arithmetic, which means that a simple python implementation may be acceptably fast.
+
 \section{Conclusion}

### 2017-04-30 C/42517/encrypt.c

@@ -9,7 +9,7 @@
         
 #define constant_time_comparison(flag, array1, array2, array_size, offset1, offset2)({\
     for (index = 0; index < array_size; index++){\
-        flag = (state[index + offset1] ^ tag[index + offset2] ^ 1) & flag;}})        
+        flag = (state[index + offset1] ^ tag[index + offset2] ^ 0xFFFFFFFF) & flag;}})        
             
 void encrypt(WORDSIZE* data, WORDSIZE* key, WORDSIZE* iv, WORDSIZE* extra_data, WORDSIZE* tag,
              unsigned long data_size, unsigned long extra_data_size){
@@ -18,10 +18,10 @@ void encrypt(WORDSIZE* data, WORDSIZE* key, WORDSIZE* iv, WORDSIZE* extra_data, 
     initialize_state(state, iv, key, extra_data, extra_data_size);
         
     unsigned long block_number;    
-    for (block_number = 0; block_number < data_size / 8; block_number++){        
-        copy(state, data, 8, 0, (block_number * 8));
+    for (block_number = 0; block_number < data_size / 8; block_number++){    
+        copy(state, data, 8, 0, (block_number * 8));                       
         permutation(state);
-        copy(data, state, 8, (block_number * 8), 0);}       
+        copy(data, state, 8, (block_number * 8), 0);}        
          
     for (index = 0; index < 8; index++){
         tag[index] = state[index + 8] ^ key[index];}}
@@ -42,7 +42,7 @@ int decrypt(WORDSIZE* data, WORDSIZE* key, WORDSIZE* iv, WORDSIZE* extra_data, W
     copy(tag, state, 8, 0, 8);          
     initialize_state(state, iv, key, extra_data, extra_data_size);  
     
-    int valid = 1;
+    int valid = 0xFFFFFFFF;
     constant_time_comparison(valid, state, tag, 8, 8, 0);
     return valid;}    
         
@@ -64,7 +64,7 @@ void test_encrypt_decrypt(){
     //iv[0] = 0;    
     //tag[0] = 0;
     //extra_data[0] = 0;
-    if (decrypt(data, key, iv, extra_data, tag, 8, 8) == 1){
+    if (decrypt(data, key, iv, extra_data, tag, 8, 8) == 0xFFFFFFFF){
         printf("%lu%lu%lu%lu%lu%lu%lu%lu\n", data[0], data[1], data[2], data[3], data[4], data[5], data[6], data[7]);}
     else{
         printf("Decryption failed\n");}}

### 2017-04-30 designs/homomorphic/modexpbased/randomizedmodulus.py

@@ -1,0 +1,85 @@
+from math import log
+
+from crypto.utilities import big_prime, modular_inverse
+
+P_SIZE = 32
+Q_SIZE = 32
+
+def generate_private_key(p_size=P_SIZE, e=65537):
+    p = big_prime(p_size)
+    d = modular_inverse(e, p - 1)
+    return e, d, p
+    
+def generate_public_key(e, p, q_size):     
+    encrypted_q = encrypt(big_prime(2), (e, p))
+    encrypted_p = encrypt(p, (e, p))
+    encrypted_n = encrypted_q * encrypted_p
+    assert encrypted_n % p == 0
+    return encrypted_n
+
+def generate_keypair(p_size=P_SIZE, q_size=Q_SIZE):
+    e, d, p = generate_private_key(p_size)
+    n = generate_public_key(e, p, q_size)
+    return (e, n), (d, p)        
+        
+def encrypt(m, public_key, q_size=16):
+    e, n = public_key
+    #n *= big_prime(q_size)
+    return pow(m, e, n)
+    
+def decrypt(c, private_key, q_size=16):
+    d, p = private_key
+    p *= big_prime(q_size)
+    return pow(c, d, p)   
+    
+# m ^ d mod n == m * r mod n
+#     
+#def sign(data, private_key):
+        
+        
+def test_encrypt_decrypt():
+    public, private = generate_keypair()
+    #p_bits = int(log(p, 2))
+    #for m in range(p_bits):
+    #    c = encrypt(m, e, p)
+    #    _m = decrypt(c, d, p)
+    #    assert _m == m
+        
+    m = 10
+    c = encrypt(m, public)
+    
+    m2 = 20
+    c2 = encrypt(m2, public)
+    
+    c3 = c * c2
+    p3 = decrypt(c3, private)
+    assert p3 == (m * m2), (p3, m, m2, m * m2)
+    
+    #c4 = c + c2
+    #p4 = decrypt(c4, d, p)
+    #assert p4 == (m + m2), (p4, m, m2, m + m2)
+    
+    #c5 = pow(c, c2, p)
+    #p5 = decrypt(c5, d, p)
+    #assert c5 == (m ** m2), (p5, m, m2, m ** m2)
+    
+    #c6 = encrypt(m, e, p) * m2
+    #p6 = decrypt(c6, d, p)
+    #assert p6 == (m * m2), (p6, m, m2, m * m2)
+    
+    #_exponent = 30000
+    #e, n = public
+    #c7 = encrypt(m, public)
[…]

### 2017-04-30 designs/permutation/nonlinearkeytest.py

@@ -1,0 +1,49 @@
+from crypto.utilities import rotate_left
+
+def fill(byte):
+    byte ^= rotate_left(byte, 1, 32)
+    byte ^= rotate_left(byte, 2, 32)
+    byte ^= rotate_left(byte, 4, 32)
+    byte ^= rotate_left(byte, 8, 32)
+    byte ^= rotate_left(byte, 16, 32)
+    #byte ^= rotate_left(byte, 32, 64)    
+    return byte
+    
+def mix_columns(_a, _b, _c, _d):
+    _a ^= _b
+    _c ^= _d
+    _b ^= _c
+    _d ^= _a
+    #r = [_a, _b, _c, _d]
+    #a = [0] * 4
+    #b = [0] * 4
+    #for count in range(4):
+    #    a[count] = r[count]        
+    #    h = fill(r[count] >> 7)
+    #    b[count] = (r[count] << 1) & 0xFFFFFFFF
+    #    b[count] ^= 0xc3 & h
+    #    
+    #r[0] = b[0] ^ a[3] ^ a[2] ^ b[1] ^ a[1]
+    #r[1] = b[1] ^ a[0] ^ a[3] ^ b[2] ^ a[2]
+    #r[2] = b[2] ^ a[1] ^ a[0] ^ b[3] ^ a[3]
+    #r[3] = b[3] ^ a[2] ^ a[1] ^ b[0] ^ a[0]
+    return _a, _b, _c, _d
+    
+def encrypt(a, b, c, d):           
+    t = a
+    a = (a & b) ^ c
+    c = (b | c) ^ d
+    d = (d & a) ^ t
+    b ^= c & t           
+    a, b, c, d = mix_columns(a, b, c, d)    
+    return a, b, c, d
+    
+def visualize_encrypt():
+    from crypto.analysis.visualization import test_4x32_function
+    test_4x32_function(encrypt, (0, 0, 0, 1))
+    
+#def test_active_bits():
+    
+if __name__ == "__main__":
+    visualize_encrypt()
+    

### 2017-05-17 latex/keyexchange/secretkeybasedpublickeyencryption.tex
added new cipher idea

@@
 \section{Introduction}
- The ability to exchange cryptographic keys over insecure channels is of vital importance to the function of the internet; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.
+ The ability to exchange cryptographic keys over insecure channels is of vital importance for secure communications in general; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.
 
 The introduction of Quantum Computing and post-quantum cryptography has lead to the development of lattice based cryptographic schemes that are believed to be secure even when faced with quantum parallelism.
-Simply put, RSA and DH will need replacement at some point, and lattices seem like a promising alternative.
 
@@
 
-Where the $r$ values are of appropriate size relative to $s_1$ and $s_2$ \todo{what sizes are appropriate}
-While decryption is computed as:
+Where the $r$ values are of appropriate size relative to $s_1$ and $s_2$.
+
+Decryption is computed as:
 
@@
 \subsection{Public Key Randomization}
+\todo{Needs more development}
 Because the public key consists of malleable homomorphic ciphertexts, it can be randomized without complicating any of the rest of the procedures.

### 2017-05-17 latex/rsareviewed.tex
added new cipher idea

--- 2017-03-14 latex/algorithmdesign/untitled-4.tex
@@
 
-\title{Brief Article}
-\author{The Author}
+\title{Alternative Perspective of the RSA Cipher}
+\author{Ella Rose}
 %\date{} % Activate to display a given date or no date (if empty),
@@
 
-\section{First section}
+\begin{abstract}
+ We provide an alternative description of the RSA cipher by breaking it up into a few discrete, separate pieces.
+We hope that by understanding RSA as part of a more generalized cipher framework, we  might come up with alternative instantiations of the cipher that utilize different hardness assumptions.
+We do not suggest such a design here.
 
-Meet Bob and Alice.
-Bob and Alice are pen pals; they write letters to each other, and send them through the mail.
-Additionally, we will introduce Eve:  Eve has no respect for others, as well as a pathological need to try and do wrong; She is not opposed to lying, cheating, and stealing, and is very creative in this arts.
-She will go to great length to do these things if she thinks it will benefit her; Even when there is no real benefit to her, she will do such things whenever she can get away with it, simply because she can.
+\section{Introduction to RSA}
+This section will outline the RSA algorithm - for the history of the design, we encourage the reader to look elsewhere. \todo{RSA history is where?}
 
-Unfortunately, Eve is the mail carrier.
-Fortunately, Bob and Alice are aware of Eve's nature, and they seek to find ways of communicating with each other without Eve interfering.
-In order to do so, they need to enumerate all of the ways that Eve could abuse their communications, and develop appropriate counter-measures.
+The RSA cryptosystem utilizes three core functions:
 
-\subsection{Lying, Cheating, and Stealing}
+ The key generation algorithm, which generates a private key and corresponding public key
+ The encryption algorithm, which replaces the supplied number with a psuedorandom number
+ The decryption algorithm, which recovers the number that was supplied to the encryption algorithm, when given the output of the encryption algorithm and the private key.
 
-The first and most obvious concern is Eve opening and reading the messages that are exchanged between Bob and Alice.
+The key generation algorithm is typically described by something like the following:
 
-Second, and slightly more devious, is that Eve could manipulate messages sent between the two.
+Select two large, random prime numbers of approximately equal size $p, q \gets bigPrime(size) bigPrime(size)$
+Calculate the totient via $totient \gets (p -1)(q - 1)$
+Set e to the usual/safe value (i.e. 65537); Select the decryption exponent via $modularInverse(e, totient)
+Multiply p and q to produce the modulus n $n \gets pq$
+Output n, e as the public key; Output d as the public key;
 
-Third, Eve actually does not have to wait for Bob to actually send a letter to Alice. She can simply write her own letter, put Bob's name on it, and deliver it to Alice.
+While the encryption/decryption algorithms are simplier and are described by something like:
 
-Fourth, she could withhold or make copies of messages, and save them for delivery at some other arbitrary point in time.
+Produce a ciphertext of message by computing $message ^ e \mod n$
+Produce a plaintext from ciphertext by computing $ciphertext ^ d mod n$
 
-Finally, Eve could simply choose not to deliver the messages at all.
+While this is enough information to produce a working implementation of the "textbook" RSA algorithm, it is does not really fit well into a generic cipher framework.
 
-\subsection{Solutions}
+\section{An Alternative Introduction to RSA}
+First, we shall describe a simple secret key cipher that is homomorphic with respect to multiplication of ciphertexts:
 
-For example, Bob might send Alice a christmas card with money inside, and a note that says "I am sending you \$20; I hope you have a nice holiday".
-Upon opening this, Eve could simply take the money, and leave a new note in the card that say "Sorry, I can't afford gifts this year; I hope you have a nice holiday anyways.
-PS: Please send me some money".
-Then she could easily repeat this process.
+Select a random prime number of sufficient size $p \gets bigPrime(size)$
+Select an encryption exponent of appropriate size (>2 and <size of p)
+Calculate the decryption exponent by computing $d \gets modularInverse(e, p - 1)$
+Encrypt a number by computing $m^e mod n$ and decrypt by computing $c^d mod n$
+
+The only difference so far is that we are using a single prime number as the modulus.
+Despite the fact that encryption and decryption are asymmetric operations, this cipher is not secure as a public key cipher, as anyone who knows $p$ and $e$ may compute $d$.
+
+RSA typically computes the decryption exponent by computing $modularInverse(e, totient(n))$, but it works equally well to use $modularInverse(e, totient(p))$ or $modularInverse(e, totient(q))$ - as long as the message is smaller then p or q, respectively.
+
+So the modulus $n \gets np$ that is typically released as part of the public key is effectively an encrypted modulus.
+
+As long as we encrypt messages of size smaller then p (the basis), then we do not need to know the totient of n - we only need to know the totient of p (or at least, one factor of n).
+
+# the purpose of q is to encrypt p so that others cannot obtain d
+# mk is a secure cipher if m and k are large primes and no "fast" classical algorithm for factoring exists
 

### 2017-05-17 cryptographyless.py

@@ -1,5 +1,6 @@
 """ Provides authenticated encryption and decryption functions using only the python standard library and the persistence module.
     Used when the cryptography module cannot be installed.  """
+raise NotImplementedError() # todo: copy aead from epqcrypto
     
 import itertools
 import hashlib

### 2017-05-17 designs/encoding/majorityencoding.py

@@ -1,0 +1,29 @@
+from crypto.utilities import random_bits
+import math
+
+# majority with variable length input
+def majority(bits):    
+    if not len(bits) % 2: 
+        raise ValueError("len(bits) must be odd to calculate majority")    
+    return int(math.floor(.5 + (float(sum(bits)) / len(bits))))             
+    
+def encode_bit(data_bit, encoding_size=3):
+    encoded_bit = random_bits(encoding_size)    
+    while majority(encoded_bit) != data_bit:
+        encoded_bit = random_bits(encoding_size)  
+    return encoded_bit
+    
+def decode_bit(encoded_bits):
+    return majority(encoded_bits)
+            
+def test_encode_bit_decode_bit():
+    for count in range(3, 32, 2):
+        for bit in range(2):            
+            encoded_bit =  encode_bit(bit, count)           
+            decoded_bit = decode_bit(encoded_bit)            
+            assert decoded_bit == bit
+    print("majority encode_bit/decode_bit unit test passed")
+                    
+if __name__ == "__main__":
+    test_encode_bit_decode_bits()    
+        

### 2017-05-17 designs/homomorphic/latticebased/tinymod.py

@@ -1,0 +1,32 @@
+from crypto.utilities import random_integer, gcd
+
+# 64 bit p1
+# 32 bit p2 * 32 bit q2 == 64 bit p2q2
+
+def generate_key(p1_size=4, p2_size=2):
+    p1 = random_integer(p1_size)
+    p2 = random_integer(p2_size)
+    while gcd(p1, p2) != 1:
+        p2 = random_integer(p2_size)
+    return p1, p2
+    
+def encrypt(m, key, q_size1=4, q_size2=1):
+    p1, p2 = key
+    q1 = random_integer(q_size1)
+    q2 = random_integer(q_size2)
+    return (p1 * q1) + (p2 * q2) + m
+    
+def decrypt(c, key):
+    p1, p2 = key
+    return (c % p1) % p2
+        
+def test_encrypt_decrypt():
+    key = generate_key()
+    m = random_integer(1)
+    ciphertext = encrypt(m, key)
+    plaintext = decrypt(ciphertext, key)
+    assert plaintext == m, (m, plaintext)
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-17 designs/homomorphic/modexpbased/crttest.py

@@ -1,0 +1,50 @@
+# dp = modular_inverse(e, p)
+# dq = modular_inverse(e, q)
+# qi = modular_inverse(q, p)
+
+# m1 = pow(c, dp, p)
+# m2 = pow(c, dq, q)
+# h = qinv(m1 - m2)
+# m = m2 + hq
+from crypto.utilities import big_prime, modular_inverse, random_integer
+
+def generate_key(size):
+    p = big_prime(size)
+    q = big_prime(size)
+    return p, q
+        
+def decrypt(c, p, e=65537):
+    dp = modular_inverse(e, p - 1)
+    return pow(c, dp, p)
+    
+    #dq = modular_inverse(e, q - 1)
+    #m1 = pow(c, dp, p)
+    #m2 = random_integer(16)
+    #h = (modular_inverse(q, p) * (m1 - m2)) % p
+    #return (m2 + (h * q)) % p
+    
+# the purpose of q is to encrypt p so that others cannot obtain d
+# mk is a secure cipher if m and k are large primes and no "fast" classical algorithm for factoring exists
+# p * q returns a homomorphic encryption of p
+# pow(p, e, k) returns a homomorphic encryption of p
+
+def encrypt(m, p, q, e=65537):
+    return pow(m, e, p * q)
+    #c1 = pow(m, e, p)
+    #c2 = random_integer(16)
+    #h = (modular_inverse(q, p) * (c1 - c2)) # qi * c1
+    #return (c2 + (h * q)) % p               # qi * c1 * q
+    
+def test_encrypt_decrypt():
+    p, q = 251, random_integer(32)#big_prime(16)#generate_key(16)
+    m = 10#1337
+    c = encrypt(m, p, q)
+    print c
+    assert pow(c, modular_inverse(65537, p), p) != m
+    _m = decrypt(c, p)
+    print _m
+    assert _m == m, (_m, m)
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-17 designs/homomorphic/modexpbased/halfrsa.py

@@ -1,0 +1,40 @@
+from math import log
+
+from crypto.utilities import big_prime, modular_inverse
+
+def generate_private_key(size, e=65537):
+    p = big_prime(size)
+    q = big_prime(size)  
+    return p, q, modular_inverse(e, p - 1)
+    
+def generate_public_key(p, q):
+    return p * q
+    
+def generate_keypair(size, e=65537):
+    p, q, d = generate_private_key(size, e)
+    return (e, p * q), (d, p)
+    
+def encrypt(m, public_key):
+    e, n = public_key
+    assert log(m, 2) <= log(n, 2) / 2, (log(m, 2), log(n, 2) / 2)
+    return pow(m, e, n)
+    
+def decrypt(c, private_key):
+    d, p = private_key
+    # single modexp with a single prime of size 1/2 the modulus
+    # instead of exponentiation modulo a 4096 bit number, only requires exponentiation modulo a 2048 bit number
+    # works as long as m < p
+    # takes about 1/3 less time
+    return pow(c, d, p) 
+    
+def test_encrypt_decrypt():    
+    from crypto.utilities import random_integer
+    public_key, private_key = generate_keypair(16)
+    m = random_integer(15)
+    c = encrypt(m, public_key)   
+    _m = decrypt(c, private_key)
+    assert _m == m, (_m, m)
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-17 designs/permutation/choicebitwisepermutation.py

@@ -20,8 +20,8 @@ def bit_permutation(a, b, c, d, k0, k1, k2, k3, size=32):
     # low weight keys are weak       
     # data does not cause avalanche effect
     for round in range(4):              
-        a ^= 0xFFFFFFFF
-        d ^= 0xFFFFFFFF
+        #a ^= 0xFFFFFFFF
+        #d ^= 0xFFFFFFFF
             
         a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)                
         b = rotate_left(b, 1, size)
@@ -43,7 +43,7 @@ def bit_permutation(a, b, c, d, k0, k1, k2, k3, size=32):
         
         a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)
         a, b, c, d = b, c, d, a 
-        a, b, c, d, k0, k1, k2, k3 = k0, k1, k2, k3, a, b, c, d
+#        a, b, c, d, k0, k1, k2, k3 = k0, k1, k2, k3, a, b, c, d
    # print
    # print '\n'.join(format(word, 'b').zfill(32) for word in (a, b, c, d))
     return a, b, c, d, k0, k1, k2, k3

### 2017-05-17 other/quicksum.py

@@ -1,0 +1,85 @@
+#n = 256
+#1 + 255
+#2 + 254
+#3 + 253
+#...
+#127 + 129
+#128
+
+def quicksum_range(p):
+    """ usage: quicksum_range(p) => int
+    
+        Sums range(p) significantly faster then sum(range(p)). """
+    q, e = divmod(p, 2)
+    if not e:
+        q -= 1   
+        e = q + 1   
+    else:
+        e -= 1
+    return (p * q) + e
+
+def quicksum_ordered_set(numbers):
+    """ usage: quicksum_ordered_set(iterable: numbers) => int
+        
+        Sums the supplied numbers.
+        Requirements:
+            - the supplied numbers must form a set (meaning no duplicates)
+                - the data type can be a list or tuple still, as long as len(set(iterable)) == len(iterable)
+            - the supplied numbers are in ascending order """            
+    p = numbers[-1]
+    _sum = quicksum_range(p)
+    # 1       5   7   9    11    13    15 desired addends
+    # 1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 quicksum all of these
+    #   2 3 4   6   8   10    12    14    subtract these out    
+    numbers = numbers[:]  
+    if numbers[0] == 0:
+        a = numbers.pop(0)
+    else:
+        a = 0
+    while numbers:        
+        b = numbers.pop(0)        
+        difference = sum(xrange(a + 1, b))    
+        _sum -= difference
+        a = b           
+    return _sum + a
+    
+def test_quicksum_range():
+    for x in range(3, 257):        
+        _sum = quicksum_range(x)
+        __sum = sum(xrange(x))
+        assert _sum == __sum, (x, _sum, __sum)
+    
+    from pride.functions.timingcomparison import timing_comparison
+    from crypto.utilities import random_integer
+    p = random_integer(2)    
+    timing_comparison((sum, (range(p), ), {}),
+                      (quicksum_range, (p, ), {}), iterations=1000)
+                      
+def test_quicksum_ordered_set():
+    from os import urandom
+    from crypto.utilities import random_integer
+    for count in range(256):
+        test_case = sorted(list(set(bytearray(urandom(32)))))
+        indices = sorted([item & 31 for item in bytearray(urandom(4))])
+        del test_case[indices.pop(0):indices.pop(0)]
+        del test_case[indices.pop(0):indices.pop(0)]
+                
+        output = quicksum_ordered_set(test_case)        
[…]

### 2017-05-22 latex/manymod/paper.tex
backing up designs

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
\title[Manymod Cipher]{Manymod Cipher}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Key Exchange]{Key Exchange}\todo{Keywords?}

\begin{abstract}
 We define a secret key cipher with homomorphic properties. The goal of the design was to improve the ratio of plaintext information contained in a ciphertext. The algorithm utilizes bignum addition and multiplication, as well as division and modular reduction. 
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
 Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes straightforward and relatively simple. Lattices are attractive because they tend to facilitate such operations. Unfortunately, some of the lattice based ciphers suffer from a practical problem: Prohibitively large ciphertexts are required to encrypt even small amounts of plaintext. For example, the DoubleMod construction requires approximately 22.5Kb of ciphertext to encrypt a single plaintext bit, and that is with a rather small security level of about 80 bits.

In this paper, we define an algorithm that appears to make more efficient use of a given amount of ciphertext space.

\section{Definitions}
We use $+$ to denote addition, $ab$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.

\section{Algorithm}
\subsection{Basic Concept}
\subsubsection{Encryption}
\begin{align}
a := k_1 m_1\\
b := k_2 m_2\\
ciphertext  := a + b
\end{align}

\subsubsection{Decryption}
Assuming that k2 is significantly larger then k1, then given $z$ and $k1, k2$, it is possible to recover $m1, m2$. This can be done via the following:

\begin{align}
a := ciphertext \mod k_2\\
b := ciphertext - a\\
m_1 := a / k_1\\
m_2 := b / k_2
\end{align}

\subsection{Randomization}
Any homomorphic cipher requires randomization in order to be secure. The presented design is very simple to randomize; Continuing with the previous example, we would simply generate an additional $k_3$ and a random $r_0$ and include that in the sum as well:

\begin{align}
a := k_1 m_1\\
b := k_2 m_2\\
c := k_3 r_0\\
ciphertext := a + b + c
\end{align}

Decryption proceeds as before, with the exception that the randomized outter-most message need not be output by the decryption procedure.

\subsection{Key Generation}
For decryption to function correctly, the size of the successive keys must grow larger. Each successive key must be greater then the square of the size of previous element.

For simplicity, we begin by generating an 8-bit random number, and setting $k_1$ to that. Then, to generate the next key, we generate a 16-bit random number, and check to ensure that the previous key is smaller then the square root of the candidate next key. If it is not of appropriate size, the sample is rejected and another obtained until the test passes. Once a key of appropriate size is obtained, then we proceed to generate a 32-bit key and repeat the process again and again until a sufficient amount of security can be obtained.

\subsection{Note}
We note that this encryption algorithm scales well in terms of security and plaintext/ciphertext ratio: Increasing the dimension (the number of key/message points) will tend to increase the hardness of any associated lattice problem, as well as the amount of plaintext that can be stored in the ciphertext.

\subsection{Orthoganlity of Points}
The final ciphertext consists of a linear superposition of orthogonal $k_n m_n$ pairs. The orthognality feature allows us to manipulate each individual $k_n m_n$ pair independently of any others wiithout having to remove it from the superposition.

 Put in other words, the entire ciphertext constitutes a kind of encrypted array, where each entry is a ciphertext (in the form of $k_n m_n$). The elements of the array are not stored successively, as in a traditional array, but are instead stored in a superposition, on top of one another.

Accessing elements of the array is not done via indexing, but instead via the lattice basis point $k_n$. For example, consider:

\begin{align}
m_1 := 1\\
m_2 := 2\\
m_3 := 3\\
m_4 := 4\\
ciphertext_1 := k_1 m_1 + k_2 m_2\\
ciphertext_2 := k_1 m_3 + k_2 m_4\\
ciphertext_3 := ciphertext_1 + ciphertext_2\\
ciphertext_3 := ciphertext_3 - k_1\\
ciphertext_3 := ciphertext_3 + ( k_2 * 10)
\end{align}

In the example, two "arrays" of ciphertexts are created. The $ciphertext_1$ "array" contains the values 1 and 2, while the $ciphertext_2$ "array" holds the values 3 and 4. Then, these two arrays are summed element-wise, and the resulting $ciphertext_3$ now holds the values $1 + 3 = 4$ and $2 + 4 = 6$. After that, $1$ is subtracted from the first element of the array, then 10 is added to the second element of the array.

While this write access requires the key to perform, an encryption of the key will also work. It is possible to provide explicit write access on individual, particular elements without providing read access to any elements.

\subsection{Decryption Order}
Ciphertexts must be decrypted in order of largest to smallest basis. If the larger "outer" ciphertexts have a sufficient security margin, then knowledge of the smaller, "inner" basis does not provide read access on the data, but it does provide write access on the data.

\section{Conclusion}

\end{document}

### 2017-05-22 designs/homomorphic/latticebased/innerouter.py

@@ -1,0 +1,55 @@
+# pm + r
+# pm1 + r1 + pm2 + r2 == pm3 + r3
+
+# pr + m
+# pr1 + m1 + pr2 + m2 == pr3 + m3
+
+# pm + m
+# pm1 + m1 + pm2 + m2 == pm3 + m3 # self certifying?
+
+# pp + e # self certifying?
+
+
+
+
+# pm + e is no good because m = 0, but even without m = 0:
+# encrypt m with another pr + m
+from crypto.utilities import random_integer
+
+def generate_key(size=33):
+    return random_integer(size), random_integer(size)
+    
+def encrypt_inner(m, inner_key, r_size):
+    return (inner_key * random_integer(r_size)) + m
+    
+def decrypt_inner(ciphertext, inner_key):
+    return ciphertext % inner_key
+    
+def encrypt_outer(c, outer_key, r_size):    
+    return (outer_key * c) + random_integer(r_size)
+    
+def decrypt_outer(ciphertext, outer_key):
+    r = ciphertext % outer_key
+    ciphertext -= r
+    return ciphertext / outer_key
+    
+def encrypt(m, key, r_size=32):
+    inner_key, outer_key = key
+    c = encrypt_inner(m, inner_key, r_size)
+    return encrypt_outer(c, outer_key, r_size)
+    
+def decrypt(ciphertext, key):
+    inner_key, outer_key = key
+    _ciphertext = decrypt_outer(ciphertext, outer_key)
+    return decrypt_inner(_ciphertext, inner_key)
+    
+def test_encrypt_decrypt():
+    key = generate_key()
+    message = random_integer(32)
+    ciphertext = encrypt(message, key)
+    plaintext = decrypt(ciphertext, key)
+    assert plaintext == message           
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-22 designs/homomorphic/latticebased/manymod.py

@@ -23,8 +23,11 @@ def generate_key(dimension=8):
         size *= 2
     return points
         
-def encrypt(message_points, key_points):
-    return sum(message_points[index] * key for index, key in enumerate(key_points))
+def encrypt(message_points, key_points, r_size=32):
+    assert len(message_points) == len(key_points) - 1, (len(message_points), len(key_points))    
+    ciphertext = sum(message_points[index] * key for index, key in enumerate(key_points[:-1]))
+    ciphertext += (key_points[-1] * random_integer(r_size)) # randomization
+    return ciphertext
     
 def decrypt(ciphertext, key_points):
     message_points = []
@@ -33,18 +36,16 @@ def decrypt(ciphertext, key_points):
         point = ciphertext - temp
         message_points.append(point / key)
         ciphertext = temp
-    return list(reversed(message_points))
+    return list(reversed(message_points[1:]))
     
 def test_encrypt_decrypt():
     key = generate_key()
-    m = [2, 5, 11] + ([0] * (len(key) - 4)) + [random_integer(64)]
-    ciphertext = encrypt(m, key)
-    print ciphertext
-    print encrypt([2, 5, 11] + ([0] * (len(key) - 4)) + [random_integer(32)], key)    
-    
-    ciphertext += key[0] * 1
+    m = [2, 5, 11] + ([0] * (len(key) - 4))
+    ciphertext = encrypt(m, key)      
+    #ciphertext += key[0] * 1
     plaintext = decrypt(ciphertext, key)
     assert plaintext == m, (plaintext, m)
+    print("manymod encrypt_decrypt unit test pass")
     
 if __name__ == "__main__":
     test_encrypt_decrypt()

### 2017-05-22 designs/homomorphic/latticebased/recursemod.py

@@ -1,0 +1,52 @@
+# recurse mod
+# Like manymod, but where each m1 is also a SingleMod ciphertext
+# c1 := k1r1 + m1
+# c2 := k2r2 + m2
+# ...
+# cN := kNrN + mN
+# ciphertext := manymod encrypt(c1, c2, ... cN)
+
+# manymod
+#encrypt:
+#    p1m1 + p2m2 + p3m3 + p4m4 + p5m5 + ...
+#
+#decrypt:
+#    p2345 = c % p1
+#    p1m1 = c - p2345
+#    m1 = p1m1 / p1
+#    
+#    ...
+
+from math import sqrt
+
+from crypto.utilities import random_integer
+   
+def generate_item_key(size):
+    return random_integer(size)
+
+def encrypt_item(m, key, r_size):
+    assert m <= key
+    r = random_integer(r_size)
+    print key, m, r
+    return (key * m) + r
+    
+def decrypt_item(ciphertext, key):
+    r = ciphertext % key
+    print r
+    ciphertext -= 4
+    return ciphertext / key
+    return (ciphertext - (ciphertext % key)) / key
+        
+def test_encrypt_decrypt_item():
+    key = generate_item_key(2)
+    m = 10    
+    ciphertext = encrypt_item(m, key, 1)
+    print ciphertext
+    plaintext = decrypt_item(ciphertext, key)
+    assert plaintext == m, (plaintext, m)
+    
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt_item()
+        
+

### 2017-05-22 designs/homomorphic/modexpbased/rsaagain.py

@@ -1,0 +1,36 @@
+from crypto.utilities import big_prime, random_integer, modular_inverse
+
+def generate_private_key(size, e=65537):
+    p = big_prime(size)
+    d = modular_inverse(e, p - 1)
+    return p, d
+    
+def generate_public_key(private_key, q_size, e=65537):
+    p, d = private_key
+    modulus = pow(p, random_integer(q_size), p * random_integer(q_size))    
+    return modulus, e
+    
+def generate_keypair(size=33, q_size=32):
+    private_key = generate_private_key(size)
+    public_key = generate_public_key(private_key, q_size)
+    return public_key, private_key
+    
+def encrypt(m, public_key):
+    n, e = public_key
+    return pow(m, e, n)
+    
+def decrypt(c, private_key):
+    p, d = private_key
+    return pow(c, d, p)
+    
+def test_encrypt_decrypt():
+    public_key, private_key = generate_keypair()
+    for count in range(256):        
+        message = random_integer(32)
+        ciphertext = encrypt(message, public_key)
+        plaintext = decrypt(ciphertext, private_key)
+        assert plaintext == message, (plaintext, message)
+        
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-22 other/math/quicksumtest.py

@@ -20,6 +20,12 @@ else:
     raise ValueError("No such combination of 2 items found")
 assert y > x
             
+            
+# p2q2 + p3q3 + p5q5 + p7q7
+# % p2q2 == p3q3 + p5q5 + p7q7
+
+
+            
 factorization = {}            
 for element in range(2, y):
     factors = factor_integer(element)

### 2017-05-26 latex/epq/paper.tex
added docstrings

--- 2017-04-13 latex/secretkeybasedpublickeyencryption/paper.tex
@@
 \begin{abstract}
-  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas.
-The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\
+  We define algorithms for performing public key encryption and key exchange based on secret key ciphers that offer a homomorphic property.
+The nature of the design(s) allows for instantiation with any secure homomorphic cipher.
+The public keys in the presented schemes are amenable to being randomized, which offers the prospect of encrypted/anonymous public keys.
 \end{abstract}
@@
 
-The introduction of Quantum Computing and post-quantum cryptography has lead to the development of lattice based cryptographic schemes that are believed to be secure even when faced with quantum parallelism.
-Simply put, RSA and DH will need replacement at some point, and lattices seem like a promising alternative.
+Two of the most important topics in cryptography right now are: replacing RSA and DH in practice, and exploring the potential of homomorphic encryption.
+In this work we examine the application of homomorphic encryption towards the creation of simple public key encryption and key exchange algorithms.
 
-Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment.
-This property is also extremely important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers.
-We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.
+Some of the algorithms are not necessarily novel, but are more explicit and general descriptions of previous public key encryption algorithms; For example, the original Merkle-Hellman Knapsack Cryptosystem is effectively an example of a secret key homorphic cipher being used to create a public key, while inverting the public key encryption function is equivalent to performing a subset sum problem.
+We generalize the method and encodings for these techniques in this work.
+
+We will examine these systems from several perspectives: As the subset sum problem, and as a lattice problem.
 

### 2017-05-26 latex/secretkeybasedpublickeyencryption/paper.tex
added docstrings

@@
 
-\author{Anonymous\inst{1}}
-\institute{City, State \email{address@provider.com}}
-\title[\texttt Design date]{\texttt Design date}
+\author{Ella Rose\inst{1}}
+\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
+\title[Secret-Key Based Public-Key Encryption]{Secret-Key Based Public-Key Encryption}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Key Exchange]{Key Exchange}\todo{Keywords?}
+\keywords[Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption]{Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption}
 
 \begin{abstract}
-  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas.
-The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\
+ We present a perspective which demonstrates not only that secret-key based public key encryption is possible, but that well known primitives already fit into this framework.
+We describe a variety of such constructions, which are of varying complexity and security.
 \end{abstract}
@@
 \section{Introduction}
- The ability to exchange cryptographic keys over insecure channels is of vital importance to the function of the internet; Without algorithms for arranging secure communication online, much of every day life in the modern world would cease to be possible.\\
-
-The introduction of Quantum Computing and post-quantum cryptography has lead to the development of lattice based cryptographic schemes that are believed to be secure even when faced with quantum parallelism.
-Simply put, RSA and DH will need replacement at some point, and lattices seem like a promising alternative.
-
-Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment.
-This property is also extremely important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers.
-We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.
+ Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes relatively straightforward and simple.
+This paper attempts to illustrate and bring to light this fact.
+We will begin by covering "classic" cryptosystems such as Merkle's original knapsack cryptosystem, as well as modular exponentiation based cryptosystems such as DH and RSA.
 
 \section{Definitions}
-We use $+$ to denote addition, $ab$ to denote multiplication, and $\mod p$ to denote the modulo operation.
+We use $+$ to denote addition, $ab$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation. Exponentiation is denoted as $a \pow b$.
 
-\section{Algorithm}
-First, we shall define the key exchange algorithm; Then, we shall define a secret key cipher suitable for instantiating the key exchange algorithm.
+\section{Merkle's Knapsack Cryptosystem}
+\subsection{Basic Concept}
+This original cryptosystem is actually slightly more complex then some of the others that will be described.
+This is largely due to the fact that decryption involves actually solving a subset sum problem.
 
-\subsection{Key Exchange Algorithm}
-Let $pb_1$ and $pb_2$ be two encryptions of $0$ under the homomorphic secret key cipher. These two values constitute a public key. To share a secret with the owner of the public key, compute:
-\begin{align}
-    e \gets secret \\
-    c \gets (pb_1  r_1) + (pb_2 r_2) + e
-\end{align}
+The secret key cipher in this cryptosystem is modular multiplication. The plaintext numbers, as well as the modulus, are kept secret, in addition to the key.
 
-Then the value $c$ is shared with the owner of the public key.
-The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $pb_1$ is an encryption of $0$, $pb_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $pb_2$.
-So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.
+To create a public key, the secret key cipher is used to encrypt a set of numbers.
+The numbers are chosen such that utilizing the set to perform a subset sum problem will result in an easy problem to solve, allowing recovery of the summed elements.
+After the numbers have been encrypted, the set of numbers will be randomized and using them in a subset sum will result in greater difficulty inverting the sum.
 
-\subsection{Secret Key Cipher}
-Creation of the $pb_1$ and $pb_2$ values requires a secure, additively homomorphic cipher.
-We define a simple lattice based cipher which utilizes effectively the same operations as the key exchange process.
-Let $p_1$ and $p_2$ be two large numbers, where $log_2(p_1) >= log_2(p_2) * 3$; These two numbers constitute the secret key for the cipher, which in turn acts as the private key for the key exchange presented previously.\\
+The public key encryption process involves summing elements of the public key according to the bits of the message to be sent.
+Decrypting a ciphertext produced this way is equivalent to solving a subset sum problem.
 
-To encrypt a ciphertext, compute:
+The secret key is used to turn the summed elements back into the "easy version" of the numbers, so that the subset sum problem can then be solved.
 
-\begin{align}
-   c \gets (p_1 r_1) + (p_2 r_2) + m
-\end{align}
+\subsection{Key Generation}
+\subsubsection{Encryption}
+\subsubsection{Decryption}
 
-Where the $r$ values are of appropriate size relative to $p_1$ and $p_2$ \todo{what sizes are appropriate}
-While decryption is computed as:
-
-\begin{align}
-    m \gets (c \mod p_1) \mod p_2
-\end{align}
-
-\subsection{Note}
-While the decryption circuit works via two modulo operations of the base points of the lattice, this operation does not work for the public key/key exchange portion of the algorithm - The reason is because in the secret key cipher, the two different lattice points are of largely different size; In the key exchange algorithm, both points are roughly the same size, and so the double modulo operation does not function identically.
+\subsection{Randomization}
+Any homomorphic cipher requires randomization in order to be secure.
+The presented design is very simple to randomize; Continuing with the previous example, we would simply generate an additional $k_3$ and a random $r_0$ and include that in the sum as well:
 
 \section{Conclusion}
- We define a simple lattice based key exchange algorithm.
-The algorithm utilizes 2 bignum multiplications and 2 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key.
-Public keys typically occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
+
 \end{document}

### 2017-05-26 latex/secretkeybasedpublickeyencryption/secretkeybasedpublickeyencryption.tex
added docstrings

\documentclass[preprint]{iacrtrans}
\usepackage[utf8]{inputenc}

% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft,color=orange!20!white,linecolor=orange,textwidth=3cm,colorinlistoftodos]{todonotes}   % notes showed
\setlength{\marginparwidth}{3cm}
\usepackage{graphicx}
\usepackage{soul}
\graphicspath{{images/}} % end dirs with `/'
% \usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds}
\usetikzlibrary{arrows}
\usetikzlibrary{crypto.symbols}
\tikzset{shadows=no}        % Option: add shadows to XOR, ADD, etc.

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
\title[Secret-Key Based Public-Key Encryption]{Secret-Key Based Public-Key Encryption}

\begin{document}

\maketitle

% use optional argument because the \LaTeX command breaks the PDF keywords
\keywords[Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption]{Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption}

\begin{abstract}
 We present a perspective which demonstrates not only that secret-key based public key encryption is possible, but that well known primitives already fit into this framework. We describe a variety of such constructions, which are of varying complexity and security.
\end{abstract}

\todototoc
\listoftodos

\section{Introduction}
 Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes relatively straightforward and simple. This paper attempts to illustrate and bring to light this fact. We will begin by covering "classic" cryptosystems such as Merkle's original knapsack cryptosystem, as well as modular exponentiation based cryptosystems such as DH and RSA.

\section{Definitions}
We use $+$ to denote addition, $ab$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation. Exponentiation is denoted as $a ^ b$.

\section{General Properties of Homomorphic Ciphers}
\subsection{Basic Definition of Homomorphic Cipher}
A ciphertext is homomorphic if it supports $D(E(m1) * (m2)) == m1 ** m2$ where $x * y$ and $x ** y$ are some operation(s) such as addition or multiplication.

A partially homomorphic cipher is usually defined as supporting an unlimited quantity of a single type of operation on ciphertexts, such as $D(E(m1) + E(m2)) == m1 + m2$.

We will note that such a property implies the ability to perform another operation with plaintext values as the second operand, as in $D(E(m1) * m2)$ == m1 * m2. Put in other words, suppose that addition can be performed on ciphertexts; Then the sum of a ciphertext with itself would be equivalent to multiplication of the ciphertext by 2. Thus the ability to add ciphertexts to each other necessarily implies the ability to multiply a ciphertext by a plaintext amount.

\subsection{Access to Encryption Oracle}
Interestingly, with homomorphic ciphers, access to a ciphertext can be effectively equivalent to access to an encryption oracle, in that the one ciphertext can be manipulated to create new ciphertexts, the plaintext values for which will have a known relation to the previous. So in this sense, homomorphic ciphers must be secure against a type of adaptive chosen plaintext attack even if only a single plaintext is released.

\subsection{Randomization}
All homomorphic ciphers requires randomization in order to be secure.

\section{Merkle's Knapsack Cryptosystem}
\subsection{Basic Concept}
This original cryptosystem is actually slightly more complex then some of the others that will be described. This is partly due to the fact that decryption involves actually solving a subset sum problem.

The secret key cipher in this cryptosystem is modular multiplication. The plaintext numbers, as well as the modulus, are kept secret, in addition to the key.

To create a public key, the secret key cipher is used to encrypt a set of plaintext numbers. The numbers are chosen such that utilizing the set to perform a subset sum problem will result in an easy problem to solve\footnote{\label{superincreasing sequence}A superincreasing sequence}, allowing recovery of the summed elements. After the numbers have been encrypted, the set of numbers will appear randomized and using them in a subset sum will result in greater difficulty inverting the sum.

The public key encryption process involves summing elements of the public key according to the bits of the message to be sent. Decrypting a ciphertext produced this way is equivalent to solving a subset sum problem.

The secret key is used to convert the summed elements back into the "easy version" of the numbers, so that the subset sum problem can then be solved. The secret key acts as a sort of toggle that changes the numbers from one representation to another.

The plaintext numbers and modulus must be kept secret, because otherwise modular multiplication does not make a strong enough cipher. A more general and flexible approach to keeping than plaintext a secret is randomization. Indeed, all homomorphic ciphers require randomization in order to be secure against chosen plaintext attack.

\subsection{Key Generation}
\subsubsection{Encryption}
\subsubsection{Decryption}

\section{Modular Exponentiation}
Exponentiation modulo a prime is, at it's simplest, equivalent to a block cipher. In this cipher, the base is the message to be encrypted, while the encryption key is the exponent, and the modulus selects the block/key size. Ciphertexts are homomorphic with respect to multiplication, and encryption is commutative.

\subsection{Diffie-Hellman}
With this perspective, we can see that Diffie-Hellman key exchange can be described as follows: Each party selects a random encryption key and encrypts the same message, generating independently two ciphertexts $c_1$ and $c_2$. The parties exchange these ciphertexts, and each encrypts the others ciphertext using their own key.

The result of this at either end point yields a ciphertext that has been encrypted by both keys, albeit in a different order. Because encryption with this cipher is commutative, the fact that the encryption operations are applied in alternative sequencing does not matter.

Note that the homomorphic property of ciphertexts was not really utilized here - only the fact that encryption is a commutative block cipher seems to be required. Additionally, since this is only a key agreement scheme, the parties are not interested in encrypting any specific messages, or inverting any encrypted messages to the plaintexts; Both parties simply need to both arrive at the same, otherwise random value. The requirements for a key agreement algorithm appear to be simpler or easier to meet than the requirements for a public key encryption algorithm.

\subsection{RSA}
Like Diffie-Hellman, RSA utilizes modular exponentiation, but utilizes the same very simple expression quite differently. The basic modular exponentiation cipher uses the base as the message, the exponent as the encryption key, and the modulus as a block size/key size selector. There is a natural asymmetry between encryption and decryption in this cipher, in that decryption requires the modular inverse of the encryption exponent.

The problem, however, is that (in the basic cipher) anyone who knows the encryption exponent and the prime modulus can compute the decryption exponent. In order to create an asymmetric algorithm, it must be difficult to compute the decryption exponent. The solution is simple: Encrypt the modulus.

Multiplication of two integers is, in the worst case scenario, a "hard" problem.

\section{Lattice Based}
\subsection{Encryptions of 0}
\subsection{Encryptions of range(N)}
\subsection{Encryptions of 2 ** i for i in range(n)}
\subsection{Encrypted array/superposition (multi-mod)}
\subsection{Encrypted 1 And 0s} % p1m + p2r + p3r % p1 = encrypt(1); p2 = encrypt(0); p3 = encrypt(0);
\subsection{Key Exchange} % p1q1 + p2q2 (where the shared secret is q1 + q2)
\subsection{Key exchange 2} % p1q1 + p2q2 + e (D(E(m) + m) == m + m is required)

\section{Conclusion}

\end{document}

### 2017-05-26 designs/homomorphic/latticebased/modular.py

@@ -1,57 +1,59 @@
-# encrypt:
-#   c := p * (kq + m) mod n
-# decrypt:
-#   p := c * pi mod n mod k
+""" Keygen:
+        random integers p, k, n such that modular_inverse(p, n) exists
+    Encrypt:
+        c := p * (kq + m) mod n
+    Decrypt:
+        p := c * pi mod n mod k """
 
-# pq1 mod n
-# pq2 mod n
-# ppq1q2 mod n
-
-#(kq1 + m1) * (kq2 + m2)
-# kkq1q2 + kq2m1 + kq1m1 + m1m2
-
-#kq2(kq1 + m1) + m2kq1 + m1m2
-#kkq1q2 + kq2m1 + m2kq1 + m1m2
-
-# pq + e
-# e must be smaller then p
-# q should be much larger then p
-# therefore it is better to store the data in q then e
-# 0 is a problem for in either place, q, or e
-# encrypt message to randomize it before it using as q
 from crypto.utilities import big_prime, random_integer, modular_inverse, size_in_bits
 
-def generate_key(p_size=33, k_size=33, n_size=67):
-    p = big_prime(p_size)
+P_SIZE = 66
+K_SIZE = 66
+N_SIZE = 133
+Q_SIZE = 32
+
+def generate_key(p_size=P_SIZE, k_size=K_SIZE, n_size=N_SIZE):
+    """ usage: generate_key(p_size=66, k_size=66, 
+                            n_size=133) => private_key
+                            
+        Returns 3 random integers, suitable for use as a key """
+    p = random_integer(p_size)
     k = random_integer(k_size)
-    n = random_integer(n_size)
-   # assert size_in_bits(p) + size_in_bits(k) < size_in_bits(n)
-    return p, k, n
+    while True: # instead of choosing p or n as a prime, just make sure modular inverse of p exists mod n
+        n = random_integer(n_size)
+        try:
+            pi = modular_inverse(p, n)
+        except ValueError:
+            continue
+        else:
+            break
+    #assert size_in_bits(p) + size_in_bits(k) < size_in_bits(n)
+    return p, pi, k, n
     
-def encrypt(m, key, q_size=32):
-    p, k, n = key
+def encrypt(m, key, q_size=Q_SIZE):
+    """ usage: encrypt(m, key, q_size=32) => ciphertext
+    
+        Encrypts an integer m using key.
+        Returns a ciphertext integer.
+        Ciphertexts are of the form: (p * ((k * q) + m)) % n
[…]

### 2017-05-26 designs/homomorphic/latticebased/modularpublickey.py

@@ -1,13 +1,20 @@
 import crypto.designs.homomorphic.latticebased.modular as modular
 from crypto.utilities import random_integer
 
-def generate_private_key(keygen_function=modular.generate_key):                         
-    key = keygen_function(66, 66, 133)
-    return key
-    
-def generate_public_key(private_key, encryption_function=modular.encrypt):    
-    public_key = (encryption_function(1, private_key),
-                  encryption_function(1, private_key))
+DIMENSION = 3
+P_SIZE = 66
+K_SIZE = 66
+N_SIZE = 133
+R_SIZE = 32
+
+def generate_private_key(keygen_function=modular.generate_key,
+                         p_size=P_SIZE, k_size=K_SIZE, n_size=N_SIZE):                         
+    return keygen_function(p_size, k_size, n_size)
+        
+def generate_public_key(private_key, dimension=DIMENSION, encryption_function=modular.encrypt):     
+    public_key = [encryption_function(1, private_key)]        
+    for counter in range(dimension - 1):
+        public_key.append(encryption_function(0, private_key))           
     return public_key
     
 def generate_keypair(keygen_private=generate_private_key,
@@ -16,31 +23,18 @@ def generate_keypair(keygen_private=generate_private_key,
     public_key = keygen_public(private_key)
     return public_key, private_key
     
-def exchange_key(public_key, r_size=32):
-    p1, p2 = public_key
-    q1, q2 = random_integer(r_size), random_integer(r_size)
-    ciphertext = (p1 * q1) + (p2 * q2)
-    shared_secret = q1 + q2       
-    return ciphertext, shared_secret
+def encrypt(message, public_key, r_size=R_SIZE):
+    p1 = public_key[0]    
+    ciphertext = (p1 * message) + sum(point * random_integer(r_size) for point in public_key[1:])    
+    return ciphertext
     
-def recover_key(ciphertext, private_key, decryption_function=modular.decrypt):
+def decrypt(ciphertext, private_key, decryption_function=modular.decrypt):
     return decryption_function(ciphertext, private_key)
     
-def test_exchange_key_recover_key():
-    print("Generating keypair...")
-    public_key, private_key = generate_keypair()
-    print("...done.")
-    for count in range(1024):             
-        ciphertext, secret = exchange_key(public_key)
-        _secret = recover_key(ciphertext, private_key)
[…]

### 2017-05-26 designs/homomorphic/latticebased/modularsigntest.py

@@ -1,0 +1,35 @@
+import crypto.designs.homomorphic.latticebased.modular as modular
+from crypto.utilities import random_integer
+
+def generate_private_key(keygen_function=modular.generate_key):                         
+    key = keygen_function(66, 66, 133)
+    return key
+    
+def generate_public_key(private_key, encryption_function=modular.encrypt):    
+    public_key = (encryption_function(1, private_key),
+                  encryption_function(0, private_key))
+    return public_key
+    
+def generate_keypair(keygen_private=generate_private_key,
+                     keygen_public=generate_public_key):
+    private_key = keygen_private()
+    public_key = keygen_public(private_key)
+    return public_key, private_key
+    
+def verify(public_key, r_size=32):
+    p1, p2 = public_key
+    q1, q2 = random_integer(r_size), random_integer(r_size)
+    ciphertext = (p1 * q1) + (p2 * q2)
+    shared_secret = q1 + q2       
+    return ciphertext, shared_secret
+    
+def sign(data_hash, public_key private_key, decryption_function=modular.decrypt):
+    p1, p2 = public_key
+    q1 = decryption_function(data_hash, private_key)
+    data_hash -= (p1 * q1)
+    while True:        
+        if not data_hash % p2:
+            q2 = data_hash / p2
+            break
+        else:
+            p2 *= 3

### 2017-05-28 latex/secretkeybasedpublickeyencryption/paper.tex
working on paper

@@
 
-\author{Ella Rose\inst{1}}
-\institute{Paso Robles, CA\email{python_pride@protonmail.com}}
-\title[Secret-Key Based Public-Key Encryption]{Secret-Key Based Public-Key Encryption}
+\author{Ella Rose}
+\institute{Paso Robles, CA \email{python_pride@protonmail.com}}
+\title[An Efficient Public Key Encryption Algorithm]{An Efficient Public Key Encryption Algorithm}
 
@@
 \begin{abstract}
- We present a perspective which demonstrates not only that secret-key based public key encryption is possible, but that well known primitives already fit into this framework.
-We describe a variety of such constructions, which are of varying complexity and security.
+ We define a homomorphic encryption based public-key encryption construction that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
+The construction requires only addition, multiplication, and modular reduction on large integers.
+The security of the secret key cipher that underlies the scheme appears to rely only on the distribution of the random numbers generated and the correct selection of key parameters.
  \end{abstract}
@@
  Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes relatively straightforward and simple.
-This paper attempts to illustrate and bring to light this fact.
-We will begin by covering "classic" cryptosystems such as Merkle's original knapsack cryptosystem, as well as modular exponentiation based cryptosystems such as DH and RSA.
+This paper presents such a cipher, as well as a public key encryption system based on it.
 
 \section{Definitions}
-We use $+$ to denote addition, $ab$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation. Exponentiation is denoted as $a \pow b$.
+We use $+$ to denote addition, $a * b$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
 
-\section{Merkle's Knapsack Cryptosystem}
-\subsection{Basic Concept}
-This original cryptosystem is actually slightly more complex then some of the others that will be described.
-This is largely due to the fact that decryption involves actually solving a subset sum problem.
+\section{General Properties of Homomorphic Ciphers}
+\subsection{Basic Definition of Homomorphic Cipher}
+A cipher is homomorphic if it supports:
 
-The secret key cipher in this cryptosystem is modular multiplication. The plaintext numbers, as well as the modulus, are kept secret, in addition to the key.
+\begin{align}
+ D(E(m1) * (m2)) == m1 ** m2
+\end{align}
 
-To create a public key, the secret key cipher is used to encrypt a set of numbers.
-The numbers are chosen such that utilizing the set to perform a subset sum problem will result in an easy problem to solve, allowing recovery of the summed elements.
-After the numbers have been encrypted, the set of numbers will be randomized and using them in a subset sum will result in greater difficulty inverting the sum.
+where $x * y$ and $x ** y$ are some operation(s) such as addition or multiplication. The two operations do not necessarily have to be the same operation, but often times are.
 
-The public key encryption process involves summing elements of the public key according to the bits of the message to be sent.
-Decrypting a ciphertext produced this way is equivalent to solving a subset sum problem.
+A partially homomorphic cipher is usually defined as supporting an unlimited quantity of a single type of operation on ciphertexts, such as $D(E(m1) + E(m2)) == m1 + m2$.
 
-The secret key is used to turn the summed elements back into the "easy version" of the numbers, so that the subset sum problem can then be solved.
+We will note that such a property implies the ability to perform another operation with plaintext values as the second operand, as in $D(E(m1) * m2)$ == m1 * m2.
+Put in other words, suppose that addition can be performed on ciphertexts; Then the sum of a ciphertext with itself would be equivalent to multiplication of the ciphertext by 2.
+Thus the ability to add ciphertexts to each other necessarily implies the ability to multiply a ciphertext by a plaintext amount.
+
+A fully homomorphic cipher supports multiple operations on ciphertexts, usually addition and multiplication.
+The public key encryption construction presented in this paper does not require a fully homomorphic cipher, only a a partially homomorphic cipher.
+We mention it here only for the sake of completeness.
+
+\subsubsection{Access to Encryption Oracle}
+Interestingly, with homomorphic ciphers, access to a single ciphertext can be effectively equivalent to access to an encryption oracle, in that the one ciphertext can be manipulated to create new ciphertexts, the plaintext values for which will have a known relation to the previous.
+So in this sense, homomorphic ciphers must be secure against a type of adaptive chosen plaintext attack even if only a single plaintext is released.
+
+\section{Algorithm}
+First, we will define the public key encryption construction. Then, we will define a secret key cipher that is suitable for instantiating the construction.
+
+There is a publicly agreed upon modulus $n$.
+The same $n$ may always be used; It it is not secret, and only needs to be both agreed upon and large enough.
+This modulus is used by both the secret key cipher and the public key cipher.
+
+\subsection{Public Key Construction}
+\subsubsection{Basic Concept}
+A public key consists of two ciphertexts, which are homomorphic encryptions of $1$ and $0$.
+The encryption function must support the addition of ciphertexts modulo $n$, which also implies that ciphertexts can be multiplied by plaintext values.
 
 \subsection{Key Generation}
-\subsubsection{Encryption}
-\subsubsection{Decryption}
+Generation of a public key is very simple: Distribute one encryption of $1$, as well an encryption of $0$.
+The size of the public key will be determined by the size of the ciphertexts generated by the secret key cipher.
 
-\subsection{Randomization}
-Any homomorphic cipher requires randomization in order to be secure.
-The presented design is very simple to randomize; Continuing with the previous example, we would simply generate an additional $k_3$ and a random $r_0$ and include that in the sum as well:
+\begin{flalign*}
+p_1 := encrypt(1, p_k) \\
+p_2 := encrypt(0, p_k) \\
+key_{public} = (p_1, p_2)
+\end{flalign*}
+
+\subsection{Encryption}
+To encrypt a value: First the encryption of $1$ is multiplied by the plaintext message; Then, the encryption of $0$ is multiplied by a random plaintext integer; Finally, these products are summed modulo n to produce the ciphertext.
+
+\begin{flalign*}
+ciphertext := (p_1 * m) + (p_2 * r) \mod n
+\end{flalign*}
+
+\subsection{Decryption}
+Decryption simply applies the decryption circuit of the secret key cipher to the plaintext. The result will be equivalent to the message, because:
+
+\begin{flalign*}
+D(ciphertext) \equiv (1 * m) + (0 * r_1) \equiv m
+\end{flalign*}
+
+\section{Secret Key Cipher}
+\subsection{Basic Concept}
+Points on a lattice can be added together, and this effect is preserved even when a modular reduction step is applied, as long as the lattice basis and modulus are coprime.
+We exploit this modular reduction to both provide security and decrease the size of ciphertexts considerably.
+
+\subsubsection{Storing Data In the Point Or In the Error}
+When using a lattice to secretly store information, there are two places that the information can be stored: Either the information is encoded as a point on the lattice, or the information is the distance to the nearest lattice point.\\
+
+Written in notation, a point on a lattice takes the form $p * q$, while a point plus some error takes the form $p * q + e$.
+In the former, the information is recovered by dividing by $p$ - or alternatively, as in this case, multiplying by the modular multiplicative inverse of $p \mod n$.
+In the latter, the information is recovered by dividing by $p$ and taking the remainder.
+\\
+
+We need to be able to encrypt 0, so using $p * q$ where $q = m$ is not suitable - therefore we must use $p * q + e$ where $e = m$.
+By itself, this cipher would be insecure; However, it does output a randomly distributed value.
+We then encrypt this randomly distributed value as a point on the lattice to produce the ciphertext.
+
+\subsection{Encryption}
+\begin{flalign*}
+r_2 := (k_1 * r_1) + m\\
+c := k_2 * r_2 \mod n
+\end{flalign*}
+
+\subsection{Decryption}
+\begin{flalign*}
+k_i := inverse(k_2, n)\\
+r_2 := c * k_i \mod n\\
+m := r_2 \mod k_1
+\end{flalign*}
+
+\subsection{Key Generation}
+$k_1$ must be selected such that it is greater then the largest message that will be encrypted.
+If 256-bit messages are to be encrypted, then $k_1$ must be greater then 256 bits in size.
+We elect to utilize 264 bits for our $k_1$ values.
+\\
+
+If the modulus is significantly larger then $k_2$, then $k_2$ could be determined by taking the gcd of $k_2 r_i$ pairs that happened to not reduce.
+This can be remedied by ensuring that $k_2$ is large enough.
+We use choose $k_2$ by generating a 256-bit number, and subtracting it from the modulus to obtain $k_2$.
+Selecting the point starting from $n$ instead of $0$ ensures that $k_2$ is large enough.
+If $k_2 >= n - k_2$, then gcd cannot be used to extract the value of $k_2$.
+
+\section{Security Analysis}
+\subsection{Secret Key Cipher}
+The security of the secret key cipher seems to reduce almost exclusively to the distribution of values produced by $(k_1 * r_1) + m$.
+If $(k_1 * r_1) + m$ is considered to be a uniformly random value, then the secret key cipher is effectively equivalent to a One Time Pad, with a re-usable key.
+This seems implausible, and so we consider that $(k_1 * r_1) + m$  probably does not always follow such a uniformly random distribution in all cases.
+
+It appears that selecting $n$ as prime ensures a good distribution, regardless of the nature of the values of $k_1$ and $k_2$.\\
+
+\subsection{Public Key Cipher}
+The security of the public key system seems very straightforward: as long as $p_2 * r_1 \mod n$ produces a random value, then $(p_1 * m) + (p_2 * r_1) \mod n$ is effectively equivalent to applying a random key to an encoding of the message.
+As long as the key material is unpredictable and remains unknown, then there shold be no way to recover the message, given only a ciphertext and the public key.
+
+\section{Metrics}
+With the parameter sizes in this paper, a public key is 1600 bits in size, while a private key is about 1864 bits in size. Ciphertexts require 800 bits of space to encrypt 256-bit plaintext values. \\
+
+With our public domain python implementation, we can encrypt 10,000 256-bit messages in approximately 0.58 seconds, while we can decrypt 10,000 ciphertexts in approximately 0.32 seconds.
+While a python implementation may not be the fastest possible, it performs well as much of the computation time is spent on BigNum operations anyways.
+\\
+
+The private key size could be decreased a small amount at the expense of computation time; The figure presented in the paragraph prior represents the storage of $k_1, k_2, inverse(k_2, n)$.
+It is not necessary to store both $k_2$ and $inverse(k_2, n)$, as they can be calculated from each other.
+Considering the small amount of space it costs to store the inverse versus how long it takes to compute it, we choose to cache this value.
+
+\subsection{Implementation Complexity}
+The implementation complexity of the scheme is very low.
+The encryption and decryption functions for both constructions can be implemented with a single line of code each in the function body.
+Our implementation of the algorithms spans approximately 100 lines, including the documentation and comments.\\
+
+Additional code is required for supporting functions such as the generation of prime numbers (only if $n$ is being generated/not already established), computation of modular inverses, and unit testing.
+\\
+
+Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that the construction is resistant to timing side channel analysis.
+
+\section{Resource Asymmetry}
+There is a computational asymmetry between encryption and decryption, even in the simplest setting.
+Encryption takes longer then decryption, and this is something that potentially could be tuned or exploited for other cryptographic constructions.
+Perhaps there is a way to distribute large public keys, which could be used as a part of a proof-of-space or proof-of-work scheme, or perhaps password hashing.
 
 \section{Conclusion}
+We define a conceptually simple, resource-practical public-key encryption algorithm.
+The security of our construction(s) appear to rest only on the distribution of intermediately generated random data and the correct selection of parameters.
 

### 2017-05-28 latex/secretkeybasedpublickeyencryption/secretkeybasedpublickeyencryption.tex
working on paper

@@
 \subsection{Diffie-Hellman}
-With this perspective, we can see that Diffie-Hellman key exchange can be described as follows: Each party selects a random encryption key and encrypts the same message, generating independently two ciphertexts $c_1$ and $c_2$.
+With this perspective, we can see that Diffie-Hellman key exchange can be described as follows: Each party selects a random encryption key and encrypts the same pre-agreed upon message, generating independently two ciphertexts $c_1$ and $c_2$.
 The parties exchange these ciphertexts, and each encrypts the others ciphertext using their own key.
@@
 The result of this at either end point yields a ciphertext that has been encrypted by both keys, albeit in a different order.
-Because encryption with this cipher is commutative, the fact that the encryption operations are applied in alternative sequencing does not matter.
+Because encryption with this cipher is commutative, the fact that the encryption operations are applied in alternative sequencing does not matter, and both parties arrive at identical values.
 
-Note that the homomorphic property of ciphertexts was not really utilized here - only the fact that encryption is a commutative block cipher seems to be required.
+Note that the homomorphic property of ciphertexts was not really utilized explicitly here - only the fact that encryption is a commutative block cipher seems to be required.
 Additionally, since this is only a key agreement scheme, the parties are not interested in encrypting any specific messages, or inverting any encrypted messages to the plaintexts; Both parties simply need to both arrive at the same, otherwise random value.
@@
 
+\section{Operations}
+
+- Modular exponentiation:
+    - The base is the message
+    - The exponent is the encryption key
+         - The decryption key is modular_inverse(encryption_exponent, modulus=P)
+    - The prime selects the block/key size
+    - Ciphertexts support unlimited multiplications
+    - Encryption commutative (g ** x) ** y == (g ** y) ** x mod P
+        - DH is basically where both parties encrypt the same message with different keys, then encrypt the others ciphertext
+    - Much of "classical" (pre-quantum) public key crypto fits into this category (i.e. RSA and DH)
+
+- Multiplication:
+    - p * q    
+    - Ciphertexts support unlimited ciphertext additions
+        - (k * m1) + (k * m2) == k(m1 + m2)               # divide by k to obtain m1 + m2            
+    - Ciphertexts supports a logged number of ciphertext multiplications
+        - Have to keep track of the number of applied multiplications
+            - (k * m1) * (k * m2) == kkm1m2               # must divide by k ** 2 to obtain m1 * m2
+            - (k * m1) * (k * m2) * (k * m3) == kkkm1m2m3 # must divide by k ** 3 to obtain m1 * m2 * m3
+
+- Addition:
+    - k + m
+    - Ciphertexts support unlimited additions
+
+- Xor:
+    - Ciphertexts support unlimited xor operations
+
+- Transposition:
+    - Transposition can be keyed (i.e. a bitwise permutation using choice swap and rotates)
+    - Does not interfere with bitwise operations (as long as bits still "line up" it does not matter where they are)
+    - Ciphertexts support unlimited XOR operations
+    - Ciphertexts support unlimited AND operations
+    - (obviously does not make a strong cipher or I'd be using it for FHE already)
+
+- Lattices:
+    - (p1 * q1) + e
+    - p1 is the lattice basis
+    - q1 is a point on the lattice
+    - e is some error that moves the point off the lattice
+    - With some lattice ciphers, ciphertexts support D(E(m1) + m2) == m1 + m2
+        - Meaning, you can add *plaintext* values to ciphertexts
+            - Other systems only support the addition of *ciphertexts* to ciphertexts.
+
 \section{Conclusion}

### 2017-05-28 designs/homomorphic/latticebased/modular.py

@@ -8,9 +8,9 @@
 from crypto.utilities import big_prime, random_integer, modular_inverse, size_in_bits
 
 P_SIZE = 32
-K_SIZE = 66
-N_SIZE = 64
-Q_SIZE = 66
+K_SIZE = 33
+N_SIZE = 100
+Q_SIZE = 32
 
 def generate_key(p_size=P_SIZE, k_size=K_SIZE, n_size=N_SIZE):
     """ usage: generate_key(p_size=66 k_size=66, 

### 2017-05-28 designs/homomorphic/latticebased/modular2.py

@@ -1,0 +1,61 @@
+""" Keygen:
+        n is public and pre-agreed (does not need to be unique)
+        random integers p, k such that p >= n - p and k >= max_size(possible_plaintexts)
+    Encrypt:
+        c := p * (kq + m) mod n
+    Decrypt:
+        p := c * pi mod n mod k """
+
+from crypto.utilities import big_prime, random_integer, modular_inverse
+
+P_SIZE = 32
+K_SIZE = 33
+N_SIZE = 100
+Q_SIZE = 32
+
+# N = big_prime(N_SIZE)
+N = 5020634727083374867033428467921864279987846875827783570524548075331408526653673292934012044279137287122086838606810449224360138237621829626400015970097740555578731440429830737191470731438461919109460716900139034514939537967910223820430209883
+
+def generate_key(p_size=P_SIZE, k_size=K_SIZE, n=N):
+    """ usage: generate_key(p_size=66 k_size=66, 
+                            n_size=133) => private_key
+                            
+        Returns 3 integers, suitable for use as a key """              
+    assert p_size <= N_SIZE, (p_size, N_SIZE)
+    k = random_integer(k_size)      
+    while True:        
+        p = (n - random_integer(p_size))
+        try:
+            p_i = modular_inverse(p, n)
+        except ValueError:
+            pass
+        else:
+            break
+    assert p > (n - p)
+    return p, p_i, k
+    
+def encrypt(m, key, q_size=Q_SIZE, n=N):
+    """ usage: encrypt(m, key, q_size=32) => ciphertext
+    
+        Encrypts an integer m using key.
+        Returns a ciphertext integer.
+        Ciphertexts are of the form: (p * ((k * q) + m)) % n
+        Ciphertexts support addition """
+    #p, p_i, k = key
+    return (key[0] * ((key[2] * random_integer(q_size)) + m)) % n
+    
+def decrypt(ciphertext, key, n=N):
+    """ usage: decrypt(ciphertext, key) => plaintext
+    
+        Decrypts ciphertext using key.
+        Returns plaintext integer. """
+    #p, p_i, k = key    
+    return ((ciphertext * key[1]) % n) % key[2]        
+        
+def test_encrypt_decrypt():
+    from unittesting import test_symmetric_encrypt_decrypt
+    test_symmetric_encrypt_decrypt("modular", generate_key, encrypt, decrypt, plaintext_size=32, iterations=10000)
+    
+if __name__ == "__main__":
+    test_encrypt_decrypt()
+    

### 2017-05-28 designs/homomorphic/latticebased/modularpublickey2.py

@@ -1,7 +1,7 @@
-import crypto.designs.homomorphic.latticebased.modular as modular
+import crypto.designs.homomorphic.latticebased.modular2 as modular
 from crypto.utilities import random_integer
 
-DIMENSION = 3
+DIMENSION = 2
 R_SIZE = 32
 
 def generate_private_key(keygen_function=modular.generate_key):    
@@ -12,7 +12,7 @@ def generate_private_key(keygen_function=modular.generate_key):
     return keygen_function()
         
 def generate_public_key(private_key, dimension=DIMENSION, encryption_function=modular.encrypt):    
-    """ usage: generate_public_key(private_key, dimension=3,
+    """ usage: generate_public_key(private_key, dimension=2,
                                    encryption_function=modular.encrypt) => public_key
                                    
         Returns an encryption of 1, as well as encryptions of 0s.
@@ -32,14 +32,12 @@ def generate_keypair(keygen_private=generate_private_key,
     public_key = keygen_public(private_key)
     return public_key, private_key
     
-def encrypt(message, public_key, r_size=R_SIZE):
+def encrypt(message, public_key, r_size=R_SIZE, n=modular.N):
     """ usage: encrypt(message, public_key, r_size=R_SIZE) =>
         
         Returns a ciphertext.
-        r_size determines the size of each randomly generated number. """
-    p1 = public_key[0]    
-    ciphertext = (p1 * message) + sum(point * random_integer(r_size) for point in public_key[1:])    
-    return ciphertext
+        r_size determines the size of each randomly generated number. """      
+    return ((public_key[0] * message) + sum(point * random_integer(r_size) for point in public_key[1:])) % n    
     
 def decrypt(ciphertext, private_key, decryption_function=modular.decrypt):
     """ usage: decrypt(ciphertext, private_key,
@@ -50,7 +48,7 @@ def decrypt(ciphertext, private_key, decryption_function=modular.decrypt):
     
 def test_encrypt_decrypt():
     from unittesting import test_asymmetric_encrypt_decrypt
-    test_asymmetric_encrypt_decrypt("modularpublickey", generate_keypair, encrypt, decrypt, iterations=10000)
+    test_asymmetric_encrypt_decrypt("modularpublickey", generate_keypair, encrypt, decrypt, plaintext_size=32, iterations=10000)
     
 if __name__ == "__main__":
     test_encrypt_decrypt()        

### 2017-05-31 latex/secretkeybasedpublickeyencryption/paper.tex
uploading new design

@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[An Efficient Public Key Encryption Algorithm]{An Efficient Public Key Encryption Algorithm}
+\title[A Practical Public Key Encryption Algorithm]{A Practical Public Key Encryption Algorithm}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption]{Homomorphic Encryption, Symmetric Encryption, Asymmetric Encryption}
+\keywords[Homomorphic Encryption, Public Keyc Encryption]{Homomorphic Encryption, Public Key Encryption}
 
 \begin{abstract}
- We define a homomorphic encryption based public-key encryption construction that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
+ We define a public-key encryption construction that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
 The construction requires only addition, multiplication, and modular reduction on large integers.
-The security of the secret key cipher that underlies the scheme appears to rely only on the distribution of the random numbers generated and the correct selection of key parameters.
+The security of the scheme appears to rely only on the distribution of the random numbers generated and the correct selection of key parameters.
  \end{abstract}
@@
  Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes relatively straightforward and simple.
-This paper presents such a cipher, as well as a public key encryption system based on it.
+This paper presents such a public key encryption system, as well as a secret key cipher that is suitable for instantiating the system.
 
@@
 We use $+$ to denote addition, $a * b$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
+We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
 
@@
 The public key encryption construction presented in this paper does not require a fully homomorphic cipher, only a a partially homomorphic cipher.
-We mention it here only for the sake of completeness.
+We mention the term here only for the sake of completeness.
 
@@
 
-\subsection{Key Generation}
+\subsubsection{Key Generation}
 Generation of a public key is very simple: Distribute one encryption of $1$, as well an encryption of $0$.
@@
 \begin{flalign*}
+p_0 := encrypt(0, p_k) \\
 p_1 := encrypt(1, p_k) \\
-p_2 := encrypt(0, p_k) \\
-key_{public} = (p_1, p_2)
+key_{public} = (p_0, p_1)
 \end{flalign*}
 
-\subsection{Encryption}
+\subsubsection{Encryption}
 To encrypt a value: First the encryption of $1$ is multiplied by the plaintext message; Then, the encryption of $0$ is multiplied by a random plaintext integer; Finally, these products are summed modulo n to produce the ciphertext.
@@
 \begin{flalign*}
-ciphertext := (p_1 * m) + (p_2 * r) \mod n
+ciphertext := (p_0 * r) + (p_1 * m) \mod n
 \end{flalign*}
 
-\subsection{Decryption}
+\subsubsection{Decryption}
 Decryption simply applies the decryption circuit of the secret key cipher to the plaintext. The result will be equivalent to the message, because:
@@
 \begin{flalign*}
-D(ciphertext) \equiv (1 * m) + (0 * r_1) \equiv m
+D(ciphertext) \equiv (0 * r) + (1 * m)\equiv m
 \end{flalign*}
 
-\section{Secret Key Cipher}
-\subsection{Basic Concept}
-Points on a lattice can be added together, and this effect is preserved even when a modular reduction step is applied, as long as the lattice basis and modulus are coprime.
+\subsection{Secret Key Cipher}
+\subsubsection{Basic Concept}
+Points on (and off of) a lattice can be added together, and this effect is preserved even when a modular reduction step is applied, as long as the lattice basis and modulus are coprime and the point is smaller then the modulus.
 We exploit this modular reduction to both provide security and decrease the size of ciphertexts considerably.
@@
 \subsubsection{Storing Data In the Point Or In the Error}
-When using a lattice to secretly store information, there are two places that the information can be stored: Either the information is encoded as a point on the lattice, or the information is the distance to the nearest lattice point.\\
+When using a lattice to secretly store information, there are two places that the information can be stored: Either the information can be encoded as a point on the lattice, or the information can be encoded as the distance to the nearest lattice point.\\
 
 Written in notation, a point on a lattice takes the form $p * q$, while a point plus some error takes the form $p * q + e$.
-In the former, the information is recovered by dividing by $p$ - or alternatively, as in this case, multiplying by the modular multiplicative inverse of $p \mod n$.
+In the former, the information is recovered by dividing by $p$ - or alternatively, multiplying by the modular multiplicative inverse of $p \mod n$.
 In the latter, the information is recovered by dividing by $p$ and taking the remainder.
@@
 
-We need to be able to encrypt 0, so using $p * q$ where $q = m$ is not suitable - therefore we must use $p * q + e$ where $e = m$.
+We need to be able to encrypt 0, and using $p * q$ where $q = m$ is not suitable - therefore we must use $p * q + e$ where $e = m$.
 By itself, this cipher would be insecure; However, it does output a randomly distributed value.
-We then encrypt this randomly distributed value as a point on the lattice to produce the ciphertext.
+We use this randomly distributed value as a point on a secret lattice to produce the ciphertext.
 
-\subsection{Encryption}
+\subsubsection{Encryption}
 \begin{flalign*}
@@
 
-\subsection{Decryption}
+\subsubsection{Decryption}
 \begin{flalign*}
@@
 
-\subsection{Key Generation}
+\subsubsection{Key Generation}
 $k_1$ must be selected such that it is greater then the largest message that will be encrypted.
@@
 Selecting the point starting from $n$ instead of $0$ ensures that $k_2$ is large enough.
-If $k_2 >= n - k_2$, then gcd cannot be used to extract the value of $k_2$.
+If $k_2 >= n - k_2$, then gcd cannot be used to extract the value of $k_2$ even for consecutive small $q$.
 
@@
 \subsection{Secret Key Cipher}
-The security of the secret key cipher seems to reduce almost exclusively to the distribution of values produced by $(k_1 * r_1) + m$.
+The security of $k * q \mod n$ as a cipher seems to reduce almost exclusively to the distribution of values for $q$, which is determined by $(k_1 * r_1) + m$.
 If $(k_1 * r_1) + m$ is considered to be a uniformly random value, then the secret key cipher is effectively equivalent to a One Time Pad, with a re-usable key.
-This seems implausible, and so we consider that $(k_1 * r_1) + m$  probably does not always follow such a uniformly random distribution in all cases.
+This is demonstrably not the case, as perfect secrecy is not provided by this cipher - A given ciphertext decrypts to one and only one particular plaintext message.
+We consider that $(k_1 * r_1) + m \mod n$  may not always follow a uniformly random distribution.
 
@@
 
+Encryptions of 0 take the form $p * k * q \mod n$.
+Given many such samples for random $q$, can p be recovered?
+If $x := p * k$, then the expressions look like $x * q \mod n$ for random $q$, which should be secure on the assumption that $q$ is unpredictable.
+If $q$ is unpredictable, then it should not be possible to recover $p$ from encryptions of $0$.\\
+
+Encryptions of $m$ take the form $(p * k * q) + p * m \mod n$.
+Given many such samples for random q, can $p$ be recovered?
+If $p * k * q \equiv p * y \mod n$, and $y \mod n$ is unpredictable, then it should not be possible to recover $p$ from encryptions of $m$.\\
+
+Under chosen ciphertext attack, we can obtain the value of $p_i \mod k$ by submitting the value of $1$ as a ciphertext to the decryption operation.
+Similarly, we can obtain the value of $p_i * c \mod n \mod k$ for some chosen values $c$.
+It is not yet clear how this information can be leveraged to recover $p$ or $p_i$.\\
+
+If $k$ is a power of two, then $p_i \mod k$ directly reveals some of the lower bits of $p_i$. It is fantastically unlikely that $k$ will be a power of two if it is a randomly generated 264-bit number.
+
 \subsection{Public Key Cipher}
-The security of the public key system seems very straightforward: as long as $p_2 * r_1 \mod n$ produces a random value, then $(p_1 * m) + (p_2 * r_1) \mod n$ is effectively equivalent to applying a random key to an encoding of the message.
-As long as the key material is unpredictable and remains unknown, then there shold be no way to recover the message, given only a ciphertext and the public key.
+The security of the public key system seems very straightforward: as long as $p_0 * r \mod n$ produces an unpredictable random value, then $(p_1 * m) + (p_0 * r) \mod n$ is effectively equivalent to applying a random key to an encoding of the message.
+As long as the key material is unpredictable and remains unknown, then, given only a ciphertext and the public key, there shold be no way to recover the plaintext message.
 
@@
 With our public domain python implementation, we can encrypt 10,000 256-bit messages in approximately 0.58 seconds, while we can decrypt 10,000 ciphertexts in approximately 0.32 seconds.
-While a python implementation may not be the fastest possible, it performs well as much of the computation time is spent on BigNum operations anyways.
+While a python implementation may not be the fastest possible, it performs well as much of the computation time is spent on BigNum operations anyways.\\
+
+The public key encryption operation requires effectively the same amount of time as the secret key encryption operation; Consequently, there is little motivation to use the secret cipher as an encryption algorithm by itself.
 \\
 
-The private key size could be decreased a small amount at the expense of computation time; The figure presented in the paragraph prior represents the storage of $k_1, k_2, inverse(k_2, n)$.
+The private key size could be decreased a small amount at the expense of computation time; The figure cited above represents the storage of $k_1, k_2, inverse(k_2, n)$.
 It is not necessary to store both $k_2$ and $inverse(k_2, n)$, as they can be calculated from each other.
@@
 Additional code is required for supporting functions such as the generation of prime numbers (only if $n$ is being generated/not already established), computation of modular inverses, and unit testing.
+These are modest requirements that are already well facilitated by existing cryptographic libraries, and in other cases can be implemented without much complexity.
 \\
 
-Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that the construction is resistant to timing side channel analysis.
+Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches.
 
-\section{Resource Asymmetry}
-There is a computational asymmetry between encryption and decryption, even in the simplest setting.
-Encryption takes longer then decryption, and this is something that potentially could be tuned or exploited for other cryptographic constructions.
+\subsection{Resource Asymmetry}
+There is a computational asymmetry between encryption and decryption: Encryption takes longer then decryption.
+This is something that potentially could be tuned or exploited for other cryptographic constructions.
 Perhaps there is a way to distribute large public keys, which could be used as a part of a proof-of-space or proof-of-work scheme, or perhaps password hashing.

### 2017-05-31 latex/secretkeybasedpublickeyencryption/scratchtest.tex
uploading new design

--- 2017-03-14 latex/algorithmdesign/untitled-4.tex
@@
 
+\usepackage{mathtools}
 %%% END Article customizations
@@
 \begin{document}
-\maketitle
-
-\section{First section}
-
-Meet Bob and Alice.
-Bob and Alice are pen pals; they write letters to each other, and send them through the mail.
-Additionally, we will introduce Eve:  Eve has no respect for others, as well as a pathological need to try and do wrong; She is not opposed to lying, cheating, and stealing, and is very creative in this arts.
-She will go to great length to do these things if she thinks it will benefit her; Even when there is no real benefit to her, she will do such things whenever she can get away with it, simply because she can.
-
-Unfortunately, Eve is the mail carrier.
-Fortunately, Bob and Alice are aware of Eve's nature, and they seek to find ways of communicating with each other without Eve interfering.
-In order to do so, they need to enumerate all of the ways that Eve could abuse their communications, and develop appropriate counter-measures.
-
-\subsection{Lying, Cheating, and Stealing}
-
-The first and most obvious concern is Eve opening and reading the messages that are exchanged between Bob and Alice.
-
-Second, and slightly more devious, is that Eve could manipulate messages sent between the two.
-
-Third, Eve actually does not have to wait for Bob to actually send a letter to Alice. She can simply write her own letter, put Bob's name on it, and deliver it to Alice.
-
-Fourth, she could withhold or make copies of messages, and save them for delivery at some other arbitrary point in time.
-
-Finally, Eve could simply choose not to deliver the messages at all.
-
-\subsection{Solutions}
-
-For example, Bob might send Alice a christmas card with money inside, and a note that says "I am sending you \$20; I hope you have a nice holiday".
-Upon opening this, Eve could simply take the money, and leave a new note in the card that say "Sorry, I can't afford gifts this year; I hope you have a nice holiday anyways.
-PS: Please send me some money".
-Then she could easily repeat this process.
+\begin{flalign*}
+P := big\_prime\\
+p_0 := k_2 (k_1 r_1 + 0) \mod P\\
+p_1 := k_2 (k_1  r_2 + 1) \mod P\\
+key_{public} := (p_0, p_1)\\
+key_{private} := (k_1, k_2, inverse(k_2, P))\\
+\\
+c := p_0 r + p_1 m \mod P\\
+m := k_{2i} c \mod P \mod k_1
+\end{flalign*}
 

### 2017-05-31 designs/homomorphic/latticebased/modularattack.py

@@ -1,3 +1,4 @@
+from math import sqrt, log
 from random import choice as random_choice
 
 from crypto.utilities import gcd, modular_inverse
@@ -12,6 +13,7 @@ def recover_pk(points, test_count):
         gcds.add(gcd(a, b))
     
     gcds = list(gcds) # sets do not support indexing and won't work with two_points
+    return gcds
     _gcds = set()
     for count in range(test_count):
         a, b = two_points(gcds)
@@ -24,3 +26,32 @@ def recover_pk(points, test_count):
     
 def crack_ciphertext(ciphertext, pk, n):
     return ((ciphertext * modular_inverse(pk, n)) % n) % pk
+    
+def attack(points, n, count=65536):
+    differences = set()
+    sqrt_n = sqrt(n) + 1
+    for count in range(len(points)):
+        a, b = two_points(points)        
+        difference = abs(a - b)
+        if difference <= sqrt_n and difference != 0:
+      #      print("Found small enough difference: {}".format(log(difference, 2)))
+            differences.add(difference)
+       # elif difference:
+       #     print("Difference too large: {}".format(log(difference, 2)))
+            
+    return differences
+    
+def test_attack():
+    n = 513
+    sqrt_n = int(sqrt(n)) + 1
+    candidate_lengths = []
+    for p in range(1, n):
+        for k in range(1, sqrt_n):
+            points = [(p * k * q) % n for q in range(n)]
+            candidates = attack(points, n, 1024)
+            candidate_lengths.append(len(candidates))
+            
+            #if k in _key:
+            #    print "Success: ", p, k, len(_key)
+    #print sorted(candidate_lengths)
+    print("Best result removed {}% of key search space.".format(float(min(candidate_lengths)) / sqrt_n))

### 2017-05-31 designs/homomorphic/latticebased/squaremod.py

@@ -1,0 +1,76 @@
+#p = random_integer(1)
+#ps = [p]
+#for count in range(8):
+#    ps.append(ps[-1] ** 2)
+#    
+#    
+#   103
+#   201
+#   ----
+#   103
+#  000   
+# 206
+# 20703
+# 
+# 
+#p + pp * (p + pp)
+#p(p + pp) + pp(p + pp)
+#pp + ppp + ppp + pp
+#pppppppppp
+#
+#2p + 2pp * (3p + 3pp)
+#3p(2p + 2pp) + 3pp(2p + 2pp)
+#6pp + 6ppp + 6ppp + 6pppp
+# / pp
+#6 + 12p + 6pp
+
+
+#2p + 2pp * (6pp + 12ppp + 6pppp)
+#2p(6pp + 12ppp + 6pppp) + 2pp(6pp + 12ppp + 6pppp)
+#12ppp + 24pppp + 12ppppp + 12pppp + 24ppppp + 12pppppp
+#12ppp + 36pppp + 36ppppp + 12pppppp
+# / ppp
+#12 + 36p + 36pp + 12ppp
+
+
+from crypto.utilities import random_integer
+
+P_SIZE = 33
+# m size = 32
+# 
+def generate_key(p_size=P_SIZE, dimensions=3):
+    p = random_integer(p_size)
+    key = [p]
+    for count in range(dimensions - 1):
+        key.append(key[0] ** (count + 2))                
+    return key
+    
+def encrypt(m, key, r_size=32):
+    k_m = key[0]
+    k_r = (item for item in key[1:])
+    return (k_m * m) + sum(k_ri * random_integer(r_size) for k_ri in k_r)
+    
+def decrypt(ciphertext, key, depth=1):
+    k_r = (item for item in reversed(key[1:]))  
+    if depth > 1:
+        ciphertext /= key[0]   
+    for k_ri in k_r:
+        ciphertext %= k_ri    
+    return ciphertext / key[0]
+        
+def test_encrypt_decrypt():
+    from unittesting import test_symmetric_encrypt_decrypt
+    test_symmetric_encrypt_decrypt("squaremod", generate_key, encrypt, decrypt)
+    key = generate_key()#[10, 100, 1000]
+    m1 = 12389124981
+    m2 = 1000129012
+    ciphertext1 = encrypt(m1, key)
+    ciphertext2 = encrypt(m2, key)
+    test_function = lambda a, b: (a * b) + (a * b) + (b * b)
[…]

### 2017-05-31 designs/homomorphic/latticebased/squaremodpublickey.py

@@ -1,0 +1,55 @@
+import crypto.designs.homomorphic.latticebased.squaremod2 as secretkey
+from crypto.utilities import random_integer
+
+DIMENSION = 2
+R_SIZE = 32
+
+def generate_private_key(keygen_function=secretkey.generate_key):    
+    """ usage: generate_private_key(keygen_function=secretkey.generate_key,
+                                    p_size=P_SIZE, k_size=K_SIZE, n_size=N_SIZE) => private_key
+                                    
+        Returns 3 numbers, suitable for use as a private key. """
+    return keygen_function()
+        
+def generate_public_key(private_key, dimension=DIMENSION, encryption_function=secretkey.encrypt):    
+    """ usage: generate_public_key(private_key, dimension=2,
+                                   encryption_function=secretkey.encrypt) => public_key
+                                   
+        Returns an encryption of 1, as well as encryptions of 0s.
+        Increasing the dimension should increase the hardness of the public key encryption operation, but will also increase the size of the public key. """
+    public_key = [encryption_function(1, private_key)]        
+    for counter in range(dimension - 1):
+        public_key.append(encryption_function(0, private_key))           
+    return public_key
+    
+def generate_keypair(keygen_private=generate_private_key,
+                     keygen_public=generate_public_key):
+    """ usage: generate_keypair(keygen_private=generate_private_key,
+                                keygen_public=generate_public_key) => public_key, private_key
+                                
+        Returns a public key and a private key. """        
+    private_key = keygen_private()
+    public_key = keygen_public(private_key)
+    return public_key, private_key
+    
+def encrypt(message, public_key, r_size=R_SIZE, n=secretkey.N):
+    """ usage: encrypt(message, public_key, r_size=R_SIZE) =>
+        
+        Returns a ciphertext.
+        r_size determines the size of each randomly generated number. """      
+    return ((public_key[0] * message) + sum(point * random_integer(r_size) for point in public_key[1:])) % n    
+    
+def decrypt(ciphertext, private_key, decryption_function=secretkey.decrypt):
+    """ usage: decrypt(ciphertext, private_key,
+                       decryption_function=secretkey.decrypt) => plaintext
+                       
+        Returns plaintext. """
+    return decryption_function(ciphertext, private_key)
+    
+def test_encrypt_decrypt():
+    from unittesting import test_asymmetric_encrypt_decrypt
[…]

### 2017-05-31 designs/homomorphic/latticebased/unittesting.py

@@ -49,14 +49,22 @@ def test_asymmetric_encrypt_decrypt(algorithm_name, generate_keypair, encrypt, d
     try:
         public_sizes = [size_in_bits(item) for item in public_key]
     except TypeError:
-        public_key_sizes = [size_in_bits(public_key)]        
+        try:
+            public_sizes = [size_in_bits(public_key)]        
+        except TypeError:
+            public_sizes = []
     try:
         private_sizes = [size_in_bits(item) for item in private_key]
     except TypeError:
-        private_sizes = [size_in_bits(private_key)]
-        
-    print("Public key size : {}".format(sum(public_sizes)))
-    print("Private key size: {}".format(sum(private_sizes)))
+        try:
+            private_sizes = [size_in_bits(private_key)]
+        except TypeError:
+            private_sizes = []
+            
+    if public_sizes:
+        print("Public key size : {}".format(sum(public_sizes)))
+    if private_sizes:
+        print("Private key size: {}".format(sum(private_sizes)))
     print("Ciphertext size : {}".format(size_in_bits(encrypt(random_integer(32), public_key))))
     print("(sizes are in bits)")
     print("{} unit test passed".format(algorithm_name))
@@ -78,9 +86,13 @@ def test_symmetric_encrypt_decrypt(algorithm_name, generate_key, encrypt, decryp
            
     try:
         sizes = [size_in_bits(item) for item in key]
-    except:
-        sizes = [size_in_bits(key)]
-    print("Key size: {}".format(sum(sizes)))
+    except TypeError:
+        try:
+            sizes = [size_in_bits(key)]
+        except TypeError:
+            sizes = []
+    if sizes:                
+        print("Key size: {}".format(sum(sizes)))
     print("Ciphertext size: {}".format(size_in_bits(encrypt(random_integer(plaintext_size), key))))
     print("{} unit test passed".format(algorithm_name))
     

### 2017-05-31 designs/homomorphic/modexpbased/signaturetest2.py

@@ -1,0 +1,68 @@
+# private key:
+#   small primes such that the product of all of them is smaller then the modulus N
+# public key:
+#   homomorphic encryptions of the private key primes; ciphertexts support multiplication
+
+# sign:
+#   decrypt value with private key cipher and check for factors according to the private key
+#   release the corresponding indices according to the primes in the factorization
+#   for example:
+#       private_key = [2, 3, 5, 7, 11]
+#       number = 70
+#       factors     = [2,   5,  7,   ] # 2 * 5 * 7 = 10 * 7 = 70
+#       signature   = [1, 0, 1, 1, 0 ]
+#
+# verify:
+#   multiply the elements indicated by the signature modulo N
+#   check that the product equals? is close? to number
+#       signature  = [1, 0, 1, 1, 0]
+#       public_key = [a, b, c, d, e]
+#       verifier =    a   * c * d  mod N
+#       check verifier?
+from crypto.utilities import prime_generator, random_integer, modular_inverse
+
+generator = prime_generator()
+primes = [next(generator) for count in range(44)]
+N = 1
+for prime in primes:
+    N *= prime
+    
+def generate_private_key(n=N):    
+    while True:
+        e = random_integer(32)
+        try:
+            d = modular_inverse(e, n)
+        except ValueError:
+            continue
+        else:
+            break
+    assert e < n
+    return e, d
+    
+def generate_public_key(private_key, n=N):   
+    e, d = private_key
+    return [pow(prime, e, n) for prime in primes]
+    
+def sign(message, private_key, n=N):
+    e, d = private_key
+    number = pow(message, d, n)    
+    
+    signature = [0] * 44
+    for index, prime in enumerate(primes):        
+        exponent = 0
+        while number % prime == 0:
+            print number, prime, exponent
+            exponent += 1
+            number /= prime
+        
+        signature[index] = exponent
+    return signature
+    
+def verify(signature, message, public_key, n=N):
+    verifier = 1
+    for index, exponent in enumerate(signature):
+        if exponent:
+            verifier *= primes[index] ** exponent
+    return verifier
+
+    

### 2017-05-31 latex/secretkeybasedpublickeyencryption2/paper.tex
moved paper to new folder

--- 2017-05-31 latex/secretkeybasedpublickeyencryption/paper.tex
@@
 The construction requires only addition, multiplication, and modular reduction on large integers.
-The security of the scheme appears to rely only on the distribution of the random numbers generated and the correct selection of key parameters.
  \end{abstract}
@@
 A fully homomorphic cipher supports multiple operations on ciphertexts, usually addition and multiplication.
-The public key encryption construction presented in this paper does not require a fully homomorphic cipher, only a a partially homomorphic cipher.
+The public key encryption construction presented in this paper does not require a fully homomorphic cipher, only a partially homomorphic cipher.
 We mention the term here only for the sake of completeness.
@@
 \subsubsection{Basic Concept}
-Points on (and off of) a lattice can be added together, and this effect is preserved even when a modular reduction step is applied, as long as the lattice basis and modulus are coprime and the point is smaller then the modulus.
+Points on (and off of) a lattice can be added together, and this effect is preserved even after being multiplied modulo a prime.
 We exploit this modular reduction to both provide security and decrease the size of ciphertexts considerably.
 
-\subsubsection{Storing Data In the Point Or In the Error}
-When using a lattice to secretly store information, there are two places that the information can be stored: Either the information can be encoded as a point on the lattice, or the information can be encoded as the distance to the nearest lattice point.\\
+Multiple points can be superpositioned together via the addition operator, which provides a mechanism for randomizing the ciphertext.
+Given a point in the form of $(p * q_1) + (p ^ 2 * q_2)$, $p * q_1$ can be recovered by computing $(p * q_1) + (p ^ 2 * q_2) \mod p ^ 2$.
+This process can be repeated for successive powers of $p$.
+We utilize a three-tiered ciphertext using this technique, where the base point encodes the messages, and the squared/cubed points are both used for randomization.
 
-Written in notation, a point on a lattice takes the form $p * q$, while a point plus some error takes the form $p * q + e$.
-In the former, the information is recovered by dividing by $p$ - or alternatively, multiplying by the modular multiplicative inverse of $p \mod n$.
-In the latter, the information is recovered by dividing by $p$ and taking the remainder.
-\\
+\subsubsection{Key Generation}
+\begin{flalign*}
+p := random\_integer\\
+k := random\_integer\\
+k_i := inverse(k, n)
+\end{flalign*}
 
-We need to be able to encrypt 0, and using $p * q$ where $q = m$ is not suitable - therefore we must use $p * q + e$ where $e = m$.
-By itself, this cipher would be insecure; However, it does output a randomly distributed value.
-We use this randomly distributed value as a point on a secret lattice to produce the ciphertext.
+\subsubsection{Key Generation}
+$p$ must be selected such that it is greater then the largest message that will be encrypted.
+If 256-bit messages are to be encrypted, then $p$ must be greater then 256 bits in size.
+We elect to utilize 264 bits for our $p$ value.
+Similarly, if $k$ is to remain unguessable even in the face of an adversary with a quantum computer, then $k$ should be at least 256 bits in size.
+We choose $k$ as an offset from $n$, rather then as an offset from $0$ - this ensures that $k * q \mod n$ is always large enough to reduce, even if $q$ is small.
+This results in a larger value for $k$.\\
 
@@
 \begin{flalign*}
-r_2 := (k_1 * r_1) + m\\
-c := k_2 * r_2 \mod n
+t := (p * m) + (p ^ 2 * random\_integer) + (p ^ 3 * random\_integer)\\
+c: = (k * t) \mod n
 \end{flalign*}
@@
 \begin{flalign*}
-k_i := inverse(k_2, n)\\
-r_2 := c * k_i \mod n\\
-m := r_2 \mod k_1
+t := (k_i * c) \mod n\\
+t := t \mod p ^ 3 \mod p ^ 2\\
+m := t / p
 \end{flalign*}
-
-\subsubsection{Key Generation}
-$k_1$ must be selected such that it is greater then the largest message that will be encrypted.
-If 256-bit messages are to be encrypted, then $k_1$ must be greater then 256 bits in size.
-We elect to utilize 264 bits for our $k_1$ values.
-\\
-
-If the modulus is significantly larger then $k_2$, then $k_2$ could be determined by taking the gcd of $k_2 r_i$ pairs that happened to not reduce.
-This can be remedied by ensuring that $k_2$ is large enough.
-We use choose $k_2$ by generating a 256-bit number, and subtracting it from the modulus to obtain $k_2$.
-Selecting the point starting from $n$ instead of $0$ ensures that $k_2$ is large enough.
-If $k_2 >= n - k_2$, then gcd cannot be used to extract the value of $k_2$ even for consecutive small $q$.
 
@@
 \subsection{Secret Key Cipher}
-The security of $k * q \mod n$ as a cipher seems to reduce almost exclusively to the distribution of values for $q$, which is determined by $(k_1 * r_1) + m$.
-If $(k_1 * r_1) + m$ is considered to be a uniformly random value, then the secret key cipher is effectively equivalent to a One Time Pad, with a re-usable key.
+The secret key cipher effectively consists of two separate sections; In the first section, a randomized ciphertext is created.
+The second section is a re-ordering of the ciphertext blocks via multiplication modulo n.
+This section exists to make the first section "harder" then it would be if it was not reduced modulo n.
+Note that $k$ is not sufficient to decrypt a given ciphertext.
+An adversary must acquire both $k$ and $p$, or find a way to recover $p$ without $k$.
+Given only $k$ and ciphertexts, it should still be difficult to recover a plaintext.\\
+
+The security of $k * q \mod n$ as a cipher seems to reduce almost exclusively to the distribution of values for $q$, which is determined by $(p * m) + (p ^ 2 * r_0) + (p ^ 3 * r_1)$.
+If this was a uniformly random value, then the secret key cipher would be effectively equivalent to a One Time Pad, with a re-usable key.
 This is demonstrably not the case, as perfect secrecy is not provided by this cipher - A given ciphertext decrypts to one and only one particular plaintext message.
-We consider that $(k_1 * r_1) + m \mod n$  may not always follow a uniformly random distribution.
+We conclude that $(p * m) + (p ^ 2 * r_0) + (p ^ 3 * r_1)\mod n$  may not always follow a uniformly random distribution.\\
 
-It appears that selecting $n$ as prime ensures a good distribution, regardless of the nature of the values of $k_1$ and $k_2$.\\
+Encryptions of 0 take the form $x := k * ((p ^ 2 * r_0) + (p ^ 3 * r_1)) \mod n$.
+Given many such samples for random $r$, can $p$ or $k$ be recovered?
+Set $q := (p ^ 2 * r_0) + (p ^ 3 * r_1) \mod n$; If $q$ is unpredictable, then it should not be possible to recover $p$ or $k$ from encryptions of $0$.\\
 
-Encryptions of 0 take the form $p * k * q \mod n$.
-Given many such samples for random $q$, can p be recovered?
-If $x := p * k$, then the expressions look like $x * q \mod n$ for random $q$, which should be secure on the assumption that $q$ is unpredictable.
-If $q$ is unpredictable, then it should not be possible to recover $p$ from encryptions of $0$.\\
+Under chosen ciphertext attack, we can obtain the value of $(k_i \mod p ^ 3 \mod p ^ 2) / p$ by submitting the value of $1$ as a ciphertext to the decryption operation.
+Similarly, we can obtain the value of $(c * k_i \mod p ^ 3 \mod p ^ 2) / p$ for some chosen values $c$.
+It is not yet clear how this information can be leveraged to recover $p$ or $k_i$.\\
 
-Encryptions of $m$ take the form $(p * k * q) + p * m \mod n$.
-Given many such samples for random q, can $p$ be recovered?
-If $p * k * q \equiv p * y \mod n$, and $y \mod n$ is unpredictable, then it should not be possible to recover $p$ from encryptions of $m$.\\
-
-Under chosen ciphertext attack, we can obtain the value of $p_i \mod k$ by submitting the value of $1$ as a ciphertext to the decryption operation.
-Similarly, we can obtain the value of $p_i * c \mod n \mod k$ for some chosen values $c$.
-It is not yet clear how this information can be leveraged to recover $p$ or $p_i$.\\
-
-If $k$ is a power of two, then $p_i \mod k$ directly reveals some of the lower bits of $p_i$. It is fantastically unlikely that $k$ will be a power of two if it is a randomly generated 264-bit number.
+It is possible that somehow the relation between $p, p ^ 2, p ^3$ might be leveraged against the design.
+In such a situation, $p ^ 2$ and $p ^ 3$ can be changed to random numbers that are larger then $p ^ 2$ and $p ^ 3$, respectively.
+Currently, these points are generated as exponents of $p$ to save space, but this is not a requirement for the function of the construction.
 
@@
 
+If necessary, the construction can be generalized to use larger quantities of randomization points. This would increase the size of the public key.
+
 \section{Metrics}
-With the parameter sizes in this paper, a public key is 1600 bits in size, while a private key is about 1864 bits in size. Ciphertexts require 800 bits of space to encrypt 256-bit plaintext values. \\
+With the parameter sizes in this paper, a public key is 2800 bits in size, while a private key is about 4400 bits in size.
+Ciphertexts require 1400 bits of space to encrypt 256-bit plaintext values.
+\\
 
-With our public domain python implementation, we can encrypt 10,000 256-bit messages in approximately 0.58 seconds, while we can decrypt 10,000 ciphertexts in approximately 0.32 seconds.
+With our public domain python implementation, we can encrypt with the public key 10,000 256-bit messages in approximately 0.66 seconds, while we can decrypt 10,000 ciphertexts in approximately 0.93 seconds.
 While a python implementation may not be the fastest possible, it performs well as much of the computation time is spent on BigNum operations anyways.\\
 
-The public key encryption operation requires effectively the same amount of time as the secret key encryption operation; Consequently, there is little motivation to use the secret cipher as an encryption algorithm by itself.
-\\
-
-The private key size could be decreased a small amount at the expense of computation time; The figure cited above represents the storage of $k_1, k_2, inverse(k_2, n)$.
-It is not necessary to store both $k_2$ and $inverse(k_2, n)$, as they can be calculated from each other.
-Considering the small amount of space it costs to store the inverse versus how long it takes to compute it, we choose to cache this value.
+The private key size could be decreased at the expense of computation time; The figure cited above represents the storage of $p, p ^ 2, p ^ 3, k, inverse(k, n)$.
+It is not necessary to store $p ^ 2$, $p ^ 3$, or $inverse(k, n)$.
+Storing only $p$ and $k$ yields private key sizes of about 1000 bits.
+Considering the relatively small amount of space required, compared to how long it takes to compute a square/cube/modular inverse, we choose to cache these values.
 
@@
 The implementation complexity of the scheme is very low.
-The encryption and decryption functions for both constructions can be implemented with a single line of code each in the function body.
+The encryption and decryption functions for the public key construction can be implemented with a single line of code each in the function body.
 Our implementation of the algorithms spans approximately 100 lines, including the documentation and comments.\\
@@
 
-Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches.
-
-\subsection{Resource Asymmetry}
-There is a computational asymmetry between encryption and decryption: Encryption takes longer then decryption.
-This is something that potentially could be tuned or exploited for other cryptographic constructions.
-Perhaps there is a way to distribute large public keys, which could be used as a part of a proof-of-space or proof-of-work scheme, or perhaps password hashing.
+Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches in the algorithm.
 
@@
 We define a conceptually simple, resource-practical public-key encryption algorithm. 
-The security of our construction(s) appear to rest only on the distribution of intermediately generated random data and the correct selection of parameters.
-
 \end{document}

### 2017-06-08 latex/qtpie/paper.tex
backing up work

--- 2017-05-31 latex/secretkeybasedpublickeyencryption2/paper.tex
@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[A Practical Public Key Encryption Algorithm]{A Practical Public Key Encryption Algorithm}
+\title[$q + p_i e$ Public Key Algorithms]{$q + p_i e$ Public Key Algorithms}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Homomorphic Encryption, Public Keyc Encryption]{Homomorphic Encryption, Public Key Encryption}
+\keywords[Homomorphic Encryption, Public Key Encryption]{Homomorphic Encryption, Public Key Encryption}
 
 \begin{abstract}
- We define a public-key encryption construction that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
+ We define an extremely simple key exchange algorithm that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
 The construction requires only addition, multiplication, and modular reduction on large integers.
+The name "qtpie" is a play on the expression that appears during decryption, $q + p_i e$.
  \end{abstract}
@@
 \section{Introduction}
- Ciphers that support homomorphic operations on ciphertexts are very attractive because they tend to make the creation of public key encryption schemes relatively straightforward and simple.
-This paper presents such a public key encryption system, as well as a secret key cipher that is suitable for instantiating the system.
 
@@
 We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
-
-\section{General Properties of Homomorphic Ciphers}
-\subsection{Basic Definition of Homomorphic Cipher}
-A cipher is homomorphic if it supports:
-
-\begin{align}
- D(E(m1) * (m2)) == m1 ** m2
-\end{align}
-
-where $x * y$ and $x ** y$ are some operation(s) such as addition or multiplication. The two operations do not necessarily have to be the same operation, but often times are.
-
-A partially homomorphic cipher is usually defined as supporting an unlimited quantity of a single type of operation on ciphertexts, such as $D(E(m1) + E(m2)) == m1 + m2$.
-
-We will note that such a property implies the ability to perform another operation with plaintext values as the second operand, as in $D(E(m1) * m2)$ == m1 * m2.
-Put in other words, suppose that addition can be performed on ciphertexts; Then the sum of a ciphertext with itself would be equivalent to multiplication of the ciphertext by 2.
-Thus the ability to add ciphertexts to each other necessarily implies the ability to multiply a ciphertext by a plaintext amount.
-
-A fully homomorphic cipher supports multiple operations on ciphertexts, usually addition and multiplication.
-The public key encryption construction presented in this paper does not require a fully homomorphic cipher, only a partially homomorphic cipher.
-We mention the term here only for the sake of completeness.
-
-\subsubsection{Access to Encryption Oracle}
-Interestingly, with homomorphic ciphers, access to a single ciphertext can be effectively equivalent to access to an encryption oracle, in that the one ciphertext can be manipulated to create new ciphertexts, the plaintext values for which will have a known relation to the previous.
-So in this sense, homomorphic ciphers must be secure against a type of adaptive chosen plaintext attack even if only a single plaintext is released.
+We use the function $random(k)$ to indicate the generation of of a random $k$-bit integer.
 
 \section{Algorithm}
-First, we will define the public key encryption construction. Then, we will define a secret key cipher that is suitable for instantiating the construction.
+There is a publicly agreed upon modulus $N$. The same $N$ may always be used. It must be prime; It it is not secret, and only needs to be both agreed upon and large enough.
 
-There is a publicly agreed upon modulus $n$.
-The same $n$ may always be used; It it is not secret, and only needs to be both agreed upon and large enough.
-This modulus is used by both the secret key cipher and the public key cipher.
-
-\subsection{Public Key Construction}
-\subsubsection{Basic Concept}
-A public key consists of two ciphertexts, which are homomorphic encryptions of $1$ and $0$.
-The encryption function must support the addition of ciphertexts modulo $n$, which also implies that ciphertexts can be multiplied by plaintext values.
-
-\subsubsection{Key Generation}
-Generation of a public key is very simple: Distribute one encryption of $1$, as well an encryption of $0$.
-The size of the public key will be determined by the size of the ciphertexts generated by the secret key cipher.
+\subsection{Basic Concept}
+Consider the following function:
 
 \begin{flalign*}
-p_0 := encrypt(0, p_k) \\
-p_1 := encrypt(1, p_k) \\
-key_{public} = (p_0, p_1)
+c := (p * q) + e \mod N
 \end{flalign*}
 
-\subsubsection{Encryption}
-To encrypt a value: First the encryption of $1$ is multiplied by the plaintext message; Then, the encryption of $0$ is multiplied by a random plaintext integer; Finally, these products are summed modulo n to produce the ciphertext.
+We can recover $e$ from $c$ using the following algorithm:
 
 \begin{flalign*}
-ciphertext := (p_0 * r) + (p_1 * m) \mod n
+p_i := inverse(p, N)\\
+t := (c * p_i) \mod N\\
+t \equiv q + p_i e\\
+q := t \mod p_i\\
+t := t - q \\
+t \equiv p_i e
+e := t / p_i
 \end{flalign*}
 
-\subsubsection{Decryption}
-Decryption simply applies the decryption circuit of the secret key cipher to the plaintext. The result will be equivalent to the message, because:
+The step $q := q + p_i e \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$.
+If $p_i$ is generated from a random $p$, this latter condition is unlikely to be met for any sizable value of e, for the generated $p_i$ will likely be close to $log_2(N)$ bits in size.
+Consequently, during key generation, we must generate a random $p_i$ of appropriate size and generate $p$ from it and $N$ via the $inverse$ function.
+The value $p$ serves as an encryption key, while the value $p_i$ serves as the decryption key.
+
+A public key consists of an encryption of the encryption key $p$ in the form of $p q \mod n$.
+The inability to selectively generate a small inverse of the public key ensures that supplying the public key to the decryption algorithm will not produce correct plaintext for any sizable message value $e$.
+
+\subsection{Key Generation}
+\begin{flalign*}
+key_{pr} := N - random(m_{size} + 1)\\
+r := random(k_{size})\\
+key_{pub} := inverse(key_{pr}, N) * r) \mod N\\
+\end{flalign*}
+
+In the above, $m_{size}$ is equal to the size of the shared secret material in bits.
+$k_{size}$ is a security parameter that is equal to the size of the randomly generated value in bits.
+We elect to set $m_{size}$ and $k_{size}$ to be 256 bits.
+
+$key_{pr}$ must be selected such that $key_{pr} e < N$, as well as $key_{pr} > r q$, where $q$ is the security parameter of the public key operation.
+
+\subsection{Exchanging Keys}
+To exchange a secret key: multiply the public key by a random value, then add the secret key to the result modulo $N$.
 
 \begin{flalign*}
-D(ciphertext) \equiv (0 * r) + (1 * m)\equiv m
+secret := random(m_{size})\\
+ciphertext := (key_{pub} random(q_{size}) + secret \mod N\\
 \end{flalign*}
 
-\subsection{Secret Key Cipher}
-\subsubsection{Basic Concept}
-Points on (and off of) a lattice can be added together, and this effect is preserved even after being multiplied modulo a prime.
-We exploit this modular reduction to both provide security and decrease the size of ciphertexts considerably.
-
-Multiple points can be superpositioned together via the addition operator, which provides a mechanism for randomizing the ciphertext.
-Given a point in the form of $(p * q_1) + (p ^ 2 * q_2)$, $p * q_1$ can be recovered by computing $(p * q_1) + (p ^ 2 * q_2) \mod p ^ 2$.
-This process can be repeated for successive powers of $p$.
-We utilize a three-tiered ciphertext using this technique, where the base point encodes the messages, and the squared/cubed points are both used for randomization.
-
-\subsubsection{Key Generation}
-\begin{flalign*}
-p := random\_integer\\
-k := random\_integer\\
-k_i := inverse(k, n)
-\end{flalign*}
-
-\subsubsection{Key Generation}
-$p$ must be selected such that it is greater then the largest message that will be encrypted.
-If 256-bit messages are to be encrypted, then $p$ must be greater then 256 bits in size.
-We elect to utilize 264 bits for our $p$ value.
-Similarly, if $k$ is to remain unguessable even in the face of an adversary with a quantum computer, then $k$ should be at least 256 bits in size.
-We choose $k$ as an offset from $n$, rather then as an offset from $0$ - this ensures that $k * q \mod n$ is always large enough to reduce, even if $q$ is small.
-This results in a larger value for $k$.\\
-
-\subsubsection{Encryption}
-\begin{flalign*}
-t := (p * m) + (p ^ 2 * random\_integer) + (p ^ 3 * random\_integer)\\
-c: = (k * t) \mod n
-\end{flalign*}
-
-\subsubsection{Decryption}
-\begin{flalign*}
-t := (k_i * c) \mod n\\
-t := t \mod p ^ 3 \mod p ^ 2\\
-m := t / p
+\subsection{Key Recover}
+The shared secret can be recover from the ciphertext via the following algorithm:
+\begin{flialign*}
+pie_q := ciphertext key_{pr} \mod N\\
+q := pie_q \mod key_{pr}\\
+pie := pie_q - q\\
+e := pie / pi
 \end{flalign*}
@@
 \section{Security Analysis}
-\subsection{Secret Key Cipher}
-The secret key cipher effectively consists of two separate sections; In the first section, a randomized ciphertext is created.
-The second section is a re-ordering of the ciphertext blocks via multiplication modulo n.
-This section exists to make the first section "harder" then it would be if it was not reduced modulo n.
-Note that $k$ is not sufficient to decrypt a given ciphertext.
-An adversary must acquire both $k$ and $p$, or find a way to recover $p$ without $k$.
-Given only $k$ and ciphertexts, it should still be difficult to recover a plaintext.\\
-
-The security of $k * q \mod n$ as a cipher seems to reduce almost exclusively to the distribution of values for $q$, which is determined by $(p * m) + (p ^ 2 * r_0) + (p ^ 3 * r_1)$.
-If this was a uniformly random value, then the secret key cipher would be effectively equivalent to a One Time Pad, with a re-usable key.
-This is demonstrably not the case, as perfect secrecy is not provided by this cipher - A given ciphertext decrypts to one and only one particular plaintext message.
-We conclude that $(p * m) + (p ^ 2 * r_0) + (p ^ 3 * r_1)\mod n$  may not always follow a uniformly random distribution.\\
-
-Encryptions of 0 take the form $x := k * ((p ^ 2 * r_0) + (p ^ 3 * r_1)) \mod n$.
-Given many such samples for random $r$, can $p$ or $k$ be recovered?
-Set $q := (p ^ 2 * r_0) + (p ^ 3 * r_1) \mod n$; If $q$ is unpredictable, then it should not be possible to recover $p$ or $k$ from encryptions of $0$.\\
-
-Under chosen ciphertext attack, we can obtain the value of $(k_i \mod p ^ 3 \mod p ^ 2) / p$ by submitting the value of $1$ as a ciphertext to the decryption operation.
-Similarly, we can obtain the value of $(c * k_i \mod p ^ 3 \mod p ^ 2) / p$ for some chosen values $c$.
-It is not yet clear how this information can be leveraged to recover $p$ or $k_i$.\\
-
-It is possible that somehow the relation between $p, p ^ 2, p ^3$ might be leveraged against the design.
-In such a situation, $p ^ 2$ and $p ^ 3$ can be changed to random numbers that are larger then $p ^ 2$ and $p ^ 3$, respectively.
-Currently, these points are generated as exponents of $p$ to save space, but this is not a requirement for the function of the construction.
-
 \subsection{Public Key Cipher}
-The security of the public key system seems very straightforward: as long as $p_0 * r \mod n$ produces an unpredictable random value, then $(p_1 * m) + (p_0 * r) \mod n$ is effectively equivalent to applying a random key to an encoding of the message.
-As long as the key material is unpredictable and remains unknown, then, given only a ciphertext and the public key, there shold be no way to recover the plaintext message.
-
-If necessary, the construction can be generalized to use larger quantities of randomization points. This would increase the size of the public key.
 
 \section{Metrics}
-With the parameter sizes in this paper, a public key is 2800 bits in size, while a private key is about 4400 bits in size.
-Ciphertexts require 1400 bits of space to encrypt 256-bit plaintext values.
-\\
-
-With our public domain python implementation, we can encrypt with the public key 10,000 256-bit messages in approximately 0.66 seconds, while we can decrypt 10,000 ciphertexts in approximately 0.93 seconds.
-While a python implementation may not be the fastest possible, it performs well as much of the computation time is spent on BigNum operations anyways.\\
-
-The private key size could be decreased at the expense of computation time; The figure cited above represents the storage of $p, p ^ 2, p ^ 3, k, inverse(k, n)$.
-It is not necessary to store $p ^ 2$, $p ^ 3$, or $inverse(k, n)$.
-Storing only $p$ and $k$ yields private key sizes of about 1000 bits.
-Considering the relatively small amount of space required, compared to how long it takes to compute a square/cube/modular inverse, we choose to cache these values.
 

### 2017-06-08 designs/homomorphic/latticebased/qtpiekeyexchange.py

@@ -1,5 +1,3 @@
-# need to randomize message
-
 from math import log
 
 from crypto.utilities import random_integer, modular_inverse, big_prime, modular_subtraction
@@ -8,7 +6,10 @@ N = 9053982199960166701001649843353809235060184806550933505038277816869787762296
 
 #1 + 33 + 32 = 66
 
+# prq + e
+# q + pirie
 
+#65 + 97 + 32 =
 def generate_private_key(pi_size=65, n=N):
     pi = random_integer(pi_size)    
     assert log(n, 2) - log(pi, 2) > 256, log(n, 2) - log(pi, 2)
@@ -26,22 +27,24 @@ def generate_keypair():
     public_key = generate_public_key(private_key)
     return public_key, private_key
     
-def encrypt(m, public_key, q_size=32, n=N): 
-    return ((public_key * random_integer(q_size)) + m) % n
+def exchange_key(public_key, q_size=32, n=N): 
+    assert n == N
+    e = random_integer(q_size)        
+    return ((public_key * random_integer(q_size)) + e) % n, e % n
         
     # pq + e == q + pie mod n
     
-def decrypt(ciphertext, private_key, n=N):    
+def recover_key(ciphertext, private_key, n=N):
     pi = private_key
     pie_q = (pi * ciphertext) % n
     q = pie_q % pi
     pie = pie_q - q
-    return pie / pi    
+    return pie / pi   
     
-def test_encrypt_decrypt():
-    from unittesting import test_asymmetric_encrypt_decrypt
-    test_asymmetric_encrypt_decrypt("qtpiepublickey", generate_keypair, encrypt, decrypt, iterations=10000)
+def test_exchange_key_recover_key():
+    from unittesting import test_key_exchange
+    test_key_exchange("qtpiekeyexchange", generate_keypair, exchange_key, recover_key, iterations=10000)
     
 if __name__ == "__main__":
-    test_encrypt_decrypt()
+    test_exchange_key_recover_key()
    

### 2017-06-08 designs/homomorphic/latticebased/unittesting.py

@@ -22,7 +22,7 @@ def determine_key_size(key):
                 for _item in item:
                     sizes.append(size_in_bits(_item))
             except TypeError:
-                sizes.append(size_in_bits(item))
+                sizes.append(size_in_bits(item))    
     return sizes
     
 def test_encrypt_decrypt_time(iterations, encrypt, decrypt, public_key, private_key, plaintext_size):    
@@ -128,3 +128,43 @@ def test_key_exchange(algorithm_name, generate_keypair, exchange_key, recover_ke
     print("(sizes are in bits)")
     print("{} unit test passed".format(algorithm_name))
     
+def test_sign_verify_time(iterations, sign, verify, public_key, private_key, message_size=32):    
+    message = random_integer(message_size)
+    print("Signing {} {}-bit messages...".format(iterations, message_size * 8))         
+    before = default_timer()
+    for count in range(iterations):                     
+        signature = sign(message, private_key)
+    after = default_timer()
+    print("Time required: {}".format(after - before))
+    
+    print("Verifying {} {}-bit signatures...".format(iterations, sum(determine_key_size(signature))))
+    before = default_timer()
+    for count in range(iterations):
+        valid_flag = verify(signature, message, public_key)       
+    after = default_timer()
+    print("Time required: {}".format(after - before))        
+    
+def test_sign_verify(algorithm_name, generate_keypair, sign, verify, 
+                     iterations=1024, message_size=32):
+    print("Beginning {} unit test...".format(algorithm_name))
+    print("Generating keypair...")
+    public_key, private_key = generate_keypair()
+    print("...done")
+    
+    print("Validating correctness...")
+    for count in range(iterations):
+        message = random_integer(message_size)
+        signature = sign(message, private_key)
+        if not verify(signature, message, public_key):        
+            raise BaseException("Unit test failed")
+    print("...done")
+    
+    test_sign_verify_time(iterations, sign, verify, public_key, private_key)
+    
+    public_sizes = determine_key_size(public_key)
+    private_sizes = determine_key_size(private_key)
+    print("Public key size : {}".format(sum(public_sizes)))
+    print("Private key size: {}".format(sum(private_sizes)))
+    print("Signature size : {}".format(sum(determine_key_size(signature))))
+    print("(sizes are in bits)")
+    print("{} unit test passed".format(algorithm_name))    

### 2017-06-19 latex/qtpie/paper.tex
working on paper

@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[$q + p_i e$ Public Key Algorithms]{$q + p_i e$ Public Key Algorithms}
+\title[EPQ Trapdoor Function]{EPQ Trapdoor Function}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Homomorphic Encryption, Public Key Encryption]{Homomorphic Encryption, Public Key Encryption}
+\keywords[Homomorphic Encryption, Public Key Cryptography]{Homomorphic Encryption, Public Key Cryptography}
 
 \begin{abstract}
- We define an extremely simple key exchange algorithm that is efficient in terms of key size, ciphertext size, key generation time, and encryption/decryption time.
-The construction requires only addition, multiplication, and modular reduction on large integers.
-The name "qtpie" is a play on the expression that appears during decryption, $q + p_i e$.
+ We define a simple trapdoor function that is suitable for use as a key exchange algorithm.
+The algorithm is relatively efficient in terms of key size, key generation time, ciphertext size, and public/private key operation time: The public key operation utilizes a single multiplication and addition modulo a big prime.
  \end{abstract}
@@
 \section{Introduction}
+A Trapdoor One-Way Function (TOWF) is a function that is easy to compute in one direction, but is hard to compute in reverse without some additional piece of information.
+A TOWF makes exchanging cryptographic keys a straightforward exercise: Alice can simply apply a TOWF to a randomly generated key and send the output to Bob, who knows the trapdoor information.
+Bob can then invert the output to obtain the key.
+
+In this paper we define a candidate Trapdoor One-Way Function that is suitable for use to exchange cryptographic keys.
+It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.
 
 \section{Definitions}
-We use $+$ to denote addition, $a * b$ to denote multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
+We use $+$ to denote addition, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
+We use both $a b$ and $a * b$ to indicate multiplication.
 We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
@@
 \section{Algorithm}
-There is a publicly agreed upon modulus $N$. The same $N$ may always be used. It must be prime; It it is not secret, and only needs to be both agreed upon and large enough.
+There is a publicly agreed upon modulus $N$.
+The same $N$ may always be used.
+It must be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
+The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation, $N$ is slightly less then 800 bits in size.
+The larger $N$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $N$ possible.
 
@@
 \begin{flalign*}
-c := (p * q) + e \mod N
+c := pq + e \mod N
 \end{flalign*}
 
-We can recover $e$ from $c$ using the following algorithm:
+Given $c, p, N$, we can recover $q, e$ using the following algorithm:
 
@@
 p_i := inverse(p, N)\\
-t := (c * p_i) \mod N\\
-t \equiv q + p_i e\\
+t := p_i c \mod N\\
 q := t \mod p_i\\
 t := t - q \\
-t \equiv p_i e
 e := t / p_i
@@
 
-The step $q := q + p_i e \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$.
-If $p_i$ is generated from a random $p$, this latter condition is unlikely to be met for any sizable value of e, for the generated $p_i$ will likely be close to $log_2(N)$ bits in size.
-Consequently, during key generation, we must generate a random $p_i$ of appropriate size and generate $p$ from it and $N$ via the $inverse$ function.
-The value $p$ serves as an encryption key, while the value $p_i$ serves as the decryption key.
+The step $q := t \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$.
+We leverage this latter fact to create a trapdoor.
+We select a suitable $p_i$ that is large enough such that $q < p_i$ and small enough such that $p_i e < N$.
+Then, we calculate the modular multilicative inverse $p := inverse(p_i, N)$.
+To create a public key, we then encrypt $p$ using a random $r$ to preclude the ability of others to calculate $p_i$.
 
-A public key consists of an encryption of the encryption key $p$ in the form of $p q \mod n$.
-The inability to selectively generate a small inverse of the public key ensures that supplying the public key to the decryption algorithm will not produce correct plaintext for any sizable message value $e$.
+The inability to selectively generate a small inverse of the public key ensures that supplying the public key to the inversion algorithm will not produce correct plaintext.
+We can witness this via the attempt below:
+
+\begin{flalign*}
+q := random(q_{size})\\
+e := random(e_{size})\\
+c := prq + e \mod N\\
+pr_i := inverse(pr, N)\\
+c_i := c pr_i \mod N\\
+c_i \equiv q + p_i r_i e \mod N\\
+\end{flalign*}
+
+In the final line $c_i \equiv q + p_i r_i e \mod N$, we can see that the inverse of the public key is too large if $p_i r_i e > N$.
+While $p_i$ is relatively small, $r_i$ is (most likely) large - Ultimately, the size of $p_i r_i$ is roughly the same as $p r$, and so this alternative perspective of $q + p_i r_i e$ offers no fewer unknown bits to guess then the original $prq + e$ did.
+
+This is in contrast to the perspective that the holder of $p_i$ has:
+
+\begin{flalign*}
+q := random(q_{size})\\
+e := random(e_{size})\\
+c := prq + e \mod N\\
+p_i := inverse(p, N)\\
+c_i := c p_i \mod N\\
+c_i \equiv qr + p_i e \mod N
+\end{flalign*}
+
+We can see the difference in the final line $c_i \equiv qr + p_i e \mod N$ from before; While the $r$ variable is still present on the left term, $p_i e < N$ and so the inversion algorithm will work as intended.
+The presence of the $r$ variable on the left does require that $p_i$ be larger to ensure that $qr < p_i$.
 
@@
 \begin{flalign*}
-key_{pr} := N - random(m_{size} + 1)\\
-r := random(k_{size})\\
-key_{pub} := inverse(key_{pr}, N) * r) \mod N\\
+k_{priv} := random(priv_{size})\\
+p := inverse(k_{priv}, N)\\
+r := random(r_{size})\\
+k_{pub} := p r \mod N\\
 \end{flalign*}
 
-In the above, $m_{size}$ is equal to the size of the shared secret material in bits.
-$k_{size}$ is a security parameter that is equal to the size of the randomly generated value in bits.
-We elect to set $m_{size}$ and $k_{size}$ to be 256 bits.
-
-$key_{pr}$ must be selected such that $key_{pr} e < N$, as well as $key_{pr} > r q$, where $q$ is the security parameter of the public key operation.
+$priv_{size}$ must be selected such that $e k_{priv} < N$, as well as $k_{priv} > r q$, where $q, e$ are the security parameter of the public key operation and shared secret.
+For 256-bit $e, r, q$ values, $priv_{size}$ is 520 bits, while $N$ is slightly less then 800 bits.
 
 \subsection{Exchanging Keys}
-To exchange a secret key: multiply the public key by a random value, then add the secret key to the result modulo $N$.
+To exchange a secret key: multiply the public key $p$ by a random value $q$, then add a random value $e$ to the result modulo $N$.
+The shared secret will be either $q$ or $e$ (or some combination of the two); We discuss the implications of the choices later.
+We default to using $e$ as the secret, as it is slightly less complex.
 
 \begin{flalign*}
-secret := random(m_{size})\\
-ciphertext := (key_{pub} random(q_{size}) + secret \mod N\\
+p := key_{pub}\\
+q := random(q_{size})\\
+e := random(e_{size})\\
+ciphertext := p q + e \mod N\\
 \end{flalign*}
 
-\subsection{Key Recover}
-The shared secret can be recover from the ciphertext via the following algorithm:
-\begin{flialign*}
-pie_q := ciphertext key_{pr} \mod N\\
-q := pie_q \mod key_{pr}\\
-pie := pie_q - q\\
-e := pie / pi
+\subsection{Key Recovery}
+The shared secret $e$ (or $q$ or both) can be recover from the ciphertext via the following algorithm:
+
+\begin{flalign*}
+p_i := key_{priv}\\
+t := ciphertext * p_i \mod N\\
+q := t \mod p_i\\
+t := t - q\\
+e := t / pi\\
+q := q / r
 \end{flalign*}
 
+\subsection{Homomorphism}
+In addition to the ability to add ciphertexts together, ciphertexts can be multiplied by plaintext values, and plaintext values can be added to ciphertexts.
+This second property follows naturally from the ability to add ciphertexts together.
+The third property is a result of the fact that $e$ is attached to the ciphertext by simple addition.
+In the following examples, $c_i$ are ciphertexts, while $1, 2$ are plaintext integers.
+
+\begin{flalign*}
+c_3 := c_1 + c_2\\
+c_4 := c_3 + 1\\
+c_5 := 2 c_4 
+\end{flalign*}
+
+It should be noted that multiplication will quickly increase the size of the terms in the expressions, and if the size of the terms grows too large, decryption will fail.
+
 \section{Security Analysis}
-\subsection{Public Key Cipher}
+There are two main security goals: First, given the public key, the private key must not be obtainable; Second, The output of the public key operation must not be invertible without the private key.
+
+\subsection{Key Generation}
+It would appear that obtaining the private key from the public key must be done by guessing one of $p, p_i, r$.
+If this were not the case, then whatever algorithm that can be used to recover any of $p, p_i, r$ from $p r \mod N$ could be used to recover plaintexts from ciphertexts of the form $m k \mod N$ for random $m, k$ where one of $m, k$ is smaller then the other (but still large enough to reduce modulo $N$).
+It seems unlikely that such an attack exists and is faster then guessing $p, p_i,  r$.
+
+This implies that the private key cannot be recovered from the public key.
+
+\subsection{Public Key Operation}
+The security of the public key operation appears to scale with the size of the randomly generated $q$. It remains to be proven that given $c := p q + e \mod N$, $p$, recovering $e$ is difficult.
+
+\subsection{Side Channel Analysis}
+Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches in the algorithm.
 
 \section{Metrics}
+Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in slightly under 1 second.
+It requires .3 seconds to perform 10,000 private key operations, which implies that roughly 30,000 private key operations per second can be performed on very modest hardware.
+Our tests were performed on an Intel Celeron N2830 2.16GHz with 2 cores.
+
+In our implementation, most of the time for the public key operation is spent generating $q$ and $e$.
+In a synthetic test where $q, e$ are not generated for each invocation of the function, we can perform 100,000 public key operations per second.
+
+Our implementation is optimized for readability.
+Much of the computation time is spent on bignum operations, and while an optimized C implementation may certainly be faster, it is not required to obtain an acceptable level of performance.
 
 \subsection{Implementation Complexity}
-The implementation complexity of the scheme is very low.
-The encryption and decryption functions for the public key construction can be implemented with a single line of code each in the function body.
-Our implementation of the algorithms spans approximately 100 lines, including the documentation and comments.\\
+The implementation complexity of the scheme is very low. Our public domain python implementation of the algorithm spans barely 100 lines, including the documentation and comments.\\
 
-Additional code is required for supporting functions such as the generation of prime numbers (only if $n$ is being generated/not already established), computation of modular inverses, and unit testing.
-These are modest requirements that are already well facilitated by existing cryptographic libraries, and in other cases can be implemented without much complexity.
+Additional code is required for supporting functions such as the generation of prime numbers (only if $N$ is being generated/not already established) and unit testing.
+These are modest requirements that can be implemented without much complexity.
 \\
 
-Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches in the algorithm.
-
 \section{Conclusion}
-We define a conceptually simple, resource-practical public-key encryption algorithm. 
+We define a conceptually simple, resource-practical key exchange algorithm. 
 \end{document}

### 2017-06-19 designs/homomorphic/latticebased/unittesting.py

@@ -88,8 +88,10 @@ def test_symmetric_encrypt_decrypt(algorithm_name, generate_key, encrypt, decryp
     print("Ciphertext size: {}".format(size_in_bits(encrypt(random_integer(plaintext_size), key))))
     print("{} unit test passed".format(algorithm_name))
 
-def test_exchange_key_recover_key_time(iterations, exchange_key, recover_key, public_key, private_key, key_size=32):    
-    print("Exchanging {} {}-byte messages...".format(iterations, key_size))            
+def test_exchange_key_recover_key_time(iterations, exchange_key, recover_key, public_key, private_key, key_size=32):        
+    if iterations == 0:
+        return None    
+    print("Exchanging {} {}-byte keys...".format(iterations, key_size))            
     before = default_timer()
     for count in range(iterations):                     
         ciphertext, key = exchange_key(public_key)
@@ -104,7 +106,7 @@ def test_exchange_key_recover_key_time(iterations, exchange_key, recover_key, pu
     print("Time required: {}".format(after - before))        
     
 def test_key_exchange(algorithm_name, generate_keypair, exchange_key, recover_key, 
-                      iterations=1024):
+                      iterations=1024, key_size=32):
     print("Beginning {} unit test...".format(algorithm_name))
     print("Generating keypair...")
     public_key, private_key = generate_keypair()
@@ -118,13 +120,13 @@ def test_key_exchange(algorithm_name, generate_keypair, exchange_key, recover_ke
             raise BaseException("Unit test failed")
     print("...done")
     
-    test_exchange_key_recover_key_time(iterations, exchange_key, recover_key, public_key, private_key)
+    test_exchange_key_recover_key_time(iterations, exchange_key, recover_key, public_key, private_key, key_size)
     
     public_sizes = determine_key_size(public_key)
     private_sizes = determine_key_size(private_key)
     print("Public key size : {}".format(sum(public_sizes)))
     print("Private key size: {}".format(sum(private_sizes)))
-    print("Ciphertext size : {}".format(size_in_bits(ciphertext)))
+    print("Ciphertext size : {}".format(size_in_bits(exchange_key(public_key)[0])))
     print("(sizes are in bits)")
     print("{} unit test passed".format(algorithm_name))
     

### 2017-06-19 other/math/latticeencoding.py

@@ -1,0 +1,15 @@
+base = 17
+points = range(16)
+
+def encode_point(point):
+    assert point in points
+    return base * point
+    
+def decode_point(encoded_point, base):
+    e = encoded_point % base
+    modifier = 0
+    if e > base / 2:
+        modifier = 1
+    return ((encoded_point - e) / base) + modifier
+    
+    

### 2017-06-21 latex/qtpie/paper.tex
improved signaturetest

@@
 A TOWF makes exchanging cryptographic keys a straightforward exercise: Alice can simply apply a TOWF to a randomly generated key and send the output to Bob, who knows the trapdoor information.
-Bob can then invert the output to obtain the key.
+Bob can then use the trapdoor information to invert the output and obtain the key.
 
-In this paper we define a candidate Trapdoor One-Way Function that is suitable for use to exchange cryptographic keys.
+In this paper we define a candidate TOWF that is suitable for use to exchange cryptographic keys.
 It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.
@@
 It must be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
-The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation, $N$ is slightly less then 800 bits in size.
+The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $N$ is slightly less then 800 bits in size.
 The larger $N$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $N$ possible.
@@
 Then, we calculate the modular multilicative inverse $p := inverse(p_i, N)$.
+This number will likely be very large, closer to $N$ in size then to $p_i$.
 To create a public key, we then encrypt $p$ using a random $r$ to preclude the ability of others to calculate $p_i$.
 
-The inability to selectively generate a small inverse of the public key ensures that supplying the public key to the inversion algorithm will not produce correct plaintext.
+The public key provides the ability to compute the forward operation $p q + e \mod N$ because there is no size constraint on $p$ for this operation (as long as $p < N$ anyways).
+Supplying the inverse of the public key to the inversion algorithm will not produce correct plaintext, because the generated value will be too large.
 We can witness this via the attempt below:
@@
 
+\subsubsection{$q$ and Anti-Malleability}
+If $q$ is used as the secret instead of $e$, then the ability to add plaintext values to ciphertexts disappears.
+The value of $e$ will not influence $q$, and manipulations of the ciphertext less then a certain magnitude will not modify the plaintext obtained upon decryption.
+This is in stark contrast to the more common Non-Malleability, where modification of the ciphertext will usually modify the corresponding plaintext to a meaningless value.
+
 \section{Security Analysis}
@@
 
-This implies that the private key cannot be recovered from the public key.
+This implies that there does not exist an algorithm to recover the private key from the public key, other then brute force guessing.
 
@@
 \section{Conclusion}
-We define a conceptually simple, resource-practical key exchange algorithm. 
+We define a conceptually simple, resource-practical Trapdoor One-Way Function and key exchange algorithm. 
 \end{document}

### 2017-06-21 designs/homomorphic/latticebased/breaktest.py

@@ -1,0 +1,30 @@
+from crypto.utilities import is_prime, big_prime, modular_inverse, random_integer
+
+def test_break():
+    N = 65537#big_prime(3)
+    assert is_prime(N)    
+    p_i = 256
+    p = modular_inverse(p_i, N)
+    
+    q = random_integer(1)
+    e = random_integer(1)
+    c = ((p * q) + e) % N
+    print q, e, p_i * e < N
+    _q, _e = break_qtpie(p, c, N)
+    assert (q, e) == (_q, _e), ((q, e), (_q, _e))
+    assert _e == e, (e, _e)
+    
+def break_qtpie(p, c, n):    
+    x = n - p
+    q, e = divmod(c, x)
+    _c = (((x * q) + e) % n)
+    assert _c == c, (_c, c)
+    
+    e -= 1
+    _c = c - e
+    q = (_c * modular_inverse(p, n)) % n    
+    return q, e
+    
+if __name__ == "__main__":
+    test_break()
+    

### 2017-06-21 designs/homomorphic/latticebased/signaturetest.py

@@ -10,39 +10,43 @@ def generate_pq(private_key, q_size=32, n=N):
     p = modular_inverse(private_key, n)
     q = random_integer(q_size)
     pq = (p * q) % n      
-    return pq, q
+    return pq, q, p * pq
     
 def generate_keypair():
     pi = generate_pi()
-    pq, q = generate_pq(pi)
-    private_key = (pi, q)
+    pq, q, p= generate_pq(pi)
+    private_key = (pi, q, p)
     public_key = pq
     return public_key, private_key
     
 def verify(signature, message, public_key, n=N):     
     q, e = signature
     _message = ((public_key * q) + e) % n
-    if _message == message:
+    if _message == (public_key * message) % n:
         return True
     else:
         return False
-                
+
 def sign(message, private_key, n=N):
-    pi, r = private_key
+    pi, r, key_e = private_key            
     pie_q = (pi * message) % n
-    qr = pie_q % pi     
-    pie = pie_q - qr
-    assert qr % r == 0
-    #print qr / r
-    q = qr / r#(qr * modular_inverse(r, n)) % n
-    e = pie / pi   
-    assert e != message
-    return q, e + (qr % r)
+    qr, e = divmod(pie_q, pi)
+    return qr, (key_e * e) % n    
+    
+    #assert (qr * pi) + e == (pi * message) % n
+    #q = (qr * modular_inverse(r, n)) % n 
+    #assert ((q * r * pi) + e) % n == (pi * message) % n
+                
+    #c = (p * message) % n # qr + pe == message
+    #c = (p * r * message) % n # p q r r + p p r e == p r message
+    #assert ((p * q * r * r) + (p * p * r * e)) % n == (p * r * message) % n
+  #  print log(qr, 2), log(e, 2)
+     
     
 def test_sign_verify():
     from unittesting import test_sign_verify    
-    test_sign_verify("signaturetest", generate_keypair, sign, verify, message_size=64)
-    
-    
+    test_sign_verify("signaturetest", generate_keypair, sign, verify, iterations=10000, message_size=64)
+        
 if __name__ == "__main__":
     test_sign_verify()
+    

### 2017-06-21 designs/homomorphic/latticebased/unittesting.py

@@ -161,7 +161,7 @@ def test_sign_verify(algorithm_name, generate_keypair, sign, verify,
             raise BaseException("Unit test failed")
     print("...done")
     
-    test_sign_verify_time(iterations, sign, verify, public_key, private_key)
+    test_sign_verify_time(iterations, sign, verify, public_key, private_key, message_size)
     
     public_sizes = determine_key_size(public_key)
     private_sizes = determine_key_size(private_key)

### 2017-06-21 pickledtest.py

@@ -1,8 +1,8 @@
 """ Provides authenticated encryption and decryption functions using only the python standard library. """    
 import hashlib
 import hmac as _hmac
-
 from pickle import dumps, loads
+
 from utilities import slide, xor_subroutine, random_bytes
 
 __all__ = ("encrypt", "decrypt")           

### 2017-06-26 latex/qtpie/paper.tex
added key agreement idea
random walks are cool :)

@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[EPQ Trapdoor Function]{EPQ Trapdoor Function}
+\title[LWE Trapdoor One-Way Function]{LWE Trapdoor One-Way Function}
 
@@
 \begin{abstract}
- We define a simple trapdoor function that is suitable for use as a key exchange algorithm.
-The algorithm is relatively efficient in terms of key size, key generation time, ciphertext size, and public/private key operation time: The public key operation utilizes a single multiplication and addition modulo a big prime.
+ We define a simple trapdoor function based on the Learning-With-Errors problem in one dimension, and present a key exchange algorithm based on the trapdoor.
+The trapdoor algorithm is efficient in terms of key size, key generation time, ciphertext size, and public/private key operation time: We can perform many thousands of public and private key operations per second with a naive python implementation on modest hardware.
  \end{abstract}
@@
 \section{Introduction}
-A Trapdoor One-Way Function (TOWF) is a function that is easy to compute in one direction, but is hard to compute in reverse without some additional piece of information.
-A TOWF makes exchanging cryptographic keys a straightforward exercise: Alice can simply apply a TOWF to a randomly generated key and send the output to Bob, who knows the trapdoor information.
+A Trapdoor One-Way Function (TOWF) is a function that is easy for anyone to compute in one direction, but is hard to compute in reverse without some additional piece of information.
+A TOWF makes exchanging cryptographic keys a straightforward exercise: Suppose that Bob happens to know the trapdoor information for a TOWF: Alice can simply apply the TOWF to a randomly generated key and send the output to Bob.
 Bob can then use the trapdoor information to invert the output and obtain the key.
 
-In this paper we define a candidate TOWF that is suitable for use to exchange cryptographic keys.
+The Learning-With-Errors (LWE) problem is a mathematical problem that is believed to be difficult to solve efficiently even with a quantum computer.
+
+In this paper we define a candidate TOWF based on 1-dimensional LWE.
 It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.
@@
 \section{Definitions}
-We use $+$ to denote addition, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
-We use both $a b$ and $a * b$ to indicate multiplication.
+We $+$ to denote addition, $a b$ to indicate multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
 We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
@@
 The same $N$ may always be used.
-It must be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
+It should be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
 The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $N$ is slightly less then 800 bits in size.
@@
 p_i := inverse(p, N)\\
-t := p_i c \mod N\\
+t := p_i c \equiv p_i p q + p_i e \equiv q + p_i e \mod N\\
 q := t \mod p_i\\
@@
 
+\subsubsection{Processing the Secret}
+The secret should be processed before use a key. Ideally, HKDF should be used; If it is not available, a simple hash function applied to the secret should be sufficient.
+
 \subsection{Homomorphism}
@@
 \section{Security Analysis}
-There are two main security goals: First, given the public key, the private key must not be obtainable; Second, The output of the public key operation must not be invertible without the private key.
+There are two main goals: First, given the public key, the private key must not be obtainable; Second, The output of the public key operation must not be invertible without the private key.
 
@@
 \subsection{Public Key Operation}
-The security of the public key operation appears to scale with the size of the randomly generated $q$. It remains to be proven that given $c := p q + e \mod N$, $p$, recovering $e$ is difficult.
+The public key operation appears to be a 1-dimensional version of the learning-with-errors problem.\\
+
+If we consider the case where $pr = 1$, then $prq + e \equiv q + e \mod P$ for uniformly random values $q, e$.
 

### 2017-06-26 designs/homomorphic/latticebased/breaktest.py

@@ -17,7 +17,7 @@ def test_break():
 def break_qtpie(p, c, n):    
     x = n - p
     q, e = divmod(c, x)
-    _c = (((x * q) + e) % n)
+    _c = n - (((x * q) + e) % n)
     assert _c == c, (_c, c)
     
     e -= 1

### 2017-06-26 designs/homomorphic/latticebased/keyagreement.py

@@ -1,0 +1,38 @@
+from crypto.utilities import random_integer
+
+G = random_integer(32)
+
+def generate_private_key(q_size=32, e_size=32):
+    q = random_integer(q_size)
+    e = random_integer(e_size)
+    return q, e
+    
+def generate_public_key(private_key, g=G):
+    q, e = private_key
+    point1 = (g * q) + e
+    return (point1 * q) + e
+    
+def generate_keypair(q_size=32, e_size=32, g=G):
+    private_key = generate_private_key(q_size, e_size)
+    public_key = generate_public_key(private_key, g)
+    return public_key, private_key
+       
+def key_agreement(public_key, private_key):
+    q, e = private_key    
+    point1 = ((public_key * q) + e) >> 640 
+    return int(format(((point1 * q) + e), 'b')[:200], 2)
+    
+def test_key_agreement():
+    for count in range(65536):
+        public1, private1 = generate_keypair()
+        public2, private2 = generate_keypair()
+        
+        key1 = key_agreement(public2, private1)
+        key2 = key_agreement(public1, private2)
+                
+        assert key1 == key2, '\n\n'.join(('\n', format(key1, 'b'), format(key2, 'b')))
+    print "key agreement unit test passed"
+    
+if __name__ == "__main__":
+    test_key_agreement()
+    

### 2017-06-28 latex/trapdoors_randomwalks/paper.tex
renamed variables

--- 2017-06-26 latex/qtpie/paper.tex
@@
 \institute{Paso Robles, CA \email{python_pride@protonmail.com}}
-\title[LWE Trapdoor One-Way Function]{LWE Trapdoor One-Way Function}
+\title[Trapdoors and Random Walks With LWE]{Trapdoors and Random Walks With LWE}
 
@@
 % use optional argument because the \LaTeX command breaks the PDF keywords
-\keywords[Homomorphic Encryption, Public Key Cryptography]{Homomorphic Encryption, Public Key Cryptography}
+\keywords[Homomorphic Encryption, Public Key Cryptography, LWE]{Homomorphic Encryption, Public Key Cryptography, LWE}
 
 \begin{abstract}
- We define a simple trapdoor function based on the Learning-With-Errors problem in one dimension, and present a key exchange algorithm based on the trapdoor.
-The trapdoor algorithm is efficient in terms of key size, key generation time, ciphertext size, and public/private key operation time: We can perform many thousands of public and private key operations per second with a naive python implementation on modest hardware.
+ We define a trapdoor function and random-walk type function based on the Learning-With-Errors problem; Together, the algorithms constitute post-quantum alternatives to traditional RSA and DH .
+Our constructions are practical and efficient in terms of size and space: public and private keys are small, ciphertext expansion is relatively low, and public and private key operation times are fast.
  \end{abstract}
@@
 Bob can then use the trapdoor information to invert the output and obtain the key.
+With the right padding, a TOWF may be used for public key encryption as well; The difference is that instead of a random value, Alice can choose the value that she sends to Bob.
+
+A Random-Walk function is a function that facilitates key agreement: Suppose Alice was to walk in a particular but random pattern where she ends up at a destination $A$; Bob does the same, walking in his own particular but random pattern to end up at a destination $B$.
+Then, if Alice starts at $B$ and walks her random path again, she will end up at a point $C$; If Bob starts at $A$ and walks his random path again, he too will end up at point $C$.
+In this way, both parties arrive at the same final location, and neither learns the particular way that the other one arrived.
+Elliptic-Curve Diffie-Hellman is an examplea of a Random-Walk type function.
 
 The Learning-With-Errors (LWE) problem is a mathematical problem that is believed to be difficult to solve efficiently even with a quantum computer.
+Problems of this type take the form $a s + e \mod q$, where $a, q$ are public knowledge and $s, e$ are kept secret.
 
@@
 It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.
+
+Additionally, we also define a Random-Walk type function using the observation of the fact that LWE incorporates scaling and translation; The combined effects of scaling and translation act as the random steps on the path taken by Alice and Bob.
 
@@
 
-\section{Algorithm}
+\section{Trapdoor Algorithm}
 There is a publicly agreed upon modulus $N$.
@@
 
-\section{Security Analysis}
+\subsection{Security Analysis}
 There are two main goals: First, given the public key, the private key must not be obtainable; Second, The output of the public key operation must not be invertible without the private key.
 
-\subsection{Key Generation}
+\subsubsection{Key Generation}
 It would appear that obtaining the private key from the public key must be done by guessing one of $p, p_i, r$.
@@
 
-\subsection{Public Key Operation}
+\subsubsection{Public Key Operation}
 The public key operation appears to be a 1-dimensional version of the learning-with-errors problem.\\
@@
 
-\subsection{Side Channel Analysis}
+\subsubsection{Side Channel Analysis}
 Assuming that BigNum operations can be implemented in a manner that does not leak timing information, it appears that a naive implementation of the algorithm is resistant to timing side channel analysis, as there are no tables or branches in the algorithm.
 
+\section{Random-Walk Algorithm}
+There is a publicly known and agreed upon starting point $x$, as well as another starting point and modulus $y$.
+The size of $y$ determines the ciphertext size and key size; The size of $x$ should be close to but smaller then $y$.
+We elect to utilize 256 bits for the size of $x$, and $264$ bits for the size of $y$; This ensures that 256 bits of key material are available as a shared secret.
+
+\subsection{Basic Concept}
+A random walk requires a starting point, as well as directions for where to proceed next.
+The LWE expression $a s + e \mod q$ incorporates a scaling by $s$ and a translation by $e$; These steps serve as the directions for the random walk, as they determine which destination point is selected; The value of $a$ acts as the initial location where the walk begins from.
+
+\subsection{Random Walk Algorithm}
+\begin{flalign*}
+point_2 := point_1 s + e y \mod y
+\end{flalign*}
+
+The above expression calculates the location of the next point (which may be the destination) according to the values of $s, e$; The value of $e$ is mutliplied by $y$ to facilitate the reduction modulo $y$.
+This expression is used to generate a public key, as well as to compute the shared secret between parties.
+
+\subsection{Key Generation}
+A private key consists of random integers $s, e$. A public key consists of the point that is arrived at after using the private key "directions" $s, e$ to walk, starting from the base points $x, y$:
+
+\begin{flalign*}
+s := random(s_{size})\\
+e := random(e_{size})\\
+point := x s + e y \mod y\\
+key_{private} := s, e\\
+key_{public} := point
+\end{flalign*}
+
+\subsection{Key Agreement}
+A shared secret can be obtained by applying the random walk function using the other parties public key as the starting location.
+
+\begin{flalign*}
+secret := key_{public} s + e y \mod y
+\end{flalign*}
+
+\subsection{Additional Points on the Walk}
+In the examples given in the prior section, the random walk function is only applied once; In fact, it may be applied many times.
+An arbitrary number of points can be walked through without increasing space requirements - it only costs more time to walk further.
+
+It may be required that a greater number of points on the path is required for security; We are unable to demonstrate an attack against a single point walk.
+We choose to utilize the fewest number of points required for efficiency reasons provided security can still be maintained.
+
 \section{Metrics}
+\subsection{Trapdoor Algorithm}
 Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in slightly under 1 second.
@@
 
-\subsection{Implementation Complexity}
+\subsubsection{Implementation Complexity}
 The implementation complexity of the scheme is very low. Our public domain python implementation of the algorithm spans barely 100 lines, including the documentation and comments.\\
@@
 
+\subsection{Random-Walk Algorithm}
+
 \section{Conclusion}

### 2017-06-30 latex/qtpie/paper.tex
added more key agreement ideas

@@
 \listoftodos
+You are missing all the non fake signature etc.
+
+Where is your trap door function defined where is the key exchange defined ?
+
+You should use the environment algorithm to write your algorithm. It is difficult to understand as is.
+
+Section 2 is too short to be a section as is.
+
+Addition over what field ? Etc for the rest. (edited)
+
+Why 800 bits for N. Why not less ?
+
+Given the following function....
+That's not a function. That's an equation. (edited)
+
+What are p q e ?
+
+Use leftarrow instead of :=
+
+If it's an algorithm don't put equivalent (triple equal) in it
+
+Use $p^-1$ or something else but not pi.
+It confusing.
+
+Inverse mod N in which field ?????
+Or group.
+My bad it's in 2.
+
+Basic concept is not a good name for a section.
+Use specifications.
+Or Design motivation (after specifications)
+
+You should not need to specify mod N in each operations.
+
+Why k private is 520 bits ?
+
+How does all this compares to others methods ?
+
+What is that t in key recovery.
 

### 2017-06-30 designs/homomorphic/latticebased/keyagreement2.py

@@ -1,0 +1,47 @@
+from crypto.utilities import random_integer, big_prime
+
+A_SIZE = 32
+B_SIZE = 32
+X_SIZE = 32
+Y_SIZE = 33
+PRIVATE_KEY_SIZE = 32
+
+def generate_parameters(a_size=A_SIZE, b_size=B_SIZE,
+                        x_size=X_SIZE, y_size=Y_SIZE):
+    a = random_integer(a_size)
+    b = random_integer(b_size)
+    x = random_integer(x_size)
+    y = big_prime(y_size)
+    return a, b, x, y
+
+A, B, X, Y = generate_parameters()
+    
+def calculate_a_adjustment(point_count):
+    return (2 * point_count) + ((point_count - 1) % 2)
+        
+def point_addition(a, b, x, y, point_count):    
+    _a = pow(a, point_count, y)
+    adjustment = calculate_a_adjustment(point_count)
+    return ((_a * x) + (b * y * (a + adjustment))) % y
+    
+def generate_private_key(private_key_size=PRIVATE_KEY_SIZE):
+    return random_integer(private_key_size)        
+    
+def generate_public_key(private_key, a=A, b=B, x=X, y=Y):
+    return point_addition(a, b, x, y, private_key)
+    
+def generate_keypair(private_key_size=PRIVATE_KEY_SIZE, parameters=(A, B, X, Y)):
+    private_key = generate_private_key(private_key_size)
+    public_key = generate_public_key(private_key, *parameters)
+    return public_key, private_key
+    
+def key_agreement(public_key, private_key, a=A, b=B, y=Y):
+    return point_addition(a, b, public_key, y, private_key)
+        
+def test_key_agreement():
+    from unittesting import test_key_agreement
+    test_key_agreement("keyagreement2", generate_keypair, key_agreement, iterations=10000)
+    
+if __name__ == "__main__":
+    test_key_agreement()
+    

### 2017-06-30 designs/homomorphic/latticebased/keyagreement3.py

@@ -1,0 +1,53 @@
+from crypto.utilities import random_integer, big_prime
+
+A_SIZE = 32
+B_SIZE = 32
+X_SIZE = 32
+Y_SIZE = 33
+PRIVATE_KEY_SIZE = 32
+
+def generate_parameters(a_size=A_SIZE, b_size=B_SIZE,
+                        x_size=X_SIZE, y_size=Y_SIZE):
+    a = random_integer(a_size)
+    b = random_integer(b_size)
+    x = random_integer(x_size)
+    y = big_prime(y_size)
+    return a, b, x, y, b * y
+    
+PARAMETERS = A, B, X, Y, BY = generate_parameters()
+    
+def point_addition(x, _a, adjustment, y=Y):
+    return ((_a * x) + adjustment) % y
+    
+def calculate_a_adjustment(point_count):
+    return (2 * point_count) + ((point_count - 1) % 2)
+                
+def generate_private_key(a, b, y, private_key_size=PRIVATE_KEY_SIZE):    
+    point_count = random_integer(private_key_size)
+    _a = pow(a, point_count, y)
+    adjustment = calculate_a_adjustment(point_count)
+    return _a, (b * y * (a + adjustment)) % y
+        
+def generate_public_key(private_key, parameters):   
+    _a, adjustment = private_key
+    a, b, x, y, by = parameters
+    public_key = point_addition(x, _a, adjustment, y)
+    return public_key
+    
+def generate_keypair(private_key_size=PRIVATE_KEY_SIZE, parameters=PARAMETERS):
+    a, b, x, y, by = parameters
+    private_key = generate_private_key(a, b, y, private_key_size)
+    public_key = generate_public_key(private_key, parameters)
+    return public_key, private_key
+    
+def key_agreement(public_key, private_key, y=Y):   
+    _a, adjustment = private_key
+    return point_addition(public_key, _a, adjustment, y)
+    
+def test_key_agreement():
+    from unittesting import test_key_agreement
+    test_key_agreement("keyagreement3", generate_keypair, key_agreement, iterations=10000)
+    
+if __name__ == "__main__":
+    test_key_agreement()
+    

### 2017-06-30 designs/homomorphic/latticebased/liblll.py

@@ -1,0 +1,325 @@
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program. If not, see <http://www.gnu.org/licenses/>.
+#
+# Authors : kutio <kutioo[.at.]gmail[.dot.]com>
+
+
+from fractions import Fraction
+import math
+
+# matrix multiplication
+def mat_mult(a, b):
+    m = len(a)
+    n = len(b[0])
+    p = len(a[0])
+    res = [ [0 for j in range(n) ] for i in range(m)]
+    for i in range(m):
+        for j in range(n):
+            coeff = 0
+            for k in range(p):
+                coeff += a[i][k] * b[k][j]
+            res[i][j] = coeff
+    return res
+
+# scalar product
+def scalar_product(a, b):
+    m = len(a)
+    res = Fraction(0)
+    for i in range(m):
+        res += a[i] * b[i]
+    return res
+
+# display matrix
+def print_mat(n):
+    maxlen = 0
+    for row in n:
+        for f in row:
+            if len(str(f)) > maxlen:
+                maxlen = len(str(f))
+    for row in n:
+        row_str = ""
+        for f in row:
+            difflen = maxlen - len(str(f))
+            sep = " "
+            for i in range(difflen):
+                sep = sep + " "
+            row_str = row_str + sep + str(f)
+        print(row_str)
+
+# display vector
+def print_vector(v):
+    row_str = " ".join("%s" % i for i in v)
+    print(row_str)
+
+# get vector j in the matrix n
+def get_vector(n, j):
+    return [ n[i][j] for i in range(len(n))]
+
+# vector substraction 
+def vector_add(a, b):
+    return [ a[i] + b[i] for i in range(len(a)) ]
+
+# vector substraction 
+def vector_sub(a, b):
[…]

### 2017-06-30 designs/homomorphic/latticebased/randomwalktest.py

@@ -1,0 +1,55 @@
+# ax + by mod y
+# 
+# a(ax + by) + by mod y
+# aax + aby + by mod y
+# aax + by(a + 1) mod y
+# 
+# aax + by(a + 1) mod y
+# a(aax + by(a + 1)) + by mod y
+# aaax + aby(a + 1) + by
+# aaax + by(a + 3)
+
+from crypto.utilities import random_integer, big_prime, modular_inverse, modular_subtraction
+
+def walk(a, b, x, y):
+    return ((a * x) + (b * y)) % y
+    
+def follow_path2(a, b, x, y, point_count):
+    _a = pow(a, point_count, y)
+    adjustment = (2 * point_count) + ((point_count - 1) % 2)
+    return ((_a * x) + (b * y * (a + adjustment))) % y
+        
+def follow_path(a, b, x, y, point_count):
+    for count in range(point_count):
+        x = walk(a, b, x, y)
+    return x
+        
+def test_walk_follow_path():
+    a, b, x = [random_integer(32) for count in range(3)]
+    y = big_prime(33)
+    
+    x1 = walk(a, b, x, y)
+    x2 = walk(a, b, x1, y)
+    x3 = walk(a, b, x2, y)
+    
+    _x2 = follow_path(a, b, x, y, 2)
+    assert _x2 == x2
+    assert ((a * a * x) + (b * y * (a + 1))) % y == _x2
+    __x2 = follow_path2(a, b, x, y, 2)
+    assert __x2 == _x2
+    
+    _x3 = follow_path(a, b, _x2, y, 1)
+    assert _x3 == x3
+    assert ((a * a * a * x) + (b * y * (a + 3))) % y == _x3
+    __x3 = follow_path2(a, b, _x2, y, 1)
+    assert _x3 == _x3
+        
+    _x4 = follow_path(a, b, _x3, y, 1)    
+    assert ((a * a * a * a * x) + (b * y * (a + 5))) % y == _x4
+    __x4 = follow_path2(a, b, _x3, y, 1)
+    assert __x4 == _x4
+    
+    
+if __name__ == "__main__":
+    test_walk_follow_path()
+    

### 2017-07-10 designs/C/arxcalibur/paper/template.tex
organized package + updated readme

--- 2017-03-16 latex/cipher_templates/blockcipher/arx/template.tex
@@
 \begin{abstract}
-  We define a block cipher with an N\todo{Block size?}-bit block size and K\todo{Key size?}-bit key size.
-The design is oriented towards PLATFORM TYPE\todo{Constrained Devices?
-Consumer CPUs?
-What architecture/native word sizes?}.
-The design makes use of certain instruction types or gates.
-\todo{XOR/AND?
-ADD/XOR?
-Multiplication?
-Modular Exponentiation?
-Lookup Tables?}\\
+  We define a block cipher with an 128-bit block size and 128-bit key size.
+The design is oriented towards general purpose CPUs and software implementation.
+The design makes use of addition and xor to mix columns, and rotations to shift rows.
+\\
 \end{abstract}
@@
 
-\todo{Explain the motivation for the design described here}
+In this paper, we define a minimalist ARX based cipher, dubbed "Arxcalibur".
+It utilizes simple addition and xor to mix the columns of four 32-bit words, and simple rotations to shift the rows.
+One iteration of the round function consists of just 21 relatively pipeline-friendly instructions, and only two rounds are required for complete diffusion.
 
+We also
 \section{Definitions}

### 2017-07-10 designs/nonlinear/blockcipher/arx/1/paper/blockcipher.tex
organized package + updated readme

--- 2017-03-07 designs/blockcipher/arx/1/paper/design.tex
@@
 \institute{Paso Robles, California \email{python_pride@protonmail.com}}
-\title[\texttt Design 3-4-17]{\texttt Design 3-4-17}
+\title[\texttt Design 2/24]{\texttt Design 2/24}
 
@@
 \begin{abstract}
-  We define and explain the design of a 256-block cipher.
-The minimalist design is tailored to produce high throughput and low latency on general purpose CPUs, and simple implementation in hardware.
-Additionally, due to the bit-sliced nature of the design, we predict that it would be reasonably efficient in constrained environments..
+  We define and explain the design of a 128-block cipher.
+It is similar in layout and design to Rinjdael, and could be modeled as such with modified linear and s-box layers.
+The modifications seek to replace one of the slower parts of Rijndael, the mixColumns routine, with an SIMD/parallel friendly routine that is scales well to 8-bit platforms.
+Additionally, the s-box is replaced with the concatenation of 2 "golden" 4x4 s-boxes.
 \end{abstract}
@@
 \section{Introduction}
-We describe a cipher algorithm that uses simple XOR, AND, and rotate left instructions on four 64-bit words.
-Minimum amounts of diffusion are guaranteed through the application of a shift rows and mix column like structure.
-The 4x4 s-box is the most compact  implementation of all ideal 4x4 s-boxes, and is implemented in 9 instructions.
-% to do: \cite{http://skew2011.mat.dtu.dk/proceedings/Finding%20Optimal%20Bitsliced%20Implementations%20of%204%20to%204-bit%20S-boxes.pdf}
+The Rijndael cipher has proven itself to be well designed.
+It has remained secure for years, despite seeing immense amounts of cryptanalysis by extremely talented researchers.
+However, the mixColumns operation is relatively complicated both in implementation and in theory.
+We describe a design similar to Rijndael that uses a conceptually simpler linear mixing function.
+This function is dubbed mixState and uses only XOR gates and rotations.
+It provides full diffusion in one round in a scalable and parallel-friendly manner.
 
 \section{Definitions}
-We use $\oplus$ to denote XOR, $\land$ to denote AND, and $\lll$ to denote bitwise rotation left.
-The state is modeled as a 4x64 grid, with each 64-bit word representing a row.
-The 64-bit rows will be referred to by $a$, $b$, $c$, and $d$.
-We define functions in the following section about the algorithm.
+We use $\oplus$ to denote XOR and $\lll$ to denote bitwise rotation left.
+The state is modeled as a 4x4 grid of 8-bit words.
+The 32-bit rows will be referred to by $a$, $b$, $c$, and $d$.
+The 8-bit bytes of the state will be address by $state_i$, where $i$ is the index of the byte in question.
+We use zero based indexing; The upper most word of a is considered to be $i = 0$, and the least significant word in d is considered to be $i = 15$.
+We denote the 8-bit s-box as s\_box, while we denote the two 4-bit s-boxes as s\_box4a and s\_box4b.
 
 \section{Algorithm}
-The cipher is an Even-Mansour based construct.
-It uses a key addition layer, followed by application of a permutation, followed by another key addition layer.
-The design uses this simple key addition layer, as opposed to generating round keys and applying them after every iteration of the permutation (as is common), because we cannot cite an explicit reason or benefit for so many key application layers.
-This saves implementation complexity, as there is no key schedule or cacheing of the key schedule.
-
-Each iteration of the permutation consists of alternating linear diffusion and non-linear layers.
-The diffusion layer consists of three applications of the shift and mix function with differing rotation amounts, which is designed to spread differences around the state evenly.
-This is followed by the non-linear layer, which is an optimal bitsliced implementation of an optimal 4x4 s-box.
-The s-box is applied 64 times in parallel on each 4-bit high 1-bit wide section of the state.
-
-Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs.
-
-In psuedocode, the cipher is defined as follows:
-
-\begin{verbatim}
-add_key(state, key)
-for round_number in 1 ... round_count:
-        add_constant(state, round)
-        permutation(state)
-add_key(state, key)
-\end{verbatim}
-
-Next, we will define the $generate\_constant$ function:
+The permutation consists of five steps: addKey, addConstant, subBytes, mixState, transposeState. The addKey step is self explanatory, and is implemented using XOR to add the key to the state:
 
 \begin{align}
-constant := round\_number\\
-constant := constant \oplus (constant <<< 3)\\
-constant := constant \oplus (constant <<< 6)\\
-constant := constant \oplus (constant << 17)\\
-constant := constant \oplus (constant << 15)\\
-constant := constant \oplus (constant << 24)\\
+\displaystyle\sum_{i=0}^{15} state_i \oplus key_i
+\end{align}\\
+
+ The addConstant step uses the index, round number, and s-box to produce and apply a constant to each 8-bit word:
+\begin{align}
+\displaystyle\sum_{i=0}^{15} state_i \oplus s\_box(i + round_i)
+\end{align}\\
+
+The subBytes step uses two separate 4x4 s-boxes on each 8-bit word; One s-box is applied to the upper 4 bits, while the other s-box is applied to the lower 4 bits.
+On a platform that is not space constrained, we simplify the process and concatenate the s-box entries to create an 8x8 s-box.
+The 8-bit s-box is applied to each 8-bit word:
+
+\begin{align}
+\displaystyle\sum_{i=0}^{15} subBytes(state_i)
+\end{align}\\
+
+The mixState function alternates between mixing vertical pairs of 8-bit words and shifting the $b$ and $d$ rows. First, we define a central component of mixState, mixPair:
+
+\begin{align}
+x := r1_i \\
+y := r2_i \\
+x := x \oplus y \\
+x := x \lll 1 \\
+y := y \oplus x \\
+y := y \lll 2 \\
+x := x \oplus y \\
+x := x \lll 4 \\
+y := y \oplus x \\
 \end{align}
 
-And the add constant function:
-
-\begin{align}
-a = a \oplus generate\_constant(round\_number)
-\end{align}
-
-Now we can define the permutation:
-
-%\begin{align}
+In the above, $r1_i$ and $r2_i$ represents either $a_i$ and $b_i$ or $c_i$ and $d_i$.
+After the first XOR, each 1x2-bit subsection has been activated.
+After the first rotation and second xor, each 2x2-bit subsection has been activated.
+After the second rotation and third xor, each 4x2 bit subsection has been activated.
+Finally, after the final rotation and  mixPair is a component of the mixPairs function, which applies mixPair to each of the eight pairs of 8-bit words:
 

### 2017-07-10 designs/nonlinear/blockcipher/arx/1/paper/design.tex
organized package + updated readme

--- 2017-03-07 designs/blockcipher/arx/1/paper/design.tex
@@
 
-Each application of the permutation is preceded by the addition of a round constant. The round constants are generated via a simple function that provides a high degree of difference between outputs.
+Each application of the permutation is preceded by the addition of a round constant.
+The round constants are generated via a simple function that provides a high degree of difference between outputs.
+Addition of the round constants eliminates rotational symmetry.
+Without them, inputs that are rotations of each other would produce outputs that are rotations of each other.
 
@@
 constant := constant \oplus (constant << 15)\\
-constant := constant \oplus (constant << 24)\\
+constant := constant \oplus (constant << 24)
 \end{align}
@@
 \begin{align}
-a = a \oplus generate\_constant(round\_number)
+a := a \oplus generate\_constant(round\_number)
 \end{align}
@@
 
-%\begin{align}
-
-\begin{align}
-\displaystyle\sum_{i=0}^{4} mixPair(a_i, b_i), mixPair(c_i, d_i)\\
-\end{align}
-
-Inside the mixState function, applications of mixPairs are interleaved with shiftRows instructions, with a final application of mixPairs operating across halves in order to mix the top and bottom rows of the state:
-
-\begin{align}
-mixPairs(a, b, c, d)\\
-shiftRows(b, d, 1) \\
-mixPairs(a, b, c, d) \\
-shiftRows(b, d, 2) \\
-mixPairs(a, b, c, d) \\
-mixPairs(a, c, b, d) \\
-\end{align}
-
-After mixState is applied, the words are transposed by feeding the indices into to s\_box4a:
-
-\begin{align}
-for\ i\ in\ 0\ ...\ 16:\\
-	\quad j = sbox[i] \\
-	\quad state_j = state_i \\
-\end{align}
+\begin{
 

### 2017-07-10 designs/nonlinear/blockcipher/arx/2/paper/design3817.tex
organized package + updated readme

--- 2017-03-10 designs/blockcipher/arx/2/paper/design3817.tex
@@
 The bit sliced design works best with the largest word size available, so we define a variant that utilizes 64-bit words.
-The design makes use of only XOR/AND gates and rotations.
+The design makes use of only XOR/AND/OR gates and rotations.
 The 4x4 S-Box is calculated discretely each application, and uses the shortest possible number of instructions among all ideal 4x4 S-Boxes.\\
@@
  Block ciphers are a widely used component in many cryptography schemes.
-They can be used with a mode of operation to provide confidentiality (as well as authenticity and integrity) to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function.
+They can be used with a mode of operation to provide confidentiality to data, they can be combined with a counter to create a secure random number generator, and they can be used as the compression function inside of a hash function.
 When required, block ciphers can be designed with a smaller state size (80-128 bits) then a hash or stream cipher (160 bits+), which can lead to smaller and less expensive hardware implementations.
@@
 We refer to the key that is exclusive-or'd into the state as the "Linear Key", and the key that is used for the bit transposition as the "Non-Linear Key".
-The four 64-bit words of the a key will be referred to as $k0$, $k1$, $k2$, and $k3$.
+The four 64-bit words of a key will be referred to as $k0$, $k1$, $k2$, and $k3$; which key will be clear from the context.
 The incrementing counter that is fed to the constant generation function is denoted as $i$\\
 
-We will use the following function names: $K_l$ refers to the linear key addition layer, while $K_n$ refers to the non-linear key addition layer (the keyed bit permutation); $K_f$ refers to the composition of $K_n$ and $K_l$, meaning $K_f(a, b, c, d) \equiv K_l(K_n(a, b, c, d))$.
-Application of the linear layer is denoted as $L(a, b, c, d)$, while application of the non-linear/S-Box layer is denoted as $S(a, b, c, d)$.
-The "load" function unpacks a 256-bit key into four 64-bit words.
+We utilize a helper function: The "load" function unpacks a 256-bit key into four 64-bit words.
 
@@
 Second, a standard linear key addition layer is applied, in the form of exclusive-or with the Linear Key.
-The key addition layer is applied before/after every four iterations of the permutation.
+The key addition layer is applied before every four iterations of the permutation, with one additional key application after the last iteration of the permutation.
 
 Each round of the permutation consists of generation and addition of the round constant to the word $a$ of the state via exclusive-or, application of the non-linear layer or "S-Box" to the columns of the state, and lastly the linear branching layer.
-Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before/after each step.
+Two rounds are required for full diffusion; One "step" consists of 4 iterations of the round function, and the key addition layer occurs before each step.
 \\
@@
 \begin{algorithmic}
-\Function{$encrypt$}{$a, b, c, d, nonlinear\_key, linear\_key$}
-	\State $i \gets 0;$
+\Function{$encrypt$}{$message, nonlinear\_key, linear\_key$}
+	\State $i \gets 1;$
+	\State $a, b, c, d \gets load(message)$
 	\For {$step \gets 0; step < 4; step \gets step + 1$}
@@
 		\For{$round \gets 0; round < 4; round \gets round + 1;$}	
-			\State $a, b, c, d \gets round_function(a, b, c, d, i);$	
+			\State $a, b, c, d \gets round\_function(a, b, c, d, i);$	
 			\State $i \gets i + 1$
@@
 \EndFunction\\
+
+\Function{$shift\_and\_shuffle$}{$a, b, c, d, r1, r2, r3, k0, k1, k2, k3$}
+	\State $b, c, d \gets shift\_rows(b, c, d, r1, r2, r3)$
+	\State $a, b, c, d \gets shuffle\_columns(a, b, c, d, k0, k1, k2, k3)$
+\EndFunction\\
+
+\Function{$shuffle\_columns$}{$a, b, c, d, k0, k1, k2, k3$}
+	\State $a, c \gets choice\_swap(k0, a, c)$
+	\State $b, d \gets choice\_swap(k1, b, d)$
+	\State $c, b \gets choice\_swap(k2, c, b)$
+	\State $d, a \gets choice\_swap(k3, d, a)$
+\EndFunction\\
+
+\Function{$choice\_swap$}{$a, b, c$}
+	\State $t \gets b$
+	\State $b \gets choice(a, b, c)$
+	\State $c \gets choice(a, c, t)$
+\EndFunction\\
+
+\Function{$choice$}{$a, b, c$}
+	\State $c \oplus (a \land (b \oplus c))$
+\EndFunction\\
 \end{algorithmic}
@@
 \Function{$add\_key$}{$a, b, c, d, linear\_key$}
-	\State $k0, k1, k2, k3 \gets load(linear\_key)$ % need to clarify k0 and friends are used for linear key to, and define load
+	\State $k0, k1, k2, k3 \gets load(linear\_key)$
 	\State $a \gets a \oplus k0$
@@
 The permutation is composed of three functions: addition of the round constant, the non-linear S-Box layer, and the linear diffusion layer.
-Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function .
+Each round constant is generated by supplying successive values of an incrementing counter to the constant generation function.
 
@@
 
-The $generate\_constant$ function is defined as follows: \\
+The $generate\_constant$ function ensures an avalanche effect occurs by ensuring one half of the bits of the input word influence one half of the bits of the output word.
+Each exclusive-or with a rotation of the word doubles the number of bits that influence each bit.
+After 5 iterations, each output bit is influenced by 32 input bits.\\
 
@@
 The S-Box is not evaluated via table lookup, but is computed explicitly upon each invocation.
-This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as follows: \\
+This removes a tming side channel that could otherwise be used to break the algorithm in practice The non-linear S-box addition layer is defined as: \\
 
@@
 Because this is a bit sliced operation, it should scale reasonably well across different architectures and word sizes.
-A hardware implementation has the potential to implement the bitwise permutation via crossed wires, which could save considerable time.
+A hardware implementation dedicated to a single key has the potential to implement the bitwise permutation via crossed wires, which could save considerable time.
 The software implementation of the bitwise permutation is not terribly slow, but it does use more instructions then the linear and non-linear parts of the round function.
@@
 
-The linear exclusive-or key addition layer is standard and is used in many if not most (modern) cipher designs.
-This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate.
+The linear exclusive-or key addition layer is standard and is used in many if not most modern cipher designs.
+This is ideal for minimizing implementation complexity: On dedicated hardware, using an integer addition based key addition layer would require implementing an adder, which requires significantly more complexity then a simple xor gate for no real benefit.
 Additionally, exclusive-or is an involution, which can simplify implementation even more in some cases.
-\\
 
@@
 We choose to utilize this model in the design here and collect the time, space, and complexity savings.
+
+The key size is not 512 bits in length because we target or claim a 512-bit security level; It is 512 bits in length to facilitate the simplest implementation possible.
+Using the linear key as the non-linear key can modify the properties of the transposition layer, so we chose to use two separate keys.
+Considering the lack of key schedule and the inability to derive additional key material from a single key, we are left with the only choice of using two separate 256-bit keys.
 
@@
 
+\section{Attacks}
+In this section we will lay out basic attacks against simplified versions of the cipher.
+We use the term "unknown" to mean a message or key bit whose value is not known.
+We use the term "unspecific" to mean a message or key bit whose index within the state is not known.
+
+By itself, the non-linear key addition layer can be broken without needing to recover the actual key in block-size (256) chosen plaintexts.
+Simply encrypt successive powers of 2, or, viewed another way, encrypt each possible word of weight 1.
+The corresponding ciphertext reveals the destination that the one input bit was transposed to.
+This attack applies against this weakened variant regardless of the number of rounds.
+
+Adding the linear key layer afterwards, such that our target is now the composition of the key addition layers, we may obtain the linear key by encrypting a block of 0s.
+The transposition has no effect, and the exclusive-or with the block of 0s leave just the key value.
+We may then obtain the equivalent information in place of the nonlinear key by the attack mentioned previously.
+This attack works against this weakened variant regardless of the number of rounds.
+
+Applying the linear diffusion layer after the composed key addition layer, we obtain output where each bit is represented as the exclusive-or sum of some unknown/unspecified key bits and some known but unspecificied input bits.
+Because the diffusion step is linear, we can still simply encrypt a block of 0s to obtain and obtain the diffused linear key.
+With this diffused key we can proceed with the encrypt powers of 2 attack to again obtain the key-equivalent information for the keyed transposition.
+Addition of the round constants will not prevent this attack from succeeding.
+This attack works against this weakened variant regardless of the number of rounds - the output will always simply be an exclusive-or sum or unknown/unspecified key bits, and some unspecified input bits.
+
+We would like to note that the above attacks would apply regardless of the implementation of the functions - using a different linear diffusing function can not ever solve the above issues, and the attacks do not indicate a failure of any of the involved functions.
+The attack utilizes only the linear nature of the produced equations.
+This is the reason why non-linearity is required in a cipher.
+While the keyed bit shuffle is implemented using AND gates, it only transposes bits and does not influence their value; it effectively just shuffles the terms of the equation.
+
+Now, we will try attacking the composition of the keyed bit shuffle and the application of the s-box.
+
 \section{Conclusion}
  We define an 256-bit Substitution-Permutation based block cipher with a 512-bit key that is oriented towards 64-bit CPUs and dedicated hardware.
-Our design uses only simple XORs, ANDs, and rotations, and offers a simple and constant-time implementation.
-While perhaps not ideal for smaller architectures, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes.
-We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the cipher structure.
+Our design uses only simple XOR/AND/OR and rotations, and offers a simple and straightforward constant-time implementation.
+While perhaps not ideal for smaller architectures, due to the large words and state, the bit-sliced nature of the design indicates that it should scale reasonably well across different architectures and word sizes.
+We introduce a non-linear key addition layer to attempt to thwart algebraic attacks against the transparent algebraic structure.
+Lastly, we include some basic attacks against weakend versions of the cipher.
 

### 2017-07-10 designs/linear/backdoorconvergent/backdoorconvergent.py

@@ -1,0 +1,134 @@
+import hashlib
+
+from crypto.utilities import random_bytes, random_integer, modular_inverse, modular_subtraction, bytes_to_integer, integer_to_bytes
+
+N = 90539821999601667010016498433538092350601848065509335050382778168697877622963864208930434463149476126948597274673237394102007067278620641565896411613073030816577188842779580374266789048335983054644275218968175557708746520394332802669663
+
+def hash_function(message, algorithm="sha256"):
+    return bytearray(getattr(hashlib, algorithm.lower())(message).digest())
+    
+def symmetric_encrypt(message, key, _hash=hash_function):
+    # encrypt one block of 256 bits
+    key_material = _hash(key)
+    ciphertext = bytearray(message)
+    assert len(key_material) == len(message)    
+    for index, byte in enumerate(key_material):
+        ciphertext[index] ^= byte
+    return ciphertext
+    
+def symmetric_decrypt(message, key, _hash=hash_function):
+    return symmetric_encrypt(message, key, _hash)    
+        
+def generate_private_key(pi_size=65, n=N):
+    pi = random_integer(pi_size)  
+    p = modular_inverse(pi, n)    
+    return p, pi
+    
+def generate_public_key(private_key, q_size=32, n=N): 
+    """ usage: generate_public_key(private_key, q_size=32, n=N) => public_key
+    
+        Returns 1 integer, suitable for use as a public key. """
+    p, pi = private_key
+    r = random_integer(q_size)
+    pr = (p * r) % n    
+    while pr & 1 != 1:
+        r = random_integer(q_size)
+        pr = (p * r) % n
+    return pr, r
+    
+def generate_keypair(n=N):
+    """ usage: generate_keypair() => public_key, private_key
+    
+        Generate a keypair; Returns 2 integers. """
+    p, pi = private_key = generate_private_key()
+    public_key, r = generate_public_key(private_key)
+    private_key = (p, pi, modular_inverse(r, n))
+    return public_key, private_key
+    
+def convergent_encrypt(message, public_key, n=N, 
+                       _hash=hash_function, encrypt=symmetric_encrypt): 
+    """ usage: convergent_encrypt(message, public_key, n=N,
+                                  _hash=hash_function, encrypt=symmetric_encrypt) => ciphertext, decryption key
+                                  
+        Given a plaintext message and public key, returns a ciphertext and secret decryption key.        
+        The ciphertext and key are both integers, which is what the convergent_decrypt function requires.
[…]

### 2017-07-10 designs/linear/homomorphic/latticebased/epqsignature.py

@@ -1,0 +1,77 @@
+#t <- k1 * m mod P
+#qr <- t mod k1
+#pie <- t - qr mod P
+#q <- qr * k2 mod P
+#e <- (pie * k3) mod P
+
+from crypto.utilities import random_integer, modular_inverse
+
+P = 90539821999601667010016498433538092350601848065509335050382778168697877622963864208930434463149476126948597274673237394102007067278620641565896411613073030816577188842779580374266789048335983054644275218968175557708746520394332802669663
+
+def generate_key(key_size=65):
+    """ usage: generate_key(key_size=KEY_SIZE) => random integer
+    
+        Returns a random integer. 
+        key_size should be set such that log(key, 2) + log(e, 2) < log(p, 2), as well as log(key, 2) > log(rk, 2) + log(q, 2)
+        For 32-byte rk, e, q values, key should be 65 bytes, and p should be 98 bytes.
+        If the key is not large enough, it cannot be used to obtain q or e
+        If the key is too large, it cannot be used to obtain q or e
+        It is recommended to use the generate_keypair function to generate a public/private keypair"""
+    key = random_integer(key_size)       
+    return key
+    
+def generate_encrypted_inverse_key(private_key, r_size=32, p=P): 
+    """ usage: generate_encrypted_inverse_key(private_key, r_size=R_SIZE, 
+                                              p=P) => ek, dk, rk
+                                              
+        Returns three integers.
+        ek is the public key for the trapdoor function.
+        dk and rk are used in the private key for the trapdoor function.
+        It is recommended to use the generate_keypair function to generate a public/private keypair"""
+    inverse_key = modular_inverse(private_key, p)
+    randomizing_key = random_integer(r_size)
+    encrypted_inverse_key = (inverse_key * randomizing_key) % p  
+    return encrypted_inverse_key, inverse_key, modular_inverse(randomizing_key, p)
+    
+def generate_keypair(key_size=65, r_size=32, p=P):
+    """ usage: generate_keypair(key_size=KEY_SIZE, r_size=R_SIZE, p=P) => public_key, private_key
+    
+        Returns a public key and a private key.
+        A private key is required to use the sign function to produce a digital signature on some data.
+        A public key is required to use the verify function to validate a digital signature on some data. """
+    key = generate_key(key_size)
+    ek, dk, rk = generate_encrypted_inverse_key(key, r_size, p)
+    private_key = (key, dk, rk)
+    public_key = ek
+    return public_key, private_key
+    
[…]

### 2017-07-10 designs/linear/homomorphic/latticebased/signaturetest3.py

@@ -1,0 +1,51 @@
+from crypto.utilities import random_integer, modular_inverse
+
+N = 90539821999601667010016498433538092350601848065509335050382778168697877622963864208930434463149476126948597274673237394102007067278620641565896411613073030816577188842779580374266789048335983054644275218968175557708746520394332802669663
+
+def generate_pi(pi_size=65, n=N):
+    pi = random_integer(pi_size)       
+    return pi
+    
+def generate_pq(private_key, q_size=32, n=N): 
+    p = modular_inverse(private_key, n)
+    q = random_integer(q_size)
+    pq = (p * q) % n      
+    return pq, modular_inverse(q, n), p
+    
+def generate_keypair():
+    pi = generate_pi()
+    pq, q, p = generate_pq(pi)
+    private_key = (pi, q, p)
+    public_key = pq
+    return public_key, private_key
+    
+def verify(signature, message, public_key, n=N):     
+    q, e = signature
+    _message = ((public_key * q) + e) % n
+    if _message == message:        
+        return True
+    else:
+        return False
+
+        
+#t <- k1 * m mod P
+#qr <- t mod k1
+#pie <- t - qr mod P
+#q <- qr * k2 mod P
+#e <- (pie * k3) mod P
+     
+def sign(message, private_key, n=N):
+    pi, ri, p = private_key       
+    pie_qr = (pi * message) % n    
+    qr = pie_qr % pi
+    assert qr == message
+    pie = pie_qr - qr     
+    return (qr * ri) % n, (pie * p) % n
+
+def test_sign_verify():
+    from unittesting import test_sign_verify    
+    test_sign_verify("signaturetest", generate_keypair, sign, verify, iterations=10000, message_size=64)
+        
+if __name__ == "__main__":
+    test_sign_verify()
+    

### 2017-07-10 designs/nonlinear/blockcipher/booleanblockcipher.py

@@ -1,0 +1,62 @@
+from crypto.utilities import rotate_left, slide, integer_to_bytes, bytes_to_integer, xor_subroutine, longs_to_bytes, bytes_to_longs
+from crypto.designs.nonlinear.ciphercomponents import choice_rotate_mixRow as nonlinear_mixing       
+from crypto.designs.nonlinear.ciphercomponents import invert_choice_rotate_mixRow as invert_nonlinear_mixing
+
+def encrypt(data, key, rounds=2):    
+    k1, k2, k3, k4 = bytes_to_longs(key)
+    s1, s2, s3, s4 = bytes_to_longs(data)
+        
+    for round in range(1, rounds + 1):              
+        
+        s1, s2, s3, s4 = nonlinear_mixing(round ^ s1 ^ k1, 
+                                          round ^ s2 ^ k2, 
+                                          round ^ s3 ^ k3, 
+                                          round ^ s4 ^ k4)
+    
+        k1, k2, k3, k4 = nonlinear_mixing(k1, k2, k3, k4)            
+        
+    return longs_to_bytes(s1 ^ k1, s2 ^ k2, s3 ^ k3, s4 ^ k4)    
+                
+def decrypt(data, key, rounds=2):
+    k1, k2, k3, k4 = bytes_to_longs(key)
+    s1, s2, s3, s4 = bytes_to_longs(data)
+        
+    keys = []
+    for round in range(1, rounds + 1):
+        keys.append((k1, k2, k3, k4))
+        k1, k2, k3, k4 = nonlinear_mixing(k1, k2, k3, k4)
+    
+    s1 ^= k1
+    s2 ^= k2
+    s3 ^= k3
+    s4 ^= k4
+    
+    for round in reversed(range(1, rounds + 1)):
+        k1, k2, k3, k4 = keys.pop(-1)
+        
+        s1, s2, s3, s4 = invert_nonlinear_mixing(s1, s2, s3, s4)
+        s1 ^= k1 ^ round
+        s2 ^= k2 ^ round
+        s3 ^= k3 ^ round
+        s4 ^= k4 ^ round        
+    return longs_to_bytes(s1, s2, s3, s4)
+    
+def test_encrypt_decrypt():
+    data = bytearray(16)
+    key = bytearray(16)
+    #data[3], data[7], data[11], data[15] = 0, 1, 1, 1
+    #key[3] = 1
+    data[-1] = 1
+    key[-1] = 1
+    rounds = 2
[…]

### 2017-07-10 designs/nonlinear/permutation/booleanpermutation2.py

@@ -1,0 +1,159 @@
+from crypto.utilities import slide
+
+def rotl16(word, amount, _mask=0xFFFF):
+    amount %= 16
+    return ((word << amount) | (word >> (16 - amount))) & _mask 
+  
+def rotl64(word, amount, _mask=0xFFFFFFFFFFFFFFFF):
+    amount %= 64
+    return ((word << amount) | (word >> (64 - amount))) & _mask 
+    
+def choice(a, b, c):
+    return c ^ (a & (b ^ c))  
+    
+def shuffle_and_shift(a, b, c, d, word_0=0xFFFF000000000000, word_1=0x0000FFFF00000000, word_2=0x00000000FFFF0000, word_3=0x000000000000FFFF):   
+    temp = a
+    tempb = b
+    tempc = c
+    register0 = (rotl16((d & word_0)    >> 48, 0 ) << 48) | (rotl16((b & word_3)    << 0 , 1 ) << 32) | (rotl16((b & word_2)    >> 16, 2 ) << 16) | rotl16((c & word_0) >> 48, 3 )
+    register1 = (rotl16((temp & word_3) >> 0 , 4 ) << 48) | (rotl16((c & word_2)    >> 16, 5 ) << 32) | (rotl16((b & word_1)    >> 32, 6 ) << 16) | rotl16((d & word_3) >> 0 , 7 )
+    register2 = (rotl16((c & word_3)    >> 0 , 8 ) << 48) | (rotl16((d & word_1)    >> 32, 9 ) << 32) | (rotl16((temp & word_0) >> 48, 10) << 16) | rotl16((d & word_2) >> 16, 11)
+    register3 = (rotl16((tempb & word_0)>> 48, 12) << 48) | (rotl16((temp & word_1) >> 32, 13) << 32) | (rotl16((tempc & word_1)>> 32, 14) << 16) | rotl16((temp & word_2) >> 16, 15)
+    return register0, register1, register2, register3          
+      
+def shuffle_bytes_and_shift_rows(_state):
+
+    temp = _state[0]
+
+    _state[0]  = rotl16(_state[11], 0 )
+    _state[11] = rotl16(_state[8] , 11)
+    _state[8]  = rotl16(_state[13], 8 )
+    _state[13] = rotl16(_state[10], 13)
+    _state[10] = rotl16(_state[14], 10)
+    _state[14] = rotl16(_state[2] , 14)
+    _state[2]  = rotl16(_state[4] , 2 )
+    _state[4]  = rotl16(_state[12], 4 )
[…]

### 2017-07-10 designs/nonlinear/permutation/choicebitwisepermutation.py

@@ -1,0 +1,74 @@
+from crypto.designs.nonlinear.ciphercomponents import choice, rotate_left
+
+def choice_swap(a, b, k):
+    t = a
+    a = choice(k, a, b)
+    b = choice(k, b, t)
+    return a, b
+    
+def shuffle_columns(a, b, c, d, k0, k1, k2, k3):
+    a, b = choice_swap(a, b, k0)      
+    c, d = choice_swap(c, d, k1)
+    #a, c = choice_swap(a, c, k2)
+    #b, d = choice_swap(b, d, k3)
+    c, b = choice_swap(c, b, k2)
+    a, d = choice_swap(a, d, k3)
+    return a, b, c, d
+    
+def bit_permutation(a, b, c, d, k0, k1, k2, k3, size=32): 
+    # this uses all reversible gates - invert, choice swap (fredkin), and rotate
+    # low weight keys are weak       
+    # data does not cause avalanche effect
+    for round in range(4):              
+        #a ^= 0xFFFFFFFF
+        #d ^= 0xFFFFFFFF
+            
+        a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)                
+        b = rotate_left(b, 1, size)
+        c = rotate_left(c, 2, size)
+        d = rotate_left(d, 3, size)               
+        
+        
+        a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)                
+        b = rotate_left(b, 4, size)
+        c = rotate_left(c, 8, size)
+        d = rotate_left(d, 12, size)                              
+        
+        
+        a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)                    
+        b = rotate_left(b, 8, size)
+        c = rotate_left(c, 12, size)
+        d = rotate_left(d, 16, size)        
+        
+        
+        a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3)
+        a, b, c, d = b, c, d, a 
+#        a, b, c, d, k0, k1, k2, k3 = k0, k1, k2, k3, a, b, c, d
+   # print
+   # print '\n'.join(format(word, 'b').zfill(32) for word in (a, b, c, d))
+    return a, b, c, d, k0, k1, k2, k3
+    
+def test_bit_permutation(key=(1, 1, 1, 1)):
+    from os import urandom
+    from crypto.analysis.visualization import test_4x32_function      
[…]

### 2017-07-10 designs/nonlinear/permutation/homomorphicbitpermutation.py

@@ -1,0 +1,495 @@
+""" Python implementation of a homomorphic secret key cipher. 
+    Uses keyed transposition to hide message bits in a sea of random bits.
+    Since transposing bits according to a key results in bits at index i relocating to index j,
+    transposing two separate messages means their bits will still "line up" in the resulting ciphertexts.
+    This, combined with padding with random data and possibly masking, facilitates homomorphic cryptography.
+
+    High level description in notation:
+        
+        padding = random_data()
+        message XOR padding
+        padding = permutation(padding)
+        message = message || padding
+        ciphertext = keyed_bit_transposition(message, key)
+        
+    outdated 11/25/2016"""
+
+from os import urandom
+
+from crypto.utilities import bytes_to_words, words_to_bytes, xor_subroutine
+from crypto.designs.nonlinear.ciphercomponents import choice, rotate_left, rotate_right
+
+def new_key(wordcount=4, wordsize=4):
+    return tuple(bytes_to_words(bytearray(urandom(wordcount * wordsize)), wordsize)) 
+
+def choice_swap(a, b, k):
+    """ Conditionally swaps a and b, based on the value of k. """
+    t = a
+    a = choice(k, a, b)
+    b = choice(k, b, t)
+    return a, b
+    
+def shuffle_columns(a, b, c, d, k0, k1, k2, k3):
+    """ Transposes each 1 bit wide/4 bit tall column such that each bit has 1/4 probability of being in any word """
+    a, b = choice_swap(a, b, k0)      
+    c, d = choice_swap(c, d, k1)
+
+    c, b = choice_swap(c, b, k2)
+    a, d = choice_swap(a, d, k3)
+    return a, b, c, d
+    
+def bit_permutation128(inputs, key, wordsize=32): 
+    """ Transpose the bits of the supplied inputs according to key.
+        Selects one of 128! permutations of bits. """
+    a, b, c, d = inputs    
+    k0, k1, k2, k3 = key
+    for round in range(1):              
+        a, b, c, d = shuffle_columns(a, b, c, d, k0, k1, k2, k3) # each 4 bit tall column is now active
+        b = rotate_left(b, 1, wordsize)
+        c = rotate_left(c, 2, wordsize)
+        d = rotate_left(d, 3, wordsize)               
+        
+        
[…]

### 2017-07-10 designs/other/scratch/choicediffusion.py

@@ -1,0 +1,37 @@
+from crypto.designs.nonlinear.ciphercomponents import choice
+
+__all__ = ["choice_diffusion", ]
+
+
+#@pride.unittest.test(crypto.crypto.analysis.visualization.test_4x64_function) ?
+# auto generate unit test    ?
+
+def hamming_weight(*inputs):
+    return sum(format(word, 'b').count('1') for word in inputs)
+    
+def choice_diffusion(in0, in1, in2, in3, k0, k1, k2, k3):
+    weight = hamming_weight(in0, in1, in2, in3)
+    print "At enter: Weight: ", hamming_weight(in0), hamming_weight(in1), hamming_weight(in2), hamming_weight(in3)
+    out0 = choice(k0, in0, in1);
+    out1 = choice(k0, in1, in0);
+    
+    out1 = choice(k1, out1, in2);
+    out2 = choice(k1, in2, out1);    
+                              
+    out2 = choice(k2, out2, in3);
+    out3 = choice(k2, in3, out2);
+                              
+    out3 = choice(k3, out3, out0);
+    out0 = choice(k3, out0, out3);      
+    
+    
+    print "At exit: Weight: ", weight
+    return out0, out1, out2, out3, k0, k1, k2, k3
+    
+def test_choice_diffusion():
+    from crypto.analysis.visualization import test_4x64_function
+    test_4x64_function(choice_diffusion, (1, 2, 4, 8, 1, 2, 4, 8))
+    
+if __name__ == "__main__":
+    test_choice_diffusion()
+    

### 2017-07-10 designs/other/scratch/swapornot.py

@@ -1,0 +1,39 @@
+from crypto.utilities import xor_subroutine
+from crypto.designs.nonlinear.ciphercomponents import choice
+
+def swap_or_not(message, key, key2):
+    k_xor_message = message ^ key
+    choice(k_xor_message, message, key2)    
+    
+    for index in range(len(message)):
+        a, b = message[index], k_xor_message[index]
+        _a, _b = message[a], k_xor_message[b]       
+        message[a]        = choice(_b, _a, key2[index])
+        k_xor_message[b]  = choice(_a, _b, key2[index])        
+        
+        #if key2[index]:        
+        #    temp = message[a]
+        #    message[a] = k_xor_message[b]
+        #    k_xor_message[b] = message[temp]
+        #else:            
+        #    temp = k_xor_message
+        #    message[a] = message[a]
+        #    k_xor_message[b] = k_xor_message[b]
+            
+            
+def test_swap_or_not():
+    message = []
+    key = []
+    key2 = []
+    for word in range(4):
+        message.extend((int(bit) for bit in format(word, 'b').zfill(8)))
+        key.extend((int(bit) for bit in format(word * 2, 'b').zfill(8)))
+        key2.extend((int(bit) for bit in format(word * 1, 'b').zfill(8)))
+    print("Before: {}".format(message))
+    for round in range(2):
+        swap_or_not(message, key, key2)
+    print("After : {}".format(message))
+    
+if __name__ == "__main__":
+    test_swap_or_not()
+    

### 2017-07-10 designs/permutation/booleanpermutation2.py

@@ -1,159 +1,0 @@
-from crypto.utilities import slide
-
-def rotl16(word, amount, _mask=0xFFFF):
-    amount %= 16
-    return ((word << amount) | (word >> (16 - amount))) & _mask 
-  
-def rotl64(word, amount, _mask=0xFFFFFFFFFFFFFFFF):
-    amount %= 64
-    return ((word << amount) | (word >> (64 - amount))) & _mask 
-    
-def choice(a, b, c):
-    return c ^ (a & (b ^ c))  
-    
-def shuffle_and_shift(a, b, c, d, word_0=0xFFFF000000000000, word_1=0x0000FFFF00000000, word_2=0x00000000FFFF0000, word_3=0x000000000000FFFF):   
-    temp = a
-    tempb = b
-    tempc = c
-    register0 = (rotl16((d & word_0)    >> 48, 0 ) << 48) | (rotl16((b & word_3)    << 0 , 1 ) << 32) | (rotl16((b & word_2)    >> 16, 2 ) << 16) | rotl16((c & word_0) >> 48, 3 )
-    register1 = (rotl16((temp & word_3) >> 0 , 4 ) << 48) | (rotl16((c & word_2)    >> 16, 5 ) << 32) | (rotl16((b & word_1)    >> 32, 6 ) << 16) | rotl16((d & word_3) >> 0 , 7 )
-    register2 = (rotl16((c & word_3)    >> 0 , 8 ) << 48) | (rotl16((d & word_1)    >> 32, 9 ) << 32) | (rotl16((temp & word_0) >> 48, 10) << 16) | rotl16((d & word_2) >> 16, 11)
-    register3 = (rotl16((tempb & word_0)>> 48, 12) << 48) | (rotl16((temp & word_1) >> 32, 13) << 32) | (rotl16((tempc & word_1)>> 32, 14) << 16) | rotl16((temp & word_2) >> 16, 15)
-    return register0, register1, register2, register3          
-      
-def shuffle_bytes_and_shift_rows(_state):
-
-    temp = _state[0]
-
-    _state[0]  = rotl16(_state[11], 0 )
-    _state[11] = rotl16(_state[8] , 11)
-    _state[8]  = rotl16(_state[13], 8 )
-    _state[13] = rotl16(_state[10], 13)
-    _state[10] = rotl16(_state[14], 10)
-    _state[14] = rotl16(_state[2] , 14)
-    _state[2]  = rotl16(_state[4] , 2 )
-    _state[4]  = rotl16(_state[12], 4 )
[…]

### 2017-07-10 designs/permutation/multipermutation.py

@@ -1,50 +1,0 @@
-from crypto.utilities import random_bytes
-
-WORD_SIZE_BITS = 6
-STATE_LENGTH = 64
-
-def generate_state(length=STATE_LENGTH):
-    return range(length)          
-        
-def permute_columns(state, key):
-    for index, word in enumerate(state):
-        state[index] = (word + key[index]) % STATE_LENGTH
-                
-def permute_row(state, key):
-    size = len(state)
-    for index in range(size - 1):
-        for index2 in range(index + 1, size):            
-            word1 = state[index]; word2 = state[index2]
-            word1, word2 = choice_swap(key, word1, word2)
-            state[index] = word1; state[index2] = word2
-        
-def choice(a, b, c):
-    return c ^ (a & (b ^ c))
-    
-def choice_swap(key, word1, word2):    
-    if key: 
-        key = 0x63    
-    t = word1    
-    word1 = choice(key, word1, word2)
-    word2 = choice(key, word2, t)
-    return word1, word2
-                        
-def permutation(state, key=[item & 1 for item in bytearray(random_bytes(STATE_LENGTH))]):    
-    # permutation /\  4 1 2 3
-    #             |   3 4 1 2 
-    #            \/   2 3 4 1 
-    #                 ------- 
-    #permutation <--> 1 2 3 4 
-    state = list(state)
-    #permute_columns(state, key)
-    permute_row(state, key)
-    
-    return state
-    
-def visualize_permutation():
-    from crypto.analysis.visualization import test_64x6_function
-    test_64x6_function(lambda *args: permutation(args), generate_state())
-    
-if __name__ == "__main__":
-    visualize_permutation()
-    

### 2017-07-10 other/scratch/bitwisemixcolumn.py

@@ -1,213 +1,0 @@
-from crypto.utilities import slide, integer_to_bytes
-from crypto.designs.ciphercomponents import choice, rotate_left
-from crypto.analysis.visualization import test_4x64_function
-
-def rotl16(word, amount):
-    return rotate_left(word, amount, bit_width=16)
-    
-def round_function(a, b, c, d):
-    # operate in parallel on 16x16 grid of bits
-    register0, register1, register2, register3 = load_to_16bit_registers(a, b, c, d)     
-    # rotate each row left by row#
-    register0, register1, register2, register3 = shift_rows(register0, register1, register2, register3) 
-    # vertically mix each 4 bit high column of each quarter, doing each quarter in parallel
-    #register0, register1, register2, register3 = mix_quarters(register0, register1, register2, register3) 
-    return register0, register1, register2, register3
-   
-def mix_quarters(register0, register1, register2, register3):   
-    register0 ^= choice(register1, register2, register3)
-    register1 ^= choice(register2, register3, register0)
-    register2 ^= choice(register3, register0, register1)
-    register3 ^= choice(register0, register1, register2)   
-    return register0, register1, register2, register3
-    
-def load_to_16bit_registers(a, b, c, d, word_0=0xFFFF000000000000, word_1=0x0000FFFF00000000, word_2=0x00000000FFFF0000, word_3=0x000000000000FFFF):   
-    register0 = ((a & word_0) << 0 ) | ((b & word_0) >> 16) | ((c & word_0) >> 32) | ((d & word_0) >> 48)    
-    register1 = ((a & word_1) << 16) | ((b & word_1) << 0 ) | ((c & word_1) >> 16) | ((d & word_1) >> 32)
-    register2 = ((a & word_2) << 32) | ((b & word_2) << 16) | ((c & word_2) << 0 ) | ((d & word_2) >> 16)    
-    register3 = ((a & word_3) << 48) | ((b & word_3) << 32) | ((c & word_3) << 16) | ((d & word_3) >> 0 )    
-    return register0, register1, register2, register3
-    
[…]

### 2017-07-10 other/scratch/hammingweighttest.py

@@ -1,100 +1,0 @@
-from os import urandom
-from math import log
-
-hamming_weight_for_size = {128 : (40, 64, 90)}
-
-# 128 bit key: hamming weight of 40 to 90 , average=64
-# 64 bit key : hamming weight of 16 to 50, average=32
-# 32 bit key : hamming weight of 3 to 29, average=16
-
-def test_average_hamming_weight():
-    _samples = []
-    sample_size = 16
-    for count in range(1024 * 100):
-        samples = bytearray(urandom(sample_size))
-        weight = sum(format(byte, 'b').zfill(8).count('1') for byte in samples)
-        _samples.append(weight)
-    print "Minimum weight: {}".format(min(_samples))
-    print "Average weight: {}".format(sum(_samples) / len(_samples))
-    print "Median  weight: {}".format(_samples[len(_samples) / 2])
-    print "Maximum weight: {}".format(max(_samples))
-    
-def test_duplicate_chance():    
-    sample_size = 2
-    samples = urandom(sample_size)
-    for count in xrange(2 ** (sample_size * 8)):
-        if urandom(sample_size) == samples:
-            break
-    print "Regenerated identical samples after: {} (2 ** {})".format(count, log(count, 2))
-
-def next_bit_permutation(v):    
-    # from http://graphics.stanford.edu/~seander/bithacks.html#NextBitPermutation
-    t = (v | (v - 1)) + 1;  
-    return t | ((((t & -t) / (v & -v)) >> 1) - 1);
-    
-def hamming_weight(data, word_size=8):
-    return sum(format(byte, 'b').zfill(word_size).count('1') for byte in data)
-    
-def find_duplicate_via_prng():    
-    import random
-    import itertools
-    from crypto.utilities import slide, bytes_to_longs
-    from crypto.designs.ciphercomponents import optimized_bit_byte_transposition_words as prng_of_hamming_weight
-    sample_size = 16
-    weight = 64
-    test_sample = list(('1' * weight).zfill(128))
-    target_sample = bytearray(16)
-    while sum(format(byte, 'b').zfill(8).count('1') for byte in target_sample) != weight:
-        target_sample[:] = urandom(16)
-    
-    random.shuffle(test_sample)
-    test_sample = tuple(int(word, 2) for word in slide(''.join(test_sample), 32))
-    target_sample = bytes_to_longs(target_sample)
-    failed = True
-    outputs = set()
-    for counter in itertools.count():
-        if test_sample == target_sample:
-            break
-        if test_sample in outputs:
[…]

### 2017-07-10 other/scratch/swapornot.py

@@ -1,39 +1,0 @@
-from crypto.utilities import xor_subroutine
-from crypto.designs.ciphercomponents import choice
-
-def swap_or_not(message, key, key2):
-    k_xor_message = message ^ key
-    choice(k_xor_message, message, key2)    
-    
-    for index in range(len(message)):
-        a, b = message[index], k_xor_message[index]
-        _a, _b = message[a], k_xor_message[b]       
-        message[a]        = choice(_b, _a, key2[index])
-        k_xor_message[b]  = choice(_a, _b, key2[index])        
-        
-        #if key2[index]:        
-        #    temp = message[a]
-        #    message[a] = k_xor_message[b]
-        #    k_xor_message[b] = message[temp]
-        #else:            
-        #    temp = k_xor_message
-        #    message[a] = message[a]
-        #    k_xor_message[b] = k_xor_message[b]
-            
-            
-def test_swap_or_not():
-    message = []
-    key = []
-    key2 = []
-    for word in range(4):
-        message.extend((int(bit) for bit in format(word, 'b').zfill(8)))
-        key.extend((int(bit) for bit in format(word * 2, 'b').zfill(8)))
-        key2.extend((int(bit) for bit in format(word * 1, 'b').zfill(8)))
-    print("Before: {}".format(message))
-    for round in range(2):
-        swap_or_not(message, key, key2)
-    print("After : {}".format(message))
-    
-if __name__ == "__main__":
-    test_swap_or_not()
-    

### 2017-07-10 pickledtest.py

@@ -1,104 +1,0 @@
-""" Provides authenticated encryption and decryption functions using only the python standard library. """    
-import hashlib
-import hmac as _hmac
-from pickle import dumps, loads
-
-from utilities import slide, xor_subroutine, random_bytes
-
-__all__ = ("encrypt", "decrypt")           
-
-_HASH_SIZES = dict((algorithm, getattr(hashlib, algorithm)().digest_size) for algorithm in hashlib.algorithms_guaranteed)
-
-def save_data(*args):      
-    return dumps(args)
-          
-def load_data(serialized_data):
-    return loads(serialized_data)    
-        
-def encrypt(data, key, nonce=None, additional_data='', algorithm="sha512", nonce_size=32):
-    """ usage: encrypt(data, key, nonce=None, additional_data='',
-                       algorithm="sha512") => cryptogram
-        
-        Encrypts and authenticates data using key and nonce.
-        Authenticates but does not encrypt additional_data
-        algorithm determines which hash algorithm to use with HMAC
-        data, key, nonce, and additional_data should be bytes or bytearray. 
-        If nonce is None, then a random nonce of nonce_size will be generated. """
-    data = bytearray(data)
-    key = bytearray(key)
-    nonce = bytearray(nonce if nonce is not None else random_bytes(32))
-    tag = _hmac_aead_cipher(data, key, nonce, additional_data, algorithm)    
-    
-    header = "hmacaead_{}".format(algorithm.lower())    
-    return save_data(header, nonce, additional_data, data, tag)
-    
-def decrypt(cryptogram, key):
-    """ usage: decrypt(cryptogram, key) => data, additional_data OR None, None
-    
-        Decrypts cryptogram using key.
-        Returns data and additional data if the data is authenticated successfully.
-        Otherwise, returns None, None."""          
-    header, nonce, additional_data, data, tag = load_data(cryptogram)
-    _hmacaead, algorithm = header.split('_', 1)
-    if _hmacaead != "hmacaead":
-        raise ValueError("Invalid algorithm '{}'".format(_hmacaead))
-    
-    if _hmac.compare_digest(tag, _hmac_aead_cipher(data, key, nonce, additional_data, algorithm, reverse=True)):
-        return data, additional_data
-    else:
-        return None, None
-                
-def _store(data, block, index, block_size):
[…]

### 2017-07-16 latex/qtpie/paper.tex
improved paper

--- 2017-06-26 latex/qtpie/paper.tex
@@
 \listoftodos
+You are missing all the non fake signature etc.
+
+You should use the environment algorithm to write your algorithm. It is difficult to understand as is.
+
+Addition over what field ? Etc for the rest. (edited)
+
+What key sizes? Why k private is 520 bits ?
+
+How does all this compares to others methods ?
 
@@
 A Trapdoor One-Way Function (TOWF) is a function that is easy for anyone to compute in one direction, but is hard to compute in reverse without some additional piece of information.
-A TOWF makes exchanging cryptographic keys a straightforward exercise: Suppose that Bob happens to know the trapdoor information for a TOWF: Alice can simply apply the TOWF to a randomly generated key and send the output to Bob.
-Bob can then use the trapdoor information to invert the output and obtain the key.
+TOWFs are useful for cryptography, because they make constructing various public key primitives a relatively straightforward exercise.
 
 The Learning-With-Errors (LWE) problem is a mathematical problem that is believed to be difficult to solve efficiently even with a quantum computer.
+A 1-dimensional LWE problem takes the form $a s + e \mod P$, where $a, P$ are known and $s, e$ are secret, random values.
 
 In this paper we define a candidate TOWF based on 1-dimensional LWE.
-It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.
+It is based on a simple observation of a congruence, $a s + e \equiv s + a^{-1} e \mod P$, along with some subtle manipulation of the sizes of the numbers involved.
+The trapdoor information is the short inverse $a^{-1}$, which allows the recovery of $s, e$ from a point $a s + e \mod P$, provided some constraints on the sizes of numbers are satisfied.
 
-\section{Definitions}
+We use the TWOF to construct basic public key algorthims for exchanging keys and creating digital signatures.
+
+\subsection{Definitions}
 We $+$ to denote addition, $a b$ to indicate multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
+We use $\leftarrow$ to indicate the assignment of a value to a name, and $\rightarrow$ to indicate the sending of data from one party to another.
 We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
 We use the function $random(k)$ to indicate the generation of of a random $k$-bit integer.
+We write application of the public key operation as $key_{pub}(s,\ e)$, and application of the private key operation as $key_{priv}(c)$.
 
 \section{Algorithm}
-There is a publicly agreed upon modulus $N$.
-The same $N$ may always be used.
+There is a publicly agreed upon modulus $P$.
+All math is done modulo $P$.
+The same $P$ may always be used.
 It should be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
-The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $N$ is slightly less then 800 bits in size.
-The larger $N$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $N$ possible.
+The size of $P$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $P$ is slightly less then 800 bits in size.
+The larger $P$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $P$ possible.
 
-\subsection{Basic Concept}
-Consider the following function:
+\subsection{Design Outline}
+Consider the following expression:
 
 \begin{flalign*}
-c := pq + e \mod N
+c \leftarrow a s + e \mod P
 \end{flalign*}
 
-Given $c, p, N$, we can recover $q, e$ using the following algorithm:
+Given $c, p, N$, we can recover $s, e$ using the following algorithm:
 
 \begin{flalign*}
-p_i := inverse(p, N)\\
-t := p_i c \equiv p_i p q + p_i e \equiv q + p_i e \mod N\\
-q := t \mod p_i\\
-t := t - q \\
-e := t / p_i
+t \leftarrow a^{-1} c\\
+s \leftarrow t \mod a^{-1}\\
+t \leftarrow t - s \\
+e \leftarrow t / a^{-1}
 \end{flalign*}
 
-The step $q := t \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$.
-We leverage this latter fact to create a trapdoor.
-We select a suitable $p_i$ that is large enough such that $q < p_i$ and small enough such that $p_i e < N$.
-Then, we calculate the modular multilicative inverse $p := inverse(p_i, N)$.
-This number will likely be very large, closer to $N$ in size then to $p_i$.
-To create a public key, we then encrypt $p$ using a random $r$ to preclude the ability of others to calculate $p_i$.
+Where $a^{-1}$ is the output of $inverse(a, P)$.
 
-The public key provides the ability to compute the forward operation $p q + e \mod N$ because there is no size constraint on $p$ for this operation (as long as $p < N$ anyways).
+The step $s \leftarrow t \mod a^{-1}$ will only function correctly if $s < a^{-1}$ and if $a^{-1} e < P$.
+We leverage this latter fact to create the trapdoor: We select a suitable $a^{-1}$ that is large enough such that $s < a^{-1}$ and small enough such that $a^{-1} e < P$.
+Then, we calculate the modular multilicative inverse $a \leftarrow inverse(a^{-1}, P)$.
+This number will likely be very large, closer to $P$ in size then to $a^{-1}$.
+To create a public key, we then encrypt $a$ using a random $r$ to preclude the ability of others to calculate $a^{-1}$.
+
+The public key provides the ability to compute the forward operation $a s + e \mod P$ because there is no size constraint on $a$ for this operation to function (as long as $a < P$ anyways).
 Supplying the inverse of the public key to the inversion algorithm will not produce correct plaintext, because the generated value will be too large.
@@
 \begin{flalign*}
-q := random(q_{size})\\
-e := random(e_{size})\\
-c := prq + e \mod N\\
-pr_i := inverse(pr, N)\\
-c_i := c pr_i \mod N\\
-c_i \equiv q + p_i r_i e \mod N\\
+key_{pub} \leftarrow a r\\
+s \leftarrow random(s_{size})\\
+e \leftarrow random(e_{size})\\
+c \leftarrow key_{pub} s + e\\
+key_{pub}^{-1} \leftarrow inverse(key_{pub}, P)\\
+c_i \leftarrow c key_{pub}^{-1}\\
+c_i \equiv s + a^{-1} r^{-1} e\\
 \end{flalign*}
 
-In the final line $c_i \equiv q + p_i r_i e \mod N$, we can see that the inverse of the public key is too large if $p_i r_i e > N$.
-While $p_i$ is relatively small, $r_i$ is (most likely) large - Ultimately, the size of $p_i r_i$ is roughly the same as $p r$, and so this alternative perspective of $q + p_i r_i e$ offers no fewer unknown bits to guess then the original $prq + e$ did.
+In the final line $c_i \equiv s + a^{-1} r^{-1} e$, we can see that the inverse of the public key is too large if $a^{-1} r^{-1} e > P$; In such a case, $s + a^{-1} r^{-1} e \mod a^{-1} r^{-1}$ will not yield $s$; While $a^{-1}$ is relatively small, $r^{-1}$ is (most likely) large - Ultimately, the size of $a^{-1} r^{-1}$ is roughly the same as $a r$, and so this alternative perspective of $s + a^{-1} r^{-1} e$ offers no more advantage to recovering $s, e$ as then the original $ars + e$ did.
 
-This is in contrast to the perspective that the holder of $p_i$ has:
+This is in contrast to the perspective that the holder of $a^{-1}$ has:
 
 \begin{flalign*}
-q := random(q_{size})\\
-e := random(e_{size})\\
-c := prq + e \mod N\\
-p_i := inverse(p, N)\\
-c_i := c p_i \mod N\\
-c_i \equiv qr + p_i e \mod N
+s \leftarrow random(s_{size})\\
+e \leftarrow random(e_{size})\\
+c \leftarrow key_{pub}s + e\\
+c_i \leftarrow c a^{-1}\\
+c_i \equiv sr + a^{-1} e
 \end{flalign*}
 
-We can see the difference in the final line $c_i \equiv qr + p_i e \mod N$ from before; While the $r$ variable is still present on the left term, $p_i e < N$ and so the inversion algorithm will work as intended.
-The presence of the $r$ variable on the left does require that $p_i$ be larger to ensure that $qr < p_i$.
+We can see the difference in the final line $c_i \equiv sr + a^{-1} e$ from before; While the $r$ variable is still present on the left term, $a^{-1} e < N$ and so $sr + a^{-1} e \mod a^{-1}$ will yield $sr$ and the inversion algorithm will work as intended.
+The presence of the $r$ variable on the left does require that $a^{-1}$ be larger to ensure that $sr < a^{-1}$.
 
@@
 \begin{flalign*}
-k_{priv} := random(priv_{size})\\
-p := inverse(k_{priv}, N)\\
-r := random(r_{size})\\
-k_{pub} := p r \mod N\\
+key_{priv} \leftarrow random(priv_{size})\\
+a \leftarrow inverse(key_{priv}, N)\\
+r \leftarrow random(r_{size})\\
+k_{pub} \leftarrow a r\\
 \end{flalign*}
 
-$priv_{size}$ must be selected such that $e k_{priv} < N$, as well as $k_{priv} > r q$, where $q, e$ are the security parameter of the public key operation and shared secret.
-For 256-bit $e, r, q$ values, $priv_{size}$ is 520 bits, while $N$ is slightly less then 800 bits.
+For the trapdoor to function correctly, $priv_{size}$ must be selected such that $e k_{priv} < P$, as well as $k_{priv} > r s$, where $s, e$ are the security parameters of the public key operation.
+For 256-bit $e, r, s$ values, $priv_{size}$ is 520 bits, while $P$ is 783 bits.
 
-\subsection{Exchanging Keys}
-To exchange a secret key: multiply the public key $p$ by a random value $q$, then add a random value $e$ to the result modulo $N$.
-The shared secret will be either $q$ or $e$ (or some combination of the two); We discuss the implications of the choices later.
-We default to using $e$ as the secret, as it is slightly less complex.
+\subsection{Public Key Operation}
+\begin{flalign*}
+a \leftarrow key_{pub}\\
+s \leftarrow random(s_{size})\\
+e \leftarrow random(e_{size})\\
+c \leftarrow a s + e\\
+\end{flalign*}
+
+\subsection{Private Key Operation}
 
 \begin{flalign*}
-p := key_{pub}\\
-q := random(q_{size})\\
-e := random(e_{size})\\
-ciphertext := p q + e \mod N\\
+t \leftarrow a^{-1} c\\
+sr \leftarrow t \mod a^{-1}\\
+t \leftarrow t - sr\\
+s \leftarrow sr r^{-1}\\
+e \leftarrow t a\\
+output\ s,\ e
 \end{flalign*}
 
-\subsection{Key Recovery}
-The shared secret $e$ (or $q$ or both) can be recover from the ciphertext via the following algorithm:
-
-\begin{flalign*}
-p_i := key_{priv}\\
-t := ciphertext * p_i \mod N\\
-q := t \mod p_i\\
-t := t - q\\
-e := t / pi\\
-q := q / r
-\end{flalign*}
-
-\subsubsection{Processing the Secret}
-The secret should be processed before use a key. Ideally, HKDF should be used; If it is not available, a simple hash function applied to the secret should be sufficient.
+Either $s, e$ or a combination of both may be used in different contexts to achieve different effects.
 
 \subsection{Homomorphism}
-In addition to the ability to add ciphertexts together, ciphertexts can be multiplied by plaintext values, and plaintext values can be added to ciphertexts.
-This second property follows naturally from the ability to add ciphertexts together.
-The third property is a result of the fact that $e$ is attached to the ciphertext by simple addition.
-In the following examples, $c_i$ are ciphertexts, while $1, 2$ are plaintext integers.
-
-\begin{flalign*}
-c_3 := c_1 + c_2\\
-c_4 := c_3 + 1\\
-c_5 := 2 c_4 
-\end{flalign*}
+Two ciphertexts of the form $a s + e$ may be added together to yield $a (s_1 + s_2) + e_1 + e_2$. 
+Ciphertexts may be multiplied by plaintext scalars - this follows from the previous property, as $c + c \equiv 2c$.
+Additionally, adjustments may be made to the value of $e$ via addition/subtraction with a plaintext scalar: $a s + e + r$.
 
@@
 
-\subsubsection{$q$ and Anti-Malleability}
-If $q$ is used as the secret instead of $e$, then the ability to add plaintext values to ciphertexts disappears.
-The value of $e$ will not influence $q$, and manipulations of the ciphertext less then a certain magnitude will not modify the plaintext obtained upon decryption.
-This is in stark contrast to the more common Non-Malleability, where modification of the ciphertext will usually modify the corresponding plaintext to a meaningless value.
+\section{Key Exchange and Digital Signatures}
+\subsection{Key Exchange}
+Given a TWOF, a basic algorithm to exchange keys can be constructed as follows: Assuming that Alice has Bob's public key already, she simply applies the public key operation to a random value and sends the result to Bob; Bob can then use the private key to recover the random value.
+Assuming that both parties are honest, then the random value will be unknown to all parties but Alice and Bob, and they can use this information to construct a secured communications channel.
+
+The basic mechanism presented in this section is not sufficient for constructing a general purpose secure communications protocol - for example, authentication is not addressed.
+The construction of such protocols is outside of the scope of this paper.
+
+\subsection{Digital Signatures}
+A TWOF can serve as a fundamental part of a digital signature scheme: The private key operation can be used to produce a preimage for a given ciphertext, and the corresponding public key can be used to check if the preimage outputs the challenge ciphertext.
+
+We note that ciphertexts produced by the TWOF are additively homomorphic - this means that signatures will possess this quality as well.
+This feature can be removed by signing a hash of the message instead of the message itself.
 
@@
 
+There is a third goal that is only applicable in the context of digital signatures: The output of the private key operation must not leak the private key.
+This goal is not applicable in the context of key exchange, because the adversary does not see the output of the private key operation.
+
 \subsection{Key Generation}
-It would appear that obtaining the private key from the public key must be done by guessing one of $p, p_i, r$.
-If this were not the case, then whatever algorithm that can be used to recover any of $p, p_i, r$ from $p r \mod N$ could be used to recover plaintexts from ciphertexts of the form $m k \mod N$ for random $m, k$ where one of $m, k$ is smaller then the other (but still large enough to reduce modulo $N$).
-It seems unlikely that such an attack exists and is faster then guessing $p, p_i,  r$.
+It would appear that obtaining the private key from the public key must be done by guessing one of $a, a^{-1}, r$.
+If this were not the case, then whatever algorithm that can be used to recover any of $a, a^{-1}, r$ from $a r \mod P$ could be used to recover plaintexts from ciphertexts of the form $m k \mod P$ for random $m, k$ where one of $m, k$ is smaller then the other (but still large enough to reduce modulo $P$).
+It seems unlikely that such an attack exists and is faster then guessing $a, a^{-1},  r$.
 
@@
 
-If we consider the case where $pr = 1$, then $prq + e \equiv q + e \mod P$ for uniformly random values $q, e$.
+If we consider the case where $ar = 1$, then $ars + e \equiv s + e \mod P$ for uniformly random values $s, e$.
+
+\subsection{Private Key Operation}
+Utilizing the TWOF here as a signature function does not provide the same confidence as using the TWOF for key exchange: With the private key operation, the expressions do not take the form of the LWE problem.
+Despite this, it is not obvious to us how to take advantage of this fact to recover the private key.
 
@@
 Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in slightly under 1 second.
-It requires .3 seconds to perform 10,000 private key operations, which implies that roughly 30,000 private key operations per second can be performed on very modest hardware.
-Our tests were performed on an Intel Celeron N2830 2.16GHz with 2 cores.
+We can perform roughly 30,000 private key operations per second.
+Our tests were performed on modest hardware, namely an Intel Celeron N2830 2.16GHz with 2 cores.
 
-In our implementation, most of the time for the public key operation is spent generating $q$ and $e$.
-In a synthetic test where $q, e$ are not generated for each invocation of the function, we can perform 100,000 public key operations per second.
+In our implementation, most of the time for the public key operation is spent generating $s$ and $e$.
+In a synthetic test where $s, e$ are not generated for each invocation of the function, we can perform 100,000 public key operations per second.
 
 Our implementation is optimized for readability.
-Much of the computation time is spent on bignum operations, and while an optimized C implementation may certainly be faster, it is not required to obtain an acceptable level of performance.
+Much of the computation time is spent on bignum operations, and while an optimized C implementation may certainly be faster, it is not required to obtain an acceptable level of performance in the context of hybrid cryptosystems.
 
@@
 \section{Conclusion}
-We define a conceptually simple, resource-practical Trapdoor One-Way Function and key exchange algorithm. 
+We define a conceptually simple, resource-practical Trapdoor One-Way Function. 
 \end{document}

### 2017-07-16 designs/linear/homomorphic/latticebased/signaturetest3.py

@@ -34,6 +34,20 @@ def verify(signature, message, public_key, n=N):
 #q <- qr * k2 mod P
 #e <- (pie * k3) mod P
      
+# ((k1m mod P) mod k1) * k2     
+# ((k1m mod P) - ((k1m mod P) mod k1)) * k3
+
+# (x mod k1) * k2
+# (x - (x mod k1)) * k3
+
+# y k2
+# (x - y) * k3
+# k3x - k3y
+
+# k1k2r + k2e1
+# (pq + e2 - k1r + e1) * k3
+#
+
 def sign(message, private_key, n=N):
     pi, ri, p = private_key       
     pie_qr = (pi * message) % n    

### 2017-07-16 designs/other/math/factoringtest.py

@@ -1,0 +1,72 @@
+# input: N such that N = xy
+# two step process
+# step 1:
+# choose a prime P > N
+# observe that xy mod P \equiv x_iy_i mod P
+# if x_iy_i > P:
+#   select another P and calculate x_iy_i again
+# else x_iy_i < P:
+#    lazily/naive factor the multiplicative inverse of N modulo P to obtain some factors of x_iy_i 
+#      - only search for "easy" results, i.e. small primes
+#        - once the search stops yielding results, abandon it
+#        - recursively apply the factoring algorithm to the remainder and accumulate the output
+#      - compute the modular inverse of factors produced this way, and accumulate them into the output container
+#    - output consists of [a, b, c, ..., n] where abc...n mod P \equiv xy mod P
+# step 2:
+# some subset of the output of step 1 produces a product modulo P that is equal to x mod P (similarly for y mod P)
+# find the subset of elements such that N % (product(subset) % P) == 0
+# if N % (product(subset) % P) == 0, then product(subset) % P equals either x or y
+# input: [a, b, c, ... , n], P, N   
+# output x, y such that xy mod P == N <- did not yield x or y in test
+
+from crypto.utilities import modular_inverse, big_prime, gcd, factor_integer
+
+def naive_factoring(number):    
+    factors = []
+    for n, exponent in factor_integer(number).items():
+        factors.extend([n] * exponent)
+    return factors
+    
+def factor_part1(xy, modulus_size=0, p=None, factoring_method=naive_factoring):
+    if p is None:
+        if modulus_size == 0:
+           raise ValueError("modulus_size or p required") 
+        p = big_prime(modulus_size) 
+        while p <= xy:
+            p = big_prime(modulus_size)    
+    inverse_xy = modular_inverse(xy, p)
+    #print "Factoring: ", xy, inverse_xy, modular_inverse(inverse_xy, p), p
+    #print "Test factoring:", inverse_xy
+    factors = factoring_method(inverse_xy) 
+    #print "Obtained factors: ", factors
+    _factors = []
+    for item in factors:     
+        _factors.extend(factoring_method(modular_inverse(item, p)))    
+
+    return _factors, p
+    
+def assemble_factors(factors, p):
+    #return itertools.product(*[[
+    possibilities = []
+    for index, number in enumerate(factors[:-1]):
+        for number2 in factors[index + 1:]:
+            possibilities.append(number * number2)
+            possibilities.append(possibilities[-1] * number2)
[…]

### 2017-07-20 latex/qtpie/paper.tex
more paper work

@@
 \begin{abstract}
- We define a simple trapdoor function based on the Learning-With-Errors problem in one dimension, and present a key exchange algorithm based on the trapdoor.
-The trapdoor algorithm is efficient in terms of key size, key generation time, ciphertext size, and public/private key operation time: We can perform many thousands of public and private key operations per second with a naive python implementation on modest hardware.
+ We define a simple trapdoor function based on the Learning-With-Errors problem in one dimension.
+The trapdoor algorithm is time and space efficient: We can perform tens of thousands of public and private key operations per second with a naive python implementation on modest hardware, and the keys and ciphertexts are small.
  \end{abstract}
@@
 In this paper we define a candidate TOWF based on 1-dimensional LWE.
-It is based on a simple observation of a congruence, $a s + e \equiv s + a^{-1} e \mod P$, along with some subtle manipulation of the sizes of the numbers involved.
+It is based on a simple observation of a congruence, $a^{-1}(a s + e) \equiv s + a^{-1} e \mod P$, along with some subtle manipulation of the sizes of the numbers involved.
 The trapdoor information is the short inverse $a^{-1}$, which allows the recovery of $s, e$ from a point $a s + e \mod P$, provided some constraints on the sizes of numbers are satisfied.
 
-We use the TWOF to construct basic public key algorthims for exchanging keys and creating digital signatures.
+We discuss the possibilities to use the TWOF to construct basic public key algorthims for encapsulating keys, public key encryption, and creating digital signatures.
+We go on to provide statistics for a key encapsulation mechanism, gathered using our open source public domain implementation of the algorithm.
+We conclude with some open problems about formal security proof for the algorithm.
 
@@
 We $+$ to denote addition, $a b$ to indicate multiplication, $a / b$ to denote division, and $\mod p$ to denote the modulo operation.
-We use $\leftarrow$ to indicate the assignment of a value to a name, and $\rightarrow$ to indicate the sending of data from one party to another.
+We use $\leftarrow$ to indicate the assignment of a value to a name.
 We use the function $inverse(k, n)$ to indicate the computation of the modular multiplicative inverse of $k \mod n$.
@@
 There is a publicly agreed upon modulus $P$.
-All math is done modulo $P$.
+All math is done in the field of integers modulo $P$.
 The same $P$ may always be used.
 It should be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough.
-The size of $P$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $P$ is slightly less then 800 bits in size.
+The size of $P$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $P$ is about 783 bits in size.
 The larger $P$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $P$ possible.
@@
 
-Given $c, p, N$, we can recover $s, e$ using the following algorithm:
+We refer to this expression as the public key operation.
+If the expression $a s + e$ were over integers instead of modulo $P$, then we could recover $e$ simply by performing $c \mod a$; We could similarly recover $s$ by performing $c / a$.
+However, since $a s > P$ then this will no longer work.
+
+Given $c, a, P$, we can recover $s, e$ using the following algorithm:
 
@@
 \begin{flalign*}
-key_{pub} \leftarrow a r\\
+k_{pub} \leftarrow a r\\
 s \leftarrow random(s_{size})\\
 e \leftarrow random(e_{size})\\
-c \leftarrow key_{pub} s + e\\
-key_{pub}^{-1} \leftarrow inverse(key_{pub}, P)\\
-c_i \leftarrow c key_{pub}^{-1}\\
+c \leftarrow k_{pub} s + e\\
+k_{pub}^{-1} \leftarrow inverse(k_{pub}, P)\\
+c_i \leftarrow k_{pub}^{-1} c\\
 c_i \equiv s + a^{-1} r^{-1} e\\
@@
 
-In the final line $c_i \equiv s + a^{-1} r^{-1} e$, we can see that the inverse of the public key is too large if $a^{-1} r^{-1} e > P$; In such a case, $s + a^{-1} r^{-1} e \mod a^{-1} r^{-1}$ will not yield $s$; While $a^{-1}$ is relatively small, $r^{-1}$ is (most likely) large - Ultimately, the size of $a^{-1} r^{-1}$ is roughly the same as $a r$, and so this alternative perspective of $s + a^{-1} r^{-1} e$ offers no more advantage to recovering $s, e$ as then the original $ars + e$ did.
+In the final line $c_i \equiv s + a^{-1} r^{-1} e$, we can see that the inverse of the public key will be too large if $a^{-1} r^{-1} e > P$; In such a case, $s + a^{-1} r^{-1} e \mod a^{-1} r^{-1}$ will not yield $s$; While $a^{-1}$ is relatively small, $r^{-1}$ is (most likely) large - Ultimately, the size of $a^{-1} r^{-1}$ is roughly the same as $a r$, and so this alternative perspective of $s + a^{-1} r^{-1} e$ offers no more advantage to recovering $s, e$ as then the original $ars + e$ did.
 
@@
 \begin{flalign*}
-s \leftarrow random(s_{size})\\
-e \leftarrow random(e_{size})\\
-c \leftarrow key_{pub}s + e\\
+\dots\\
 c_i \leftarrow c a^{-1}\\
@@
 \begin{flalign*}
-key_{priv} \leftarrow random(priv_{size})\\
-a \leftarrow inverse(key_{priv}, N)\\
+k_{priv} \leftarrow random(priv_{size})\\
+a \leftarrow inverse(k_{priv}, N)\\
 r \leftarrow random(r_{size})\\
@@
 \begin{flalign*}
-a \leftarrow key_{pub}\\
+a \leftarrow k_{pub}\\
 s \leftarrow random(s_{size})\\
@@
 
-\section{Key Exchange and Digital Signatures}
-\subsection{Key Exchange}
+\section{Key Encapsulation, Public Key Encryption, and Digital Signatures}
+\subsection{Key Encapsulation}
 Given a TWOF, a basic algorithm to exchange keys can be constructed as follows: Assuming that Alice has Bob's public key already, she simply applies the public key operation to a random value and sends the result to Bob; Bob can then use the private key to recover the random value.
@@
 
+\subsection{Public Key Encryption}
+We can generalize and say that the Key Encapsulation Mechanism presented in the prior section is an example of using the trapdoor for public key encryption on random plaintext values.
+It is clear then that one of the values of $s, e$ can be used to store a plaintext value.
+
+Considering the efficiency of hybrid cryptosystems, where an asymmetric algorithm is used to establish a key for a message, then a symmetric cipher is used to perform the actual encryption, we first must determine what can be gained by storing a message inside the public key ciphertext.
+
+The most attractive feature is probably the homomorphism - the ability to add and manipulate ciphertexts can enable more complex cryptographic schemes and protocols.
+However, the manner with which plaintext information is stored and possibly padded will influence the nature of the homomorphic properties, and a careful configuration will be required to preserve the desired relationship(s).
+For example, if $e$ is used to store the message, then plaintext adjustments may be made to the resultant ciphertext; However, if $s$ is used as to store the message, then the ciphertext will no longer facilitate plaintext adjustments.
+
 \subsection{Digital Signatures}
@@
 We note that ciphertexts produced by the TWOF are additively homomorphic - this means that signatures will possess this quality as well.
-This feature can be removed by signing a hash of the message instead of the message itself.
+Usually this feature can be removed by incorporating a hash function into the signature process and padding the result before applying the private key signing operation.
 
@@
 \subsection{Key Generation}
-It would appear that obtaining the private key from the public key must be done by guessing one of $a, a^{-1}, r$.
+Obtaining the private key from the public key must be done by guessing one of $a, a^{-1}, r$.
 If this were not the case, then whatever algorithm that can be used to recover any of $a, a^{-1}, r$ from $a r \mod P$ could be used to recover plaintexts from ciphertexts of the form $m k \mod P$ for random $m, k$ where one of $m, k$ is smaller then the other (but still large enough to reduce modulo $P$).
@@
 
-If we consider the case where $ar = 1$, then $ars + e \equiv s + e \mod P$ for uniformly random values $s, e$.
+We will first consider the case where $e \leftarrow random(1)$.
+The task of the adversary is to recover $e$, given $a,\ a s + e$ for $a \leftarrow \{0,\ \dots,\ P\}$, $s \leftarrow \{0,\ \dots,\ P\}$.
+If an adversary can guess the least significant bit of $a s$, then they can obtain $e$ from $a s + e$.
+
+If we consider the case where $a = 1$, then $a s + e \equiv s + e \mod P$ for uniformly random values $s, e$. Recovering $s,\ e$ in this situation is clearly intractable.
+
+If we consider 8-bit $a, s$ values and $P = 257$, then we can evaluate the function $a x$ on values $\{0,\dots,\ 256\}$ and produce an 8-bit s-box, like the kind used in symmetric cryptography.
+We can then analyze the result with the same techniques and tools.
+We have done so and found differentials ranging from probability $62/256$ in the worst case, to around $64/256$ in the average case, to $254/256$ in the worst case.
+However, considering that each ciphertext $a s + e$ uses a unique, random $s$, it is not clear how to select a differential to try to exploit.
+Additionally, real instances of the problem will use $a,\ s$ values that are much larger then any tool for analyzing s-boxes can handle.
 
@@
 \section{Metrics}
-Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in slightly under 1 second.
+Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in 1 second.
 We can perform roughly 30,000 private key operations per second.
@@
 
-\subsection{Implementation Complexity}
-The implementation complexity of the scheme is very low. Our public domain python implementation of the algorithm spans barely 100 lines, including the documentation and comments.\\
+\section{Open Problems}
+Our results are lacking in rigorous proof; We do not posses the requisite skills to create such proofs.
+We leave it as an open problem to formally prove (or dis-prove) the security of the key generation function and public key operation.
 
-Additional code is required for supporting functions such as the generation of prime numbers (only if $N$ is being generated/not already established) and unit testing.
-These are modest requirements that can be implemented without much complexity.
-\\
+We do not know if the private key operation can be proven secure; We leave this as an open problem, along with the construction of a concrete digital signature scheme.
 
@@
 We define a conceptually simple, resource-practical Trapdoor One-Way Function.
+We discuss the potential applications of such a function, and provide performance statistics from our open-source public-domain python implementation of a key encapsulation mechanism using the trapdoor function.
+Finally, we discuss some open problems related to formally proving the security of the algorithm.
 \end{document}

### 2017-07-23 latex/qtpie/paper.tex
paper changes

@@
 \listoftodos
-You are missing all the non fake signature etc.
-
-You should use the environment algorithm to write your algorithm. It is difficult to understand as is.
-
-Addition over what field ? Etc for the rest. (edited)
-
-What key sizes? Why k private is 520 bits ?
 
@@
 For 256-bit $e, r, s$ values, $priv_{size}$ is 520 bits, while $P$ is 783 bits.
+The size of the modulus effectively determines the size of the public key; This results in a public key size of 783 bits, for the aforementioned parameters.
 
@@
 
+The private key operation presented here is slightly more complex than the example demonstrated earlier because of the presence of the $r$ term.
 Either $s, e$ or a combination of both may be used in different contexts to achieve different effects.
@@
 \subsection{Homomorphism}
-Two ciphertexts of the form $a s + e$ may be added together to yield $a (s_1 + s_2) + e_1 + e_2$. 
+Ciphertexts support integer addition: Two ciphertexts of the form $a s + e$ may be added together to yield $a (s_1 + s_2) + e_1 + e_2$.
+
 Ciphertexts may be multiplied by plaintext scalars - this follows from the previous property, as $c + c \equiv 2c$.
+
 Additionally, adjustments may be made to the value of $e$ via addition/subtraction with a plaintext scalar: $a s + e + r$.
@@
 \subsection{Key Encapsulation}
-Given a TWOF, a basic algorithm to exchange keys can be constructed as follows: Assuming that Alice has Bob's public key already, she simply applies the public key operation to a random value and sends the result to Bob; Bob can then use the private key to recover the random value.
+Given a TWOF, a basic algorithm to exchange keys can be constructed as follows: Assuming that Alice has Bob's public key already, she simply applies the public key operation to a random value and sends the output to Bob; Bob can then use the private key to recover the random value.
 Assuming that both parties are honest, then the random value will be unknown to all parties but Alice and Bob, and they can use this information to construct a secured communications channel.
@@
 
-If we consider 8-bit $a, s$ values and $P = 257$, then we can evaluate the function $a x$ on values $\{0,\dots,\ 256\}$ and produce an 8-bit s-box, like the kind used in symmetric cryptography.
+If we consider 8-bit $a, s$ values and $P = 257$, then we can evaluate the function $a s$ on values $\{0,\dots,\ 256\}$ and produce an 8-bit s-box, like the kind used in symmetric cryptography.
 We can then analyze the result with the same techniques and tools.
@@
 \section{Metrics}
-Using our public domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in 1 second.
+We have implemented the trapdoor and developed a key encapsulation mechanism with it.
+Using our open-source public-domain python implementation that is configured for a 256-bit security level, we can perform 10,000 public key operations in 1 second.
 We can perform roughly 30,000 private key operations per second.
@@
 
-Our implementation is optimized for readability.
+Key sizes and ciphertext sizes are relatively small - ciphertexts and public keys are effectively the same size as the modulus; In our implementation, ciphertexts and public keys are about 783 bits in size.
+
+Private keys are also quite small, with certain time/space tradeoffs available: In the most compact scenario for key encapsulation, the private key can require only 520 bits for storage, used to store only the short inverse $a^{-1}$.
+In the worst case scenario, where each of $a,\ a^{-1},\ r$ is stored, the private key size requires slightly less then 1600 bits of storage space.
+
+Our implementation is optimized for clarity and readability.
 Much of the computation time is spent on bignum operations, and while an optimized C implementation may certainly be faster, it is not required to obtain an acceptable level of performance in the context of hybrid cryptosystems.
@@
 \section{Open Problems}
-Our results are lacking in rigorous proof; We do not posses the requisite skills to create such proofs.
-We leave it as an open problem to formally prove (or dis-prove) the security of the key generation function and public key operation.
+Our results are lacking in formal rigorous proof; We do not posses the requisite skills to create such proofs.
+We leave it as an open problem to formally prove or dis-prove the security of the key generation function and public key operation.
 
